### 2022-05-18 packages/spec-haskell/yellowpaper/Paper.tex
yellow paper latex pipeline

\documentclass{article}

\usepackage{fvextra}
\usepackage{csquotes}
\usepackage{xcolor}
\usepackage{minted}

\usepackage{biblatex}
\addbibresource{../../yellowpaper/Biblio.bib}

\input{../tex/lhsfmt.tex}
\long\def\ignore#1{}
\newcommand{\lhsparagraph}[1]{\paragraph{#1}\mbox{}\\}

\title{Superfluid Money: Enabling Generalized Schemes For Monetary Units}
\author{
    Miao, ZhiCheng (hellwolf)\\
    Co-Founder, Superfluid Finance\\
    miao@superfluid.finance
}

\begin{document}

\maketitle

\begin{abstract}
    \begin{center}
        (Some Distant Lyric as Placeholder)

        Money, money, money

        Must be funny

        In the rich man's world

        Money, money, money

        Always sunny

        In the rich man's world

        \

        Ah, all the things I could do

        If I had a little money

        It's a rich man's world

        It's a rich man's world
    \end{center}
\end{abstract}

\section{Introduction}

It should be fair to say, every aspects of money are controversial: the nature of money, the value of money, money and
banking, and monetary reconstruction. \cite{von2013theory}

But less has been challenged is the underlying theory of money schemes, or often called payment systems.

This yellow paper aims to add a new controversy, by introducing the concept of context into the money schemes and
generalizing existing theory for a new unifying theory of money schemes in Part 1.

In Part 2, we also put forth a realization and specification of a version of contextual money scheme known enabled by a
system called Superfluid money.

The yellow paper also uses literate Haskell as a technique to embed concepts and specifications as compilable code for
better verifiability and reusability.

(STILL WIP)

\newpage
\part{Philosophy of Money}
\newpage

\section{Nature of Money}

\section{Money Schemes}

\subsection{A New Unifying Theory}

\input{../tex/MoneyDistributionConcepts.tex}

\subsection{Communism}

\input{../tex/Communism.tex}

\subsection{Context free Schemes}

Most of the existing money schemes are of this category, where a money unit completely disregards its context and hence
its liquidity value and bearer are static until the next money redistribution occurs.

Here are the type definitions of these money schemes defined in \cite{buldas2021unifying}:

TODO...

\subsection{Contextual Schemes}

In contract, under the contextual money schemes, the liquidity value and maybe even bearer of a money unit can be a
function of context too.

TODO...

\newpage
\part{Superfluid Money}
\newpage

\section{Real Time Balance}

\section{Sub Systems}

\section{Agreement Sub System}

\section{Type of Agreements}

\subsection{Transferable Balance Agreement}

\subsection{Constant Flow Agreement}

\subsection{Distribution Agreement}

\subsection{Decaying Flow Agreement}

\section{Solvency Sub Systems}

\subsection{Buffer Based Solvency Systems}

\section{Type Of Money Units}

\newpage

\printbibliography{}

\end{document}

### 2022-09-20 packages/spec-haskell/yellowpaper/Paper.tex
cleanup build system
yellow paper - finalizing introduction part

@@
-\documentclass{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Document Preamble
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[a4paper]{article}
 
+%% Base Folder for Inputs
+\makeatletter
+\def\input@path{{../tex/}}
+\makeatother
+
+%% Import Packages
 \usepackage{fvextra}
@@
 \usepackage{minted}
+\usepackage{amsmath}
+\usepackage{enumitem}
 
-\usepackage{biblatex}
-\addbibresource{../../yellowpaper/Biblio.bib}
+%% Literate Haskell Macros
 
-\input{../tex/lhsfmt.tex}
+%%% include common formatting
+\input{lhsfmt.tex}
+%%% for ignoring some code
 \long\def\ignore#1{}
+%%% for creating a paragraph
 \newcommand{\lhsparagraph}[1]{\paragraph{#1}\mbox{}\\}
 
-\title{Superfluid Money: Enabling Generalized Schemes For Monetary Units}
-\author{
-    Miao, ZhiCheng (hellwolf)\\
+%% Document Meta Data
+
+\title{Denotational Semantics of General Payment Primitives, and Its Payment System}
+
+\author{\\
+    Miao, ZhiCheng\\
     Co-Founder, Superfluid Finance\\
@@
 
+\usepackage[
+    backend=biber,
+    style=alphabetic,
+]{biblatex}
+\addbibresource{../tex/Biblio.bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Document Body
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-
 \maketitle
@@
     \begin{center}
-        (Some Distant Lyric as Placeholder)
+        (Some distant lyrics as the placeholder of the actual abstract)
 
@@
 
-It should be fair to say, every aspects of money are controversial: the nature of money, the value of money, money and
-banking, and monetary reconstruction. \cite{von2013theory}
+It should be fair to say, every aspect of money are controversial: the nature of money, the value of money, money and
+banking, and monetary reconstruction. Two major schools of thoughts about theory of money are the \textit{Austrian
+    school} \cite{von2013theory} and the \textit{Chicago school} \cite{friedman1989quantity}. That is before the
+appearance of Internet-era version of monetary reconstruction, broadly defined as cryptocurrency, which challenges
+theories of money further and demands their updates \cite{ammous2018can} \cite{hardle2020understanding}.
 
-But less has been challenged is the underlying theory of money schemes, or often called payment systems.
+But when it comes to the function of money, it is less controversial. According to Von Mises,
 
-This yellow paper aims to add a new controversy, by introducing the concept of context into the money schemes and
-generalizing existing theory for a new unifying theory of money schemes in Part 1.
+\begin{quotation}
+The function of money is to facilitate the business of the market by acting as a common medium of
+exchange. \footfullcite[][Part One, Chapter I, § 1, p1]{von2013theory}
+\end{quotation}
 
-In Part 2, we also put forth a realization and specification of a version of contextual money scheme known enabled by a
-system called Superfluid money.
+How do different forms of money perform this function, especially in the information age, when electronic forms of money
+are increasingly used?
 
-The yellow paper also uses literate Haskell as a technique to embed concepts and specifications as compilable code for
-better verifiability and reusability.
+This yellow paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of
+how money can perform its function of medium of exchange using computer science.
 
-(STILL WIP)
+In Part I, we shall first explore the foundation for the survey. Here we present a formal definitions of payment system,
+and various models in the system. We then select a few relevant approaches used in computer science useful for defining
+formal specification of payment system.
+
+One of the approaches is denotational semantics, which is used in Part II of the paper to define the general payment
+primitives. Along with the denotational semantics, a restatement of it in \textit{Haskell programming language} is also
+included.
+
+In Part III, a reference implementation of the general payment primitives and its payment system called
+\textit{Superfluid Money} is introduced.
+
+In Part IV, some possible further investigations are included for future study purpose.
 
 \newpage
-\part{Philosophy of Money}
+\part{Foundation}
 \newpage
@@
 
-\section{Money Schemes}
+Nature of money.
 
-\subsection{A New Unifying Theory}
-
-\input{../tex/MoneyDistributionConcepts.tex}
-
-\subsection{Communism}
-
-\input{../tex/Communism.tex}
-
-\subsection{Context free Schemes}
+\section{Money Distribution}
 
@@
 
-\subsection{Contextual Schemes}
+\subsection{A New Unifying Theory}
+
+\input{MoneyDistributionConcepts.tex}
+
+\section{Forms of Medium}
+
+\section{Payment Models}
+
+\subsection{Discrete Payments}
+
+\subsection{Continuous Payments}
 
@@
 TODO...
+
+\section{Related Paradigms}
+
+\subsection{Constraint Programming}
+
+\subsection{Functional Reactive Programming}
+
+\subsection{Denotational Semantics}
+
+\section{Generalized Denotational Payment Semantics}
+
+Here is the specification of denotational semantics that support both discrete and continous payments.
+
+Here is the list of acronyms used:
+
+\begin{itemize}
+    \item \textbf{MD} is \textit{Money Distribution}.
+    \item \textbf{MU} is \textit{Monetary Unit}.
+    \item \textbf{RTB} is \textit{Real Time Balance}.
+\end{itemize}
+
+\subsection{Generalized Payment Model}
+
+\begin{equation}\label{sem_transfer}
+    \begin{split}
+        [\![MD\ mu\ t\ rtb]\!] = mu \rightarrow t \rightarrow rtb
+    \end{split}
+\end{equation}
+
+\subsection{Monoidial Payment Model}
+
+\begin{equation}\label{sem_mzero}
+    [\![\emptyset]\!] = \lambda\ mu\ t\ \rightarrow 0
+\end{equation}
+
+\begin{equation}\label{sem_mappend}
+    [\![mda \oplus\ mdb]\!] = \lambda\ mu\ t\ \rightarrow
+    [\![mda]\!]\ mu\ t\ +\ [\![mdb]\!]\ mu\ t
+\end{equation}
+
+\subsection{Payment Premitives}
+
+\begin{equation}\label{sem_transfer}
+    \begin{split}
+        [\![&transfer\ from\ to\ amount\ md]\!] = [\![md]\!]\ \oplus \\
+        (\lambda\ case&\ mu\ t \\
+        &|\ from = mu \rightarrow -amount \\
+        &|\ to   = mu \rightarrow amount \\
+        &|\ otherwise \rightarrow 0 \\
+        )
+    \end{split}
+\end{equation}
+
+\begin{equation}\label{sem_updateConstantFlow}
+    \begin{split}
+        [\![&updateConstantFlow\ from\ to\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
+        (\lambda\ case&\ mu\ t \\
+        &|\ from = mu \rightarrow -flowRate * (t - t') \\
+        &|\ to   = mu \rightarrow flowRate  * (t - t') \\
+        &|\ otherwise \rightarrow 0 \\
+        )
+    \end{split}
+\end{equation}
+
+\begin{equation}
+    unit :: sub \rightarrow subs \rightarrow Int
+\end{equation}
+
+\begin{equation}
+    proportion\ sub\ subs = {{ unit\ sub\ subs } \over { \displaystyle \sum_{x \in subs} unit\ x\ subs }}
+\end{equation}
+
+\begin{equation}\label{sem_distributeProportionally}
+    \begin{split}
+        [\![&distributeProportionally\ pub\ subs\ amount\ md]\!] = [\![md]\!]\ \oplus \\
+        (\lambda\ case&\ mu\ t \\
+        &|\ pub = mu \rightarrow -amount \\
+        &|\ \exists sub \in subs\ { sub = mu } \rightarrow amount * (proportion\ mu\ subs) \\
+        &|\ otherwise \rightarrow 0 \\
+        )
+    \end{split}
+\end{equation}
+
+\begin{equation}\label{sem_distributeProportionally}
+    \begin{split}
+        [\![&updateProportionalDistributionConstantFlow\ pub\ subs\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
+        (\lambda\ case&\ mu\ t \\
+        &|\ pub = mu \rightarrow -flowRate * (t - t') \\
+        &|\ \exists sub \in subs\ { sub = mu } \rightarrow flowRate * (t - t') * (proportion\ mu\ subs) \\
+        &|\ otherwise \rightarrow 0 \\
+        )
+    \end{split}
+\end{equation}
 

### 2022-09-21 packages/spec-haskell/yellowpaper/Paper.tex
[yellowpaper] updated outline and added payment system section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[a4paper]{article}
+\documentclass[a4paper]{report}
 
@@
 \usepackage{enumitem}
+\usepackage{graphicx}
 
@@
 
-\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 banking, and monetary reconstruction. Two major schools of thoughts about theory of money are the \textit{Austrian
-    school} \cite{von2013theory} and the \textit{Chicago school} \cite{friedman1989quantity}. That is before the
+    school} (\cite{von2013theory}) and the \textit{Chicago school} (\cite{friedman1989quantity}). That is before the
 appearance of Internet-era version of monetary reconstruction, broadly defined as cryptocurrency, which challenges
-theories of money further and demands their updates \cite{ammous2018can} \cite{hardle2020understanding}.
+theories of money further and demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
 
@@
 The function of money is to facilitate the business of the market by acting as a common medium of
-exchange. \footfullcite[][Part One, Chapter I, § 1, p1]{von2013theory}
+exchange. \footfullcite[][Chapter One, Chapter I, § 1, p1]{von2013theory}
 \end{quotation}
@@
 
-In Part I, we shall first explore the foundation for the survey. Here we present a formal definitions of payment system,
-and various models in the system. We then select a few relevant approaches used in computer science useful for defining
-formal specification of payment system.
+In Chapter I, we shall first explore the foundation for the survey. Here we present a formal definition of payment system,
+and various models used in the system. We then select a few relevant approaches used in computer science useful for
+modeling and defining formal specification for the payment system.
 
-One of the approaches is denotational semantics, which is used in Part II of the paper to define the general payment
-primitives. Along with the denotational semantics, a restatement of it in \textit{Haskell programming language} is also
-included.
+One of the approaches is \textit{denotational semantics}, which is used in Chapter II of the paper to define the general
+payment primitives. Along with the denotational semantics, a restatement\footnote{It is a borrowed term from common law:
+"restatement of the law". In our case, the denotative mathematical "laws".} of it in \textit{Haskell programming
+    language} (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
 
-In Part III, a reference implementation of the general payment primitives and its payment system called
+In Chapter III, a reference implementation of the general payment primitives and its payment system called
 \textit{Superfluid Money} is introduced.
 
-In Part IV, some possible further investigations are included for future study purpose.
+In Chapter IV, some possible further investigations are included for future study purpose.
 
-\newpage
-\part{Foundation}
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Foundation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Nature of Money}
+\section{Payment System}
 
-Nature of money.
+We shall define a payment system, whereby:
 
-\section{Money Distribution}
+\begin{itemize}
+\item \textit{money distribution} models how monetary value is distributed amongst bearers\footnote{(Banking \& Finance)
+a person who presents a note or bill for payment. - Collins English Dictionary},
+\item \textit{payment primitives} updates money distribution,
+\item \textit{financial system} provides the execution environment for the payment primitives,
+\item and \textit{forms of money medium} are the "user interfaces" of money for the bearers.
+\end{itemize}
+
+\subsection{Money Distribution Models}
 
@@
 
-TODO...
+\begin{figure}
+  \includegraphics[width=\linewidth]{assets/discrete-money-distribution.png}
+  \caption{Schematic representation of discrete money distribution}
+  \label{fig:discrete-md}
+\end{figure}
 
-\subsection{A New Unifying Theory}
+\subsubsection{A New Unifying Model}
 
@@
 
-\section{Forms of Medium}
+\subsection{Payment Primitives}
 
-\section{Payment Models}
+\subsection{Payment System Models}
 
-\subsection{Discrete Payments}
+\subsubsection{Discrete Payments}
 
-\subsection{Continuous Payments}
+\subsubsection{Continuous Payments}
 
-In contract, under the contextual money schemes, the liquidity value and maybe even bearer of a money unit can be a
-function of context too.
+\subsection{Money Medium Models}
 
-TODO...
-
-\section{Related Paradigms}
+\section{Relevant Approaches}
 
@@
 
-\section{Generalized Denotational Payment Semantics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{General Payment Primitives}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Denotational Semantics}
 
@@
 
-\newpage
-\part{Superfluid Money}
-\newpage
+\section{Restatement in Haskell}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Superfluid Money - A Reference Implementation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Future Investigations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Restatement in Agda and Correctness Proof}
+
+\section{Constraint in Consensus}
+
+\section{Payment in General Accounting Domains}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
-
 \printbibliography{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-09-21 packages/spec-haskell/yellowpaper/Paper.tex
money distribution models

@@
 \usepackage{minted}
+\usepackage{amsfonts}
 \usepackage{amsmath}
@@
 
-In Chapter I, we shall first explore the foundation for the survey. Here we present a formal definition of payment system,
+In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal definition of payment system,
 and various models used in the system. We then select a few relevant approaches used in computer science useful for
@@
 
-One of the approaches is \textit{denotational semantics}, which is used in Chapter II of the paper to define the general
+One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to define the general
 payment primitives. Along with the denotational semantics, a restatement\footnote{It is a borrowed term from common law:
@@
 
-In Chapter III, a reference implementation of the general payment primitives and its payment system called
+In Chapter 4, a reference implementation of the general payment primitives and its payment system called
 \textit{Superfluid Money} is introduced.
 
-In Chapter IV, some possible further investigations are included for future study purpose.
+In Chapter 5, some possible further investigations are included for future study purpose.
 
@@
 
-We shall define a payment system, whereby:
+We first define a payment system, whereby:
 
@@
 
+For its modern upgrade, the system should also have these properties:
+
+\begin{itemize}
+\item Money can be distributed continuously over time, as opposed to be discrete.
+\item Payment primitives can involve more than two parties, as opposed to be only for a sender and a receiver.
+\item Financial system should be compositional.
+\end{itemize}
+
 \subsection{Money Distribution Models}
 
-Most of the existing money schemes are of this category, where a money unit completely disregards its context and hence
-its liquidity value and bearer are static until the next money redistribution occurs.
+A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the following components:
 
-Here are the type definitions of these money schemes defined in \cite{buldas2021unifying}:
+\begin{itemize}
+\item U is the set of monetary units
+\item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of every value unit u. The set
+    $\mathbb{N}$ is the set of all natural numbers, but instead, we can use any set of numerals that is totally ordered
+    (e.g.\ integers, real numbers).
+\item $\beta : U \rightarrow \mathfrak{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
+    $\mathfrak{B}$ is the set of possible bearers. The bearer is usually a legal construction defining any type of legal
+    entity, such as a person, a family, a company, a state institution, etc.
+\end{itemize}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{assets/discrete-money-distribution.png}
+This discrete nature of money distribution is schematically depicted in {\ref{fig:discrete-md}}:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{../assets/discrete-money-distribution.png}
     \caption{Schematic representation of discrete money distribution}

### 2022-09-22 packages/spec-haskell/yellowpaper/Paper.tex
DONE subsection: Money Distribution Models

@@
 
-But when it comes to the function of money, it is less controversial. According to Von Mises,
+This yellow paper does not intend to address these controversies, but to focus on the function of money. According to
+Von Mises:
 
@@
 
-This yellow paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of
-how money can perform its function of medium of exchange using computer science.
+This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
+can perform its function of medium of exchange using computer science.
 
-In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal definition of payment system,
-and various models used in the system. We then select a few relevant approaches used in computer science useful for
-modeling and defining formal specification for the payment system.
+In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal definition of payment
+system and its components. We then select a few relevant approaches used in computer science useful for modeling and
+defining formal specification for the payment system.
 
@@
 
-We first define a payment system, whereby:
+Here we present a formal definition of payment system and its components.
+
+\paragraph{}
+
+A payment system can be solely defined by these components:
 
@@
 \end{itemize}
+
+\paragraph{}
 
@@
 \begin{itemize}
-\item U is the set of monetary units
+\item U is the set of monetary units.
 \item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of every value unit u. The set
@@
 
-This discrete nature of money distribution is schematically depicted in {\ref{fig:discrete-md}}:
+This discrete nature of this money distribution model is schematically depicted in {\ref{fig:discrete-md}}:
 
@@
 
-\subsubsection{A New Unifying Model}
+\subsubsection{Using Shared Context}
+
+But the discrete nature of the model does not provide the necessary element for us to add the desired properties to the
+payment system. Here we propose a modification that involves the usage of \textit{shared context (ctx for short)}:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{../assets/money-distribution-with-ctx.png}
+    \caption{Schematic representation of money distribution with shared context}
+    \label{fig:md-with-ctx}
+\end{figure}
+
+Note that in this model, shared context can be updated independently while value functions of the same money
+distribution can produce different monetary values.
+
+\paragraph{}
+
+Here are some examples how that could work:
+
+\begin{itemize}
+\item If time is included the shared context, then monetary value of each money unit can be continuous over time.
+\item A subset of money units can also have their value functions depending on the same information in shared
+    context. This could enable payment primitives that involve many parties.
+\end{itemize}
+
+\subsubsection{Haskell Definitions}
 
@@
 \subsection{Money Medium Models}
+
+An attempt of creating a unifying theory for money and its distribution was made by Buldas, Saarepera et al.\cite{buldas2021unifying}
+
+\begin{displayquote}
+A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
+digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs, etc.
+\end{displayquote}
 

### 2022-09-22 packages/spec-haskell/yellowpaper/Paper.tex
subsection FILLED: payment primitives

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[a4paper]{report}
+\documentclass[a4paper,10pt]{report}
+
+%% \usepackage[margin=0.5in,nomarginpar]{geometry}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Payment System}
+%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Money Distribution Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{itemize}
-\item If time is included the shared context, then monetary value of each money unit can be continuous over time.
-\item A subset of money units can also have their value functions depending on the same information in shared
+\item If time is included the shared context, then monetary value of each monetary unit can be continuous over time.
+\item A subset of monetary units can also have their value functions depending on the same information in shared
     context. This could enable payment primitives that involve many parties.
@@
 
-\input{MoneyDistributionConcepts.tex}
+\input{MoneyDistribution.lhs.tex}
 
 \subsection{Payment Primitives}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Payment primitives are functions that takes a money distribution, shared context and some arbitrary arguments as inputs
+and an updated money distribution and shared context as outputs:
+
+\begin{minted}[escapeinside=||,mathescape=true]{haskell}
+    somePaymentPrimitive :: MoneyDistribution |$\otimes$| SharedContext
+                         -> Args
+                         -> MoneyDistribution |$\otimes$| SharedContext
+\end{minted}
+
+Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
+in the same money distribution.
+
+The best known primitive is instant transfer of monetary value between one monetary unit to another. Shared context
+enables more primitives to be defined, which will be introduced in later chapters.
 
 \subsection{Payment System Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsubsection{Discrete Payments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsubsection{Continuous Payments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Money Medium Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Relevant Approaches}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Constraint Programming}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Functional Reactive Programming}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Denotational Semantics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Denotational Semantics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Monoidial Payment Model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{Payment Premitives}
+\subsection{Payment Primitives}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Restatement in Haskell}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Type Of Money Units}
+\section{Type Of Monetary Units}
 

### 2022-09-22 packages/spec-haskell/yellowpaper/Paper.tex
subsection WIP: Payment Execution Environment Models

@@
 \item \textit{payment primitives} updates money distribution,
-\item \textit{financial system} provides the execution environment for the payment primitives,
+\item \textit{payment execution environment} performs payment primitives,
 \item and \textit{forms of money medium} are the "user interfaces" of money for the bearers.
@@
 
-\subsubsection{Haskell Definitions}
+\subsubsection{Haskell Definition Of Money Distribution}
 
@@
 
-Payment primitives are functions that takes a money distribution, shared context and some arbitrary arguments as inputs
+Payment primitives are functions that takes a money distribution, shared context and some payment instruction as inputs
 and an updated money distribution and shared context as outputs:
@@
     somePaymentPrimitive :: MoneyDistribution |$\otimes$| SharedContext
-                         -> Args
+                         -> PaymentInstruction
                          -> MoneyDistribution |$\otimes$| SharedContext
@@
 Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
-in the same money distribution.
+in the same money distribution; additionally primitives should be the only constructs in a payment system that can
+update money distribution.
 
@@
 
-\subsection{Payment System Models}
+\subsection{Payment Execution Environment Models}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{Discrete Payments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The purpose of a payment execution environment is to perform the actual payment primitives taking into account their
+conditions, timing and order.
 
-\subsubsection{Continuous Payments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Composing Financial Contracts}
+
+Inspired by the \textit{technique of composing financial contracts} demonstrated in \cite{peyton2000composing}, we first
+define a type class for financial contract:
+
+\input{FinancialContract.lhs.tex}
+
+And let $fcSet$ be the set of all financial contracts in the payment system.
+
+\subsubsection{Sequential Model of Execution Environment}
+
+A sequential execution environment model that can support conditional payment primitives\footnote{Timing is a type of
+condition of which current system time is a factor} then can be defined as follows:
+
+\begin{equation}
+    \begin{split}
+        [\![& \text{FS md fcSet t}]\!] = \sum_{x \in fcSet} ( \\
+        & \text{if fcPred md x t} \\
+        & \text{then fcExec x t} \\
+        & \text{else }\emptyset \\
+        )
+    \end{split}
+\end{equation}
+
+\subsubsection{Deterministic Execution Order}
+
+\subsubsection{Concurrency}
 
@@
 
-An attempt of creating a unifying theory for money and its distribution was made by Buldas, Saarepera et al.\cite{buldas2021unifying}
+An attempt of creating a unifying theory for money and its distribution was made by Buldas, Saarepera et
+al.\cite{buldas2021unifying}
 
@@
 A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
-digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs, etc.
+digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs, etc. \cite{buldas2021unifying}
 \end{displayquote}

### 2022-09-22 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes.hs

@@ -36,7 +36,7 @@ class (Default ts, Integral ts) => Timestamp ts
 -- Note:
 -- - Note the "6.4.9.7.1. Syntax of injectivity annotation"
 class ( SFTFloat (SFT_FLOAT sft)
-      , Typeable (SFT_MVAL sft), Value (SFT_MVAL sft)
+      , Typeable (SFT_MVAL sft), MonetaryValue (SFT_MVAL sft)
       , Timestamp (SFT_TS sft)
       , RealTimeBalance (SFT_RTB_F sft) (SFT_MVAL sft)
       ) => SuperfluidCoreTypes (sft :: Type) where

### 2022-09-22 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes/RealTimeBalance.hs

@@ -27,7 +27,7 @@ import           Money.Systems.Superfluid.CoreTypes.TypedValue
 -- [RTB's mappend commutativity] @x <> y@ = @y <> x@
 -- [RTB's identity to and from typed values] @(typedValuesToRTB . typedValuesFromRTB) x@ = @x@
 -- [RTB's conservation of net value] @(netValueOfRTB . valueToRTB . netValueOfRTB) v@ = @netValueOfRTB v@
-class ( Value v
+class ( MonetaryValue v
       , Foldable rtbF
       , Monoid (rtbF v)
       , Eq (rtbF v)

### 2022-09-22 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes/TypedValue.hs

@@ -14,7 +14,7 @@
 --   readily to be used by any 'sub-system'.
 --
 module Money.Systems.Superfluid.CoreTypes.TypedValue
-    ( Value
+    ( MonetaryValue
     , TypedValue (..)
     , UntappedValue (..)
     , AnyTypedValue (..)
@@ -26,14 +26,14 @@ import           Data.Coerce               (Coercible, coerce)
 import           Data.Default              (Default (..))
 import           Data.Typeable             (Proxy (..), Typeable)
 
-import           Money.Theory.Distribution (Value)
+import           Money.Theory.MoneyDistribution (MonetaryValue)
 
 
 -- | Typed value is an otherwise unaccounted value ~v~ with a type.
 --
 -- Notional conventions:
 --  * Type name: tv
-class (Typeable tv, Value v, Coercible tv v) => TypedValue tv v | tv -> v where
+class (Typeable tv, MonetaryValue mv, Coercible tv mv) => TypedValue tv mv | tv -> mv where
     -- | Get string representation of typed value tag.
     typedValueTag :: Proxy tv -> String
 
@@ -43,8 +43,8 @@ class (Typeable tv, Value v, Coercible tv v) => TypedValue tv v | tv -> v where
 -- Notional conventions:
 --  * Term name: uval
 newtype UntappedValue v = MkUntappedValue v
-    deriving newtype (Default, Enum, Num, Eq, Ord, Real, Integral, Value)
-instance (Typeable v, Value v) => TypedValue (UntappedValue v) v where typedValueTag _ = "_"
+    deriving newtype (Default, Enum, Num, Eq, Ord, Real, Integral, MonetaryValue)
+instance (Typeable v, MonetaryValue v) => TypedValue (UntappedValue v) v where typedValueTag _ = "_"
 
 -- | Any typed value.
 --

### 2022-09-22 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/MonetaryUnitData/MintedValue.hs

@@ -18,8 +18,8 @@ import           Money.Systems.Superfluid.SystemTypes
 --
 
 newtype MintedValue v = MkMintedValue v
-    deriving newtype (Default, Enum, Num, Eq, Ord, Real, Integral, Value)
-instance (Typeable v, Value v) => TypedValue (MintedValue v) v where typedValueTag _ = "b"
+    deriving newtype (Default, Enum, Num, Eq, Ord, Real, Integral, MonetaryValue)
+instance (Typeable v, MonetaryValue v) => TypedValue (MintedValue v) v where typedValueTag _ = "b"
 
 -- * Monetary unit data
 --

### 2022-09-22 packages/spec-haskell/packages/core/test/Money/Systems/Superfluid/TestTypes.hs

@@ -21,12 +21,8 @@ import           Test.QuickCheck
 import           Money.Systems.Superfluid.SystemTypes
 --
 import qualified Money.Systems.Superfluid.Agreements.ProportionalDistribution.ConstantFlowDistributionAgreement as CFDA
--- import qualified Money.Systems.Superfluid.Agreements.ProportionalDistribution.InstantDistributionAgreement      as IDA
 import qualified Money.Systems.Superfluid.Agreements.ProportionalDistributionIndex                              as PDIDX
 import qualified Money.Systems.Superfluid.Agreements.Universal.ConstantFlowAgreement                            as CFA
--- import qualified Money.Systems.Superfluid.Agreements.Universal.DecayingFlowAgreement                            as DFA
--- import qualified Money.Systems.Superfluid.Agreements.Universal.InstantTransferAgreement                         as ITA
--- import qualified Money.Systems.Superfluid.Agreements.Universal.MinterAgreement                                  as MINTA
 import qualified Money.Systems.Superfluid.MonetaryUnitData.ConstantFlow                                         as CFMUD
 import qualified Money.Systems.Superfluid.MonetaryUnitData.MintedValue                                          as MVMUD
 import qualified Money.Systems.Superfluid.SubSystems.BufferBasedSolvency                                        as BBS
@@ -43,7 +39,7 @@ instance Arbitrary T_Timestamp where
 -- * Value
 
 newtype T_MVal = T_MVal Integer
-    deriving newtype (Default, Eq, Enum, Real, Ord, Num, Integral, Value, Show, Arbitrary)
+    deriving newtype (Default, Eq, Enum, Real, Ord, Num, Integral, MonetaryValue, Show, Arbitrary)
 
 deriving instance Show (UntappedValue T_MVal)
 

### 2022-09-22 packages/spec-haskell/packages/simple/src/Money/Systems/Superfluid/Instances/Simple/Types.hs

@@ -89,7 +89,7 @@ import qualified Money.Systems.Superfluid.SubSystems.BufferBasedSolvency        
 --   - Name is a monicker of MakerDAO v1 WAD type.
 
 newtype Wad = Wad Integer
-    deriving newtype (Default, Eq, Enum, Real, Ord, Num, Integral, Binary, Value)
+    deriving newtype (Default, Eq, Enum, Real, Ord, Num, Integral, Binary, MonetaryValue)
 
 toWad :: (RealFrac a) => a -> Wad
 toWad x = Wad (round $ x * (10 ^ (18::Integer)))

### 2022-09-22 packages/spec-haskell/utils/lhs2tex.sh

@@ -10,6 +10,6 @@ TEX_FILE="$(basename $LHS_FILE)"
 {
     cat $1
 } | \
-    sed -e '/\s*--.*/d' | # quirk: fix for haskell comments
-    sed -e 's/\\begin{code}/\\begin{minted}{haskell}/g' -e 's/\\end{code}/\\end{minted}/g' | # quirk: fix for haskell code blocks
+    sed -e 's/\\begin{code}/\\begin{minted}{haskell}/g' \
+        -e 's/\\end{code}/\\end{minted}/g' | # quirk: fix for haskell code blocks
     cat

### 2022-09-23 packages/spec-haskell/yellowpaper/Paper.tex
WIP Payment Execution Environment Models

--- 2022-09-22 packages/spec-haskell/yellowpaper/Paper.tex
@@
 
-\subsubsection{Using Shared Context}
+\subsubsection{Using Context}
 
 But the discrete nature of the model does not provide the necessary element for us to add the desired properties to the
-payment system. Here we propose a modification that involves the usage of \textit{shared context (ctx for short)}:
+payment system. Here we propose a modification that involves the usage of \textit{context ($\gamma$)}:
 
@@
     \includegraphics[width=0.5\textwidth]{../assets/money-distribution-with-ctx.png}
-    \caption{Schematic representation of money distribution with shared context}
+    \caption{Schematic representation of money distribution with context}
     \label{fig:md-with-ctx}
@@
 
-Note that in this model, shared context can be updated independently while value functions of the same money
-distribution can produce different monetary values.
+Note that in this model, context can be updated independently while value functions of the same money distribution can
+produce different monetary values.
 
@@
 \begin{itemize}
-\item If time is included the shared context, then monetary value of each monetary unit can be continuous over time.
-\item A subset of monetary units can also have their value functions depending on the same information in shared
-    context. This could enable payment primitives that involve many parties.
+\item If time (t) is included the context, then monetary value of each monetary unit can be continuous over time. Time
+    is part of the physical reality, hence not changeable by the actors in the payment system.
+\item Any subset of monetary units can also have their value functions depending on the same information in
+    context. This could enable payment primitives that involve many parties. This set of information in context is
+    referred to as \textit{ctx :: SharedContext}, they can be changed over time by the actors in the payment system.
 \end{itemize}
 
-\subsubsection{Haskell Definitions}
+For the purpose of this paper, the model of context is: $\gamma = (t :: Timestamp) \oplus (ctx :: SharedContext)$.
+
+\subsubsection{Haskell Definition Of Money Distribution}
 
@@
 
-Payment primitives are functions that takes a money distribution, shared context and some arbitrary arguments as inputs
-and an updated money distribution and shared context as outputs:
+Payment primitives are functions that takes a money distribution, shared context, some payment instruction (args) and
+timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
+associative binary operation and an identity element. See \url{https://ncatlab.org/nlab/show/monoid}.} of money
+distribution and shared context as outputs:
 
 \begin{minted}[escapeinside=||,mathescape=true]{haskell}
-    somePaymentPrimitive :: MoneyDistribution |$\otimes$| SharedContext
-                         -> Args
-                         -> MoneyDistribution |$\otimes$| SharedContext
+    somePaymentPrimitive :: ( Timestamp t
+                            , MoneyDistribution md
+                            , SharedContext ctx
+                            , PaymentInstruction args
+                            , Monoid md, Monoid ctx
+                            )
+                         => md |$\otimes$| ctx -> args -> t -> md |$\otimes$| ctx
 \end{minted}
@@
 Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
-in the same money distribution.
+in the same money distribution; additionally primitives should be the only constructs in a payment system that can
+update money distribution.
 
-The best known primitive is instant transfer of monetary value between one monetary unit to another. Shared context
-enables more primitives to be defined, which will be introduced in later chapters.
+Updates are \textit{monoidal}, so that they can be incremental and their parallel executions can be modeled.
 
-\subsection{Payment System Models}
+The best known primitive is instant transfer of monetary value between one monetary unit to another. The introduction of
+context enables more primitives to be defined, and this will be discussed in later chapters.
+
+\subsection{Payment Execution Environment Models}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{Discrete Payments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Continuous Payments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{FinancialContract.lhs.tex}
 

### 2022-09-23 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes.hs

@@ -4,7 +4,6 @@ module Money.Systems.Superfluid.CoreTypes
     ( module Money.Systems.Superfluid.CoreTypes.TypedValue
     , module Money.Systems.Superfluid.CoreTypes.RealTimeBalance
     , SFTFloat
-    , Timestamp
     , RealTimeBalance (..)
     , SuperfluidCoreTypes (..)
     , SFT_RTB
@@ -21,13 +20,6 @@ import           Money.Systems.Superfluid.CoreTypes.TypedValue
 -- | Superfluid float type. TODO naming?
 class (Default fr, RealFloat fr) => SFTFloat fr
 
--- | Timestamp type class.
---
--- Notional conventions:
---  * Type name: ts
---  * SuperfluidTypes type indexer: SFT_TS
-class (Default ts, Integral ts) => Timestamp ts
-
 -- | Superfluid core types as associated type synonyms.
 --
 -- Notional conventions:
@@ -40,9 +32,9 @@ class ( SFTFloat (SFT_FLOAT sft)
       , Timestamp (SFT_TS sft)
       , RealTimeBalance (SFT_RTB_F sft) (SFT_MVAL sft)
       ) => SuperfluidCoreTypes (sft :: Type) where
-    type family SFT_FLOAT sft = (sft_float :: Type)         | sft_float -> sft
-    type family SFT_MVAL  sft = (sft_mval  :: Type)         | sft_mval  -> sft
-    type family SFT_TS    sft = (sft_ts    :: Type)         | sft_ts    -> sft
-    type family SFT_RTB_F sft = (sft_rtbF  :: Type -> Type) | sft_rtbF  -> sft
+    type family SFT_FLOAT sft = (float :: Type)         | float -> sft
+    type family SFT_MVAL  sft = (mval  :: Type)         | mval  -> sft
+    type family SFT_TS    sft = (t     :: Type)         | t     -> sft
+    type family SFT_RTB_F sft = (rtbF  :: Type -> Type) | rtbF  -> sft
 
 type SFT_RTB sft = SFT_RTB_F sft (SFT_MVAL sft)

### 2022-09-23 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes/TypedValue.hs

@@ -14,7 +14,8 @@
 --   readily to be used by any 'sub-system'.
 --
 module Money.Systems.Superfluid.CoreTypes.TypedValue
-    ( MonetaryValue
+    ( Timestamp
+    , MonetaryValue
     , TypedValue (..)
     , UntappedValue (..)
     , AnyTypedValue (..)
@@ -26,7 +27,7 @@ import           Data.Coerce               (Coercible, coerce)
 import           Data.Default              (Default (..))
 import           Data.Typeable             (Proxy (..), Typeable)
 
-import           Money.Theory.MoneyDistribution (MonetaryValue)
+import           Money.Theory.MoneyDistribution (Timestamp, MonetaryValue)
 
 
 -- | Typed value is an otherwise unaccounted value ~v~ with a type.

### 2022-09-26 packages/spec-haskell/yellowpaper/Paper.tex
[WIP] still in Payment Execution Environment sub section

@@
 %% Import Packages
+\usepackage{hyperref}
 \usepackage{fvextra}
@@
 \long\def\ignore#1{}
-%%% for creating a paragraph
-\newcommand{\lhsparagraph}[1]{\paragraph{#1}\mbox{}\\}
+%%% for code
+\newminted[code]{haskell}{}
+\newminted[spec]{haskell}{}
 
@@
 
-\subsection{Money Distribution Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Money Distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-This discrete nature of this money distribution model is schematically depicted in {\ref{fig:discrete-md}}:
+This discrete nature of this money distribution model is schematically depicted in \ref{fig:discrete-md}:
 
@@
 timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
-associative binary operation and an identity element. See \url{https://ncatlab.org/nlab/show/monoid}.} of money
+associative binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid. } of money
 distribution and shared context as outputs:
@@
 
-\subsection{Payment Execution Environment Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Payment Execution Environment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The purpose of a payment execution environment is to perform the actual payment primitives taking into account their
+conditions, timing and order.
+
+It is out of scope for this paper to survey in-depth the problem space of the operation semantics of payment execution
+environments. Nonetheless, a simplified model and some potential extensions to it is discussed briefly.
+
+\subsubsection{Composing Financial Contracts}
 
 \input{FinancialContract.lhs.tex}
+
+\subsubsection{Simplified Execution Environment Models}
+
+\input{PaymentExecutionEnvironment.lhs.tex}
 

### 2022-09-26 packages/spec-haskell/utils/lhs2tex.sh

@@ -1,15 +1,20 @@
 #!/bin/sh
 
-cd "$(dirname "$0")"/..
-
-LHS_FILE=$1
+LHS_FILE=$(readlink -f "$1")
 [ -f "$LHS_FILE" ] || exit 1
 
-TEX_FILE="$(basename $LHS_FILE)"
+cd "$(dirname "$0")"/..
 
 {
     cat $1
-} | \
-    sed -e 's/\\begin{code}/\\begin{minted}{haskell}/g' \
-        -e 's/\\end{code}/\\end{minted}/g' | # quirk: fix for haskell code blocks
-    cat
+} | awk '
+    # process haddock documentation
+    /\\begin{haddock}/ { h = 1; next }
+    /\\end{haddock}/   { h = 0; next }
+    /\\begin{code}/    { if (h) next }
+    /\\end{code}/      { if (h) next }
+    /^{-/  { if (h) next }
+    /^-}/  { if (h) next }
+    /^--}/ { if (h) next }
+    { print $0 }
+' | cat

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
concluide draft of Payment Execution Environment

@@
 
-\paragraph{}
+\paragraph{Payment system}
 
-A payment system can be solely defined by these components:
+It can be solely defined by these components:
 
@@
 
-\paragraph{}
+\paragraph{Modernization}
 
@@
 
-\paragraph{}
+\paragraph{Components of Context}
 
-Here are some examples how that could work:
+Here are some possible components of context, and how they work:
 
@@
 
-The purpose of a payment execution environment is to perform the actual payment primitives taking into account their
-conditions, timing and order.
+The purpose of a payment execution environment is to perform the actual payment primitives, where their computation
+interface, parallel evaluation strategies and payment system solvency are defined.
 
@@
 
+\subsection{Payment System Solvency}
+
 \subsection{Money Medium Models}
@@
 A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
-digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs, etc. \cite{buldas2021unifying}
+digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
+etc. \cite{buldas2021unifying}
 \end{displayquote}

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
added Payment System Solvency subsection

@@
 
+While money distribution does not assign meaning to the range of monetary values, in real world applications, negative
+values can have special meanings. In the following analysis, we call any money unit that has a negative monetary value
+insolvent.
+
+The detailed analysis of these solvency models are out of scope for this paper.
+
+\paragraph{Buffer Based Solvency Treatment}
+
+In a nondeterministic execution environment, we cannot determine when any financial contract will actually be
+executed. That means, there is always a chance a monetary unit could reach negative monetary value.
+
+To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value which is set aside in a solvency conditional financial contract, such that if a solvency
+condition arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the execution.
+
+\paragraph{Deterministic Solvency Treatment}
+
+Since \textit{fcNext} returns what is the next financial contract executable at a specific time, this deterministic
+property eliminates the need for the buffer.
+
+But it introduces a different type of systemic risk, that is denial-of-service, since the system cannot advance the
+system time until all next executable contracts are executed.
+
 \subsection{Money Medium Models}

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
subsection Money Mediums!!

@@
 
-Here we present a formal definition of payment system and its components.
+Here we present a definition of payment system and its components.
 
@@
 
-\subsection{Money Medium Models}
+\subsection{Money Mediums}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-An attempt of creating a unifying theory for money and its distribution was made by Buldas, Saarepera et
-al.\cite{buldas2021unifying}
 
@@
 digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
-etc. \cite{buldas2021unifying}
+etc. \footfullcite[][P3]{buldas2021unifying}
 \end{displayquote}
+
+We call these money mediums. And we further separate them into two big groups:
+
+\begin{itemize}
+\item \textit{Token and Its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
+    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
+    token.
+\item \textit{Note} - E.g. federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
+    independent of the notes, but it needs notes to complete the execution of financial contracts.
+\end{itemize}
+
+One of the main differences is from the ``user interface'' perspective. A bearer expects to keep many notes at hand,
+while maybe only needs a few accounts for each token. Also it is up to bearers to keep track of all their notes, while
+token can keep track of most of the states for bearers; hence notes are more decentralized and tokens are more
+centralized. Some also argue note-like model is better for complex concurrent and distributed computing environment
+\footfullcite[][P2]{chakravarty2020extended}.
+
+\subsubsection{Haskell Definition Of Money Mediums}
+
+\input{MoneyMedium.lhs.tex}
 
@@
 
+\section{Complexity Argument}
+
 \section{Restatement in Agda and Correctness Proof}

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
section relevant approaches WIP

@@
 \usepackage{graphicx}
+
+%% Formattings
+
+\renewcommand{\mkbegdispquote}[2]{\itshape}
 
@@
     \begin{center}
-        (Some distant lyrics as the placeholder of the actual abstract)
+        (Some distant lyrics as the placeholder for the actual abstract)
 
@@
 
-\begin{quotation}
+\begin{displayquote}
 The function of money is to facilitate the business of the market by acting as a common medium of
 exchange. \footfullcite[][Chapter One, Chapter I, § 1, p1]{von2013theory}
-\end{quotation}
+\end{displayquote}
 
@@
 This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
-can perform its function of medium of exchange using computer science.
+can perform its function of medium of exchange.
 
@@
 
-We call these money mediums. And we further separate them into two big groups:
+We call them money mediums, and we further separate them into two big groups:
 
 \begin{itemize}
-\item \textit{Token and Its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
+\item \textit{Token and its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
     environment, bearers access their monetary value through their accounts, and execute financial contracts through the
@@
 
-\subsection{Constraint Programming}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The focus of this paper is to formally define a set of payment primitives that modernize our payment systems. To prevent
+reinventing wheels, it is relevant to discuss first some approaches in computer science that are believed to help
+solving this challenge.
 
@@
 
+Recall that we want our modernized payment system to handle money distribution continuously over time, and its financial
+contracts compositional. A very closely related software design paradigm best known to address those needs is
+\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving multimedia
+animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
+\cite{wan2000functional} making FRP a more general framework for programming hybrid system with continuous behaviors in
+a high-level, declarative manner.
+
+After FRP got more adoption, it evolved to some variations that support discrete semantics, and some variations better
+suited more for interactive systems. In this paper we will stick to and revisit the original formulation use in
+\cite{elliott1997functional} where we will draw inspirations from.
+
+... TODO
+
 \subsection{Denotational Semantics}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We also want a formal and precise specification of payment primitives. The title of the paper mentions denotational
+semantics, it is a \textit{compositional} style for precisely specifying the meanings of languages, invented by
+Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward}). Conal Elliott proposed that denotational
+semantics can also be applied to \textit{data types} in programming \footfullcite[][section 2, denotational semantics
+    and data types]{Elliott2009-type-class-morphisms-TR}. We will revisit this formulation too.
+
+... TODO
 

### 2022-09-28 packages/spec-haskell/yellowpaper/Paper.tex
subsection Functional Reactive Programming drafted

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Document Preamble
+%% Document Setup
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[a4paper,10pt]{report}
-
-%% \usepackage[margin=0.5in,nomarginpar]{geometry}
-
-%% Base Folder for Inputs
+%%% This document is processed in an isolated clean folder at the same level.
 \makeatletter
@@
 \makeatother
+%%% Include the preamble at choice during processing.
+\input{preamble.tex}
+%%% Bibliography system setup using biblatex.
+\usepackage[
+    backend=biber,
+    style=alphabetic,
+]{biblatex}
+\addbibresource{../tex/Biblio.bib}
+%%% Macros used.
+\long\def\ignore#1{} % for ignoring some code
+\newcommand{\eg}{\textit{e}.\textit{g}.}
+\newcommand{\ie}{\textit{i}.\textit{e}.}
+\newcommand{\etal}{\textit{et al}.}
 
-%% Import Packages
-\usepackage{hyperref}
-\usepackage{fvextra}
-\usepackage{csquotes}
-\usepackage{xcolor}
-\usepackage{minted}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{enumitem}
-\usepackage{graphicx}
-
-%% Formattings
-
-\renewcommand{\mkbegdispquote}[2]{\itshape}
-
-%% Literate Haskell Macros
-
-%%% include common formatting
-\input{lhsfmt.tex}
-%%% for ignoring some code
-\long\def\ignore#1{}
-%%% for code
-\newminted[code]{haskell}{}
-\newminted[spec]{haskell}{}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% Document Meta Data
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 }
-
-\usepackage[
-    backend=biber,
-    style=alphabetic,
-]{biblatex}
-\addbibresource{../tex/Biblio.bib}
 
@@
     $\mathbb{N}$ is the set of all natural numbers, but instead, we can use any set of numerals that is totally ordered
-    (e.g.\ integers, real numbers).
+    (\eg\ integers, real numbers).
 \item $\beta : U \rightarrow \mathfrak{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
@@
                             )
-                         => md |$\otimes$| ctx -> args -> t -> md |$\otimes$| ctx
+                         => md |$\times$| ctx -> args -> t -> md |$\times$| ctx
 \end{minted}
@@
 \begin{itemize}
-\item \textit{Token and its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
+\item \textit{Token and its Accounts} - \eg\ bank currency accounts. Each token is its own centralized execution
     environment, bearers access their monetary value through their accounts, and execute financial contracts through the
     token.
-\item \textit{Note} - E.g. federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
+\item \textit{Note} - \eg\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
     independent of the notes, but it needs notes to complete the execution of financial contracts.
@@
 contracts compositional. A very closely related software design paradigm best known to address those needs is
-\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving multimedia
-animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
+\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving
+multimedia animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
 \cite{wan2000functional} making FRP a more general framework for programming hybrid system with continuous behaviors in
@@
 After FRP got more adoption, it evolved to some variations that support discrete semantics, and some variations better
-suited more for interactive systems. In this paper we will stick to and revisit the original formulation use in
-\cite{elliott1997functional} where we will draw inspirations from.
+suited more for interactive systems. In this paper we will stick to and revisit the basic constructions of the original
+formulation used in \cite{elliott1997functional} where we will draw inspirations from.
 
-... TODO
+\paragraph{Temporal Modeling and Behaviors}
+
+Values that vary over continuous time are called \textit{behaviors}. They are first-class values, and are built up
+compositionally. In modern payment systems, we should want the monetary values of monetary units capable of varying over
+continuous time. The semantic function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given
+time:
+
+\begin{equation}
+    at : Behavior_{\alpha} \rightarrow Time \rightarrow \alpha
+\end{equation}
+
+\paragraph{Event Modeling}
+
+Like behaviors, \textit{events} are first-class values too. The semantic function of $\alpha$-event describes the time and
+information associated with an \textit{occurrence} of the event:
+
+\begin{equation}
+    occ : Event_{\alpha} \rightarrow Time \times \alpha
+\end{equation}
+
+In modern payment systems, the payment primitives executed in payment execution environments are one type of
+events. More types of events can be read from the original paper \footfullcite[][section 2.3 Semantics of
+    Events]{elliott1997functional}.
+
+\paragraph{Reactivity}
+
+They key to modeling the payment execution environment using FRP is the \textit{reactivity}, which makes behaviors
+reactive. Specifically, the behavior \textit{b untilB e} exhibits b's behavior until \textit{e} occurs, and then swiches
+to a new behavior encoded in \textit{e}:
+
+\begin{equation}
+    \begin{split}
+    &untilB : Behavior_{\alpha} \rightarrow Event_{Behavior_{\alpha}} \rightarrow Behavior_{\alpha} \\
+    &at\ [\![b\ until\ B]\!]\ t = if\ t\ \leq\ t_{e}\ then\ at\ [\![b]\!]\ t\ else\ at\ [\![b']\!]\ t \\
+    &\qquad where (t_e, b') = occ[\![e]\!]
+    \end{split}
+\end{equation}
+
+Note that $[\![.]\!]$ is the denotational semantics notation to be introduced later.
+
+In the context of modern payment systems, the occurrences of payment primitives (events) change the behaviors of
+monetary units in how much monetary values it has over continuous. The building blocks of the financial contracts should
+be about modeling these events and their reactivity declaratively.
 
@@
 
-We also want a formal and precise specification of payment primitives. The title of the paper mentions denotational
-semantics, it is a \textit{compositional} style for precisely specifying the meanings of languages, invented by
-Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward}). Conal Elliott proposed that denotational
-semantics can also be applied to \textit{data types} in programming \footfullcite[][section 2, denotational semantics
-    and data types]{Elliott2009-type-class-morphisms-TR}. We will revisit this formulation too.
+We also want a formal and precise specification of payment primitives. The title of the paper contains
+\textit{denotational semantics}: ``it is a \textit{compositional} style for precisely specifying the meanings of
+languages, invented by Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward})'', and Conal Elliott
+proposed that denotational semantics can also be applied to \textit{data types} in programming \footfullcite[][section
+    2, denotational semantics and data types]{Elliott2009-type-class-morphisms-TR}. We will revisit this formulation
+too.
 
@@
 
-\section{Complexity Argument}
-
 \section{Restatement in Agda and Correctness Proof}
-
-\section{Constraint in Consensus}
 

### 2022-09-28 packages/spec-haskell/yellowpaper/Paper.tex
section Relevant Approaches  done!

@@
     (\eg\ integers, real numbers).
-\item $\beta : U \rightarrow \mathfrak{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
-    $\mathfrak{B}$ is the set of possible bearers. The bearer is usually a legal construction defining any type of legal
+\item $\beta : U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
+    $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal construction defining any type of legal
     entity, such as a person, a family, a company, a state institution, etc.
@@
 
-Recall that we want our modernized payment system to handle money distribution continuously over time, and its financial
+Recall that we want our modernized payment systems to handle money distribution continuously over time, and its financial
 contracts compositional. A very closely related software design paradigm best known to address those needs is
@@
 Values that vary over continuous time are called \textit{behaviors}. They are first-class values, and are built up
-compositionally. In modern payment systems, we should want the monetary values of monetary units capable of varying over
+compositionally. In modernized payment systems, we should want the monetary values of monetary units capable of varying over
 continuous time. The semantic function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given
@@
 
-In modern payment systems, the payment primitives executed in payment execution environments are one type of
+In modernized payment systems, the payment primitives executed in payment execution environments are one type of
 events. More types of events can be read from the original paper \footfullcite[][section 2.3 Semantics of
@@
 
-In the context of modern payment systems, the occurrences of payment primitives (events) change the behaviors of
+In the context of modernized payment systems, the occurrences of payment primitives (events) change the behaviors of
 monetary units in how much monetary values it has over continuous. The building blocks of the financial contracts should
@@
 
-We also want a formal and precise specification of payment primitives. The title of the paper contains
+We also want a formal and precise specification of payment primitives. The title of the paper includes
 \textit{denotational semantics}: ``it is a \textit{compositional} style for precisely specifying the meanings of
 languages, invented by Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward})'', and Conal Elliott
-proposed that denotational semantics can also be applied to \textit{data types} in programming \footfullcite[][section
-    2, denotational semantics and data types]{Elliott2009-type-class-morphisms-TR}. We will revisit this formulation
-too.
+proposed that denotational semantics can also be applied to \textit{data types within a programming language}
+\footfullcite[][section 2, denotational semantics and data types]{Elliott2009-type-class-morphisms-TR}.
 
-... TODO
+To create denotational semantics for each syntactic category $\mathcal{C}$, we should specify:
+
+\begin{itemize}
+\item a mathematical model $[\![\mathcal{C}]\!]$ of meanings, and
+\item a semantic function $[\![.]\!]_{\mathcal{C}} :: \mathcal{C} \rightarrow [\![\mathcal{C}]\!]$.
+\end{itemize}
+
+The syntactic category we are interested in is \textit{payment primitives}, which we should treat them as FRP-style
+\textit{Behavior} data types. In the following chapters, it is also unambiguously referred to in short as
+$[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie must be defined by structural recursion.
+
+It is important to note that our purpose of using the denotational semantics is to give precise meaning to payment
+primitives, independent of its implementation (which deals with performance, optimization, side effects, etc.). We will
+spend the next chapter exploring the denotational semantics for general payment primitives in modernized payment
+systems.
 

### 2022-09-29 packages/spec-haskell/yellowpaper/Paper.tex
Denotational Semantics WIP!

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Document Setup
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% This document is processed in an isolated clean folder at the same level.
-\makeatletter
-\def\input@path{{../tex/}}
-\makeatother
-%%% Include the preamble at choice during processing.
+%% Include a preamble at choice during processing.
 \input{preamble.tex}
-%%% Bibliography system setup using biblatex.
-\usepackage[
-    backend=biber,
-    style=alphabetic,
-]{biblatex}
-\addbibresource{../tex/Biblio.bib}
-%%% Macros used.
-\long\def\ignore#1{} % for ignoring some code
-\newcommand{\eg}{\textit{e}.\textit{g}.}
-\newcommand{\ie}{\textit{i}.\textit{e}.}
-\newcommand{\etal}{\textit{et al}.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Document Meta Data
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
 
@@
     Miao, ZhiCheng\\
-    Co-Founder, Superfluid Finance\\
+    Co-founder, Superfluid Finance\\
     miao@superfluid.finance
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Document Body
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Title Page
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \maketitle
@@
 
-This discrete nature of this money distribution model is schematically depicted in \ref{fig:discrete-md}:
+This discrete nature of this money distribution model is schematically depicted in~\ref{fig:discrete-md}:
 
@@
 \begin{itemize}
-\item If time (t) is included the context, then monetary value of each monetary unit can be continuous over time. Time
-    is part of the physical reality, hence not changeable by the actors in the payment system.
+\item If time (t) is included the context, then monetary value of each monetary unit can vary continuously over
+    time. Time is part of the physical reality, hence not changeable by the actors in the payment system.
 \item Any subset of monetary units can also have their value functions depending on the same information in
@@
 
+The set of payment primitives supported in a payment system is general, if monetary value of each monetary unit can vary
+continuously over time and monetary values can logically be shifted between two or more monetary units. The extent of
+the generality of each payment system may vary. We introduce a set of payment primitives that is general and serves as a
+starting point for the readers to explore the space of modern payment system. The specifications will be formally
+defined using denotational semantics, and its restatement in Haskell is also applied as a constructive artifact friendly
+to computer environment\footnote{One may argue for a restatement in \textit{Agda} instead, for it has a richer
+dependently-type system for needed constructive proofs. This matter will be dealt in the ``future investigations'' chapter
+of this paper.}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Here is the specification of denotational semantics that support both discrete and continous payments.
-
-Here is the list of acronyms used:
+Here is the convention for symbols used in the formulas:
 
 \begin{itemize}
-    \item \textbf{MD} is \textit{Money Distribution}.
-    \item \textbf{MU} is \textit{Monetary Unit}.
-    \item \textbf{RTB} is \textit{Real Time Balance}.
+    \item \textbf{M} is \textit{money distribution}.
+    \item \textbf{U} is for \textit{the set of all money units in M}.
+    \item $\boldsymbol{\nu}$ is for \textit{monetary value}.
+    \item \textbf{t} is for \textit{time}.
+    \item \textbf{mu, ma, mb, etc.} are for \textit{monetary units}.
 \end{itemize}
 
-\subsection{Generalized Payment Model}
+\subsection{Money Distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{equation}\label{sem_transfer}
+Recall the definition of payment system previously, money distribution sits in the core of the system, and that is the
+syntactic category $\mathcal{M}$ we will be dealing with:
+
+\begin{itemize}
+\item The meaning of $[\![\mathcal{M}]\!]$ is money distribution.
+\item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ include payment primitives.
+\end{itemize}
+
+\paragraph{Model}
+
+This is the model for money distribution.
+
+\begin{equation}\label{md_model}
     \begin{split}
-        [\![MD\ mu\ t\ rtb]\!] = mu \rightarrow t \rightarrow rtb
+        [\![M\ mu\ t\ \nu]\!] &= mu \rightarrow t \rightarrow \nu \\
+        [\![.]\!] &= M\ mu\ t\ \nu \rightarrow (mu \rightarrow t \rightarrow \nu) \\
     \end{split}
@@
 
-\subsection{Monoidial Payment Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Monoidal}
 
-\begin{equation}\label{sem_mzero}
-    [\![\emptyset]\!] = \lambda\ mu\ t\ \rightarrow 0
+With this model, $\mathcal{M}$ is also monoidal, hence compositional.
+
+\begin{equation}
+    \begin{split}
+        [\![\emptyset]\!] &= \lambda mu \times t\ \rightarrow 0 \\
+        [\![ma \oplus mb]\!] &= \lambda mu \times t\ \rightarrow [\![ma]\!]\ mu\ t\ +\ [\![mb]\!]\ mu\ t \\
+    \end{split}
 \end{equation}
 
-\begin{equation}\label{sem_mappend}
-    [\![mda \oplus\ mdb]\!] = \lambda\ mu\ t\ \rightarrow
-    [\![mda]\!]\ mu\ t\ +\ [\![mdb]\!]\ mu\ t
+Knowing that function application category $a \rightarrow b$ is also monoidal:
+
+\begin{equation}
+    \begin{split}
+        \emptyset &= \lambda a \rightarrow \emptyset \\
+        f \oplus g &= \lambda a \rightarrow f\ a \oplus g\ a \\
+    \end{split}
+\end{equation}
+
+With some substitutions, we get the desired \textit{monoid homomorphism} property for $\mathcal{M}$.
+
+\begin{equation}
+    \begin{split}
+        [\![\emptyset]\!] &= \emptyset \\
+        [\![ma \oplus mb]\!] &= [\![ma]\!] \oplus [\![mb]\!] \\
+    \end{split}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A payment primitive \textit{prim} is a semantic function that produces a monoidal money distribution, semantically
+representing an ``update'' to a money distribution:
+
+\begin{equation}
+    [\![prim\ args]\!] = [\![M\ mu\ t\ \nu]\!]
+\end{equation}
+
+\paragraph{Law of Conservation of Value}
+
+First of all, money distribution must obey the \textit{law of conservation of value}:
+
+\begin{equation}
+    \forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t = 0}
+\end{equation}
+
+That is to say, for any given time, the sum of monetary value of all monetary units shall always equal to zero. Zero is
+used to keep the semantical meaning of payment system simple and elegant. In its applications, a payment system may use
+some special monetary unit accounting negative monetary values to accommodate concepts such as mining, minting, money
+printing, etc.
+
+Further more, in a payment system, we restrict that only payment primitives can provide ``updates'' to its money
+distribution. So a money distribution is a result of a sequence of payment primitive updates:
+
+\begin{equation}
+    \begin{split}
+        &\textbf{Axioms A:\ }
+        \textit{law of conservation of value for payment primitives} \\
+        &\forall t \in \mathbb{R} ({\displaystyle \sum_{mu \in U} [\![prim\ args]\!]\ mu\ t = 0}) \\
+        \\
+        &\textbf{Axioms B:\ }
+        \textit{money distribution consists of updates from payment primitives} \\
+        &[\![M\ mu\ t\ \nu]\!] =
+          [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
+    \end{split}
+\end{equation}
+
+This allows us impose the law of conservation of value on payment primitives, then prove the law for money
+distribution inductively using monoid homomorphism:
+
+\begin{equation}
+    \begin{split}
+        &\textbf{In addition to the axioms, given:} \\
+        \\
+        &\textit{(base case with empty money distribution is trivial)} \\
+        &\forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![\emptyset]\!]\ mu\ t = 0} \\
+        \\
+        &\textit{(monoid homomorphism)} \\
+        &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1\oplus prim_2\ args_2]\!]\ mu\ t} = \\
+        &\qquad {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
+          {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \\
+        \\
+        &\textbf{We have:} \\
+        &\forall t \in \mathbb{R}. \\
+        &{\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t} \\
+        &\textit{(applying Axioms B)} \\
+        = &{\displaystyle \sum_{mu \in U}
+            ([\![prim_1\ args_1]\!] \oplus
+            [\![prim_2\ args_2]\!] \oplus
+            [\![prim_3\ args_3]\!]\oplus \dotsb)
+        }\ mu\ t\\
+        &\textit{(applying monoid homomorphism)} \\
+        = &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1]\!]\ mu\ t} \oplus
+        {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
+        {\displaystyle \sum_{mu \in U} [\![prim_3\ args_3]\!]\ mu\ t} \oplus \dotsb
+        )\\
+        &\textit{(applying Axioms A)} \\
+        =&\ 0
+        \\
+        \blacksquare
+    \end{split}
+\end{equation}
+
+\subsection{One to One Payment Primitives}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+???
 
@@
 \end{equation}
+
+\subsection{Index Abstraction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Proportional Distribution Primitives}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Restatement in Agda and Correctness Proof}
+\section{Restatement in Agda, Correctness and Equivalence Proofs}
 

### 2022-09-29 packages/spec-haskell/yellowpaper/Paper.tex
added index abstraction semantics

@@
 
-The set of payment primitives supported in a payment system is general, if monetary value of each monetary unit can vary
-continuously over time and monetary values can logically be shifted between two or more monetary units. The extent of
-the generality of each payment system may vary. We introduce a set of payment primitives that is general and serves as a
-starting point for the readers to explore the space of modern payment system. The specifications will be formally
-defined using denotational semantics, and its restatement in Haskell is also applied as a constructive artifact friendly
-to computer environment\footnote{One may argue for a restatement in \textit{Agda} instead, for it has a richer
-dependently-type system for needed constructive proofs. This matter will be dealt in the ``future investigations'' chapter
-of this paper.}.
+The set of payment primitives supported in a payment system is general, if (a) monetary value of each monetary unit can
+vary continuously over time (b) monetary values can logically be shifted between two or more monetary units.
+
+The extent of the generality of each payment system may vary. This paper introduces a set of payment primitives that is
+general and serves as a starting point for the readers to explore the space of modern payment system.
+
+The specifications will be formally defined using denotational semantics, along with a restatement in Haskell also
+applied as a constructive artifact friendly to computer environment\footnote{One may argue for a restatement in
+\textit{Agda} instead, for it has a richer dependently-type system for desirable constructive proofs. This matter will
+be dealt in the ``future investigations'' chapter of this paper.}.
 
@@
 \begin{itemize}
-    \item \textbf{M} is \textit{money distribution}.
-    \item \textbf{U} is for \textit{the set of all money units in M}.
-    \item $\boldsymbol{\nu}$ is for \textit{monetary value}.
+\item \textbf{M} is the \textit{model for money distribution}.
+\item \textbf{m} is for \textit{money distributions}.
+\item \textbf{U} is the \textit{set of all money units} in money distribution.
+\item \textbf{u} is for \textit{monetary units}.
+\item $\boldsymbol{\nu}$ is for \textit{monetary values}.
 \item \textbf{t} is for \textit{time}.
-    \item \textbf{mu, ma, mb, etc.} are for \textit{monetary units}.
 \end{itemize}
@@
     \begin{split}
-        [\![M\ mu\ t\ \nu]\!] &= mu \rightarrow t \rightarrow \nu \\
-        [\![.]\!] &= M\ mu\ t\ \nu \rightarrow (mu \rightarrow t \rightarrow \nu) \\
+        [\![M\ u\ t\ \nu]\!] &= u \rightarrow t \rightarrow \nu \\
+        [\![.]\!] &= M\ u\ t\ \nu \rightarrow (u \rightarrow t \rightarrow \nu) \\
     \end{split}
@@
     \begin{split}
-        [\![\emptyset]\!] &= \lambda mu \times t\ \rightarrow 0 \\
-        [\![ma \oplus mb]\!] &= \lambda mu \times t\ \rightarrow [\![ma]\!]\ mu\ t\ +\ [\![mb]\!]\ mu\ t \\
+        [\![\emptyset]\!] &= \lambda u \rightarrow \lambda t\ \rightarrow \emptyset \\
+        [\![m_a \oplus m_b]\!] &= \lambda u \rightarrow \lambda t\ \rightarrow [\![m_a]\!]\ u\ t\ +\ [\![m_b]\!]\ u\ t \\
     \end{split}
@@
         [\![\emptyset]\!] &= \emptyset \\
-        [\![ma \oplus mb]\!] &= [\![ma]\!] \oplus [\![mb]\!] \\
+        [\![m_a \oplus m_b]\!] &= [\![m_a]\!] \oplus [\![m_b]\!] \\
     \end{split}
@@
 \begin{equation}
-    [\![prim\ args]\!] = [\![M\ mu\ t\ \nu]\!]
+    [\![prim\ args]\!] = [\![\Delta\ m]\!]
 \end{equation}
@@
 \begin{equation}
-    \forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t = 0}
+    \forall t \in \mathbb{R} {\displaystyle \sum_{u \in U} [\![m]\!]\ u\ t = 0}
 \end{equation}
 
-That is to say, for any given time, the sum of monetary value of all monetary units shall always equal to zero. Zero is
+That is to say, at any given time, the sum of monetary value of all monetary units shall always equal to zero. Zero is
 used to keep the semantical meaning of payment system simple and elegant. In its applications, a payment system may use
@@
 
-Further more, in a payment system, we restrict that only payment primitives can provide ``updates'' to its money
-distribution. So a money distribution is a result of a sequence of payment primitive updates:
+\paragraph{Restricted Money Distribution}
+
+To come up with such lawful money distribution, we can divide and conquer. In a payment system, if we restrict that only
+payment primitives can provide ``updates'' to its money distribution, so that a money distribution is only a result of a
+sequence of payment primitive updates; then we can have these axioms as the basis for the proof:
+
+\centerline{\textbf{Axioms of restricted money distributions}}
 
@@
     \begin{split}
-        &\textbf{Axioms A:\ }
+        &\textbf{Axiom A:\ }
         \textit{law of conservation of value for payment primitives} \\
-        &\forall t \in \mathbb{R} ({\displaystyle \sum_{mu \in U} [\![prim\ args]\!]\ mu\ t = 0}) \\
+        &\forall t \in \mathbb{R} ({\displaystyle \sum_{u \in U} [\![prim\ args]\!]\ u\ t = 0}) \\
         \\
-        &\textbf{Axioms B:\ }
+        &\textbf{Axiom B:\ }
         \textit{money distribution consists of updates from payment primitives} \\
-        &[\![M\ mu\ t\ \nu]\!] =
-          [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
+        &[\![m]\!] = [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
     \end{split}
@@
 
-This allows us impose the law of conservation of value on payment primitives, then prove the law for money
-distribution inductively using monoid homomorphism:
+This allows us to impose the law of conservation of value on payment primitives, then prove inductively that such
+restricted money distribution obey the law of conservation of value too.
+
+\centerline{\textbf{Proof of restricted money distributions satisfying the law of conservation of value}}
 
@@
         &\textit{(base case with empty money distribution is trivial)} \\
-        &\forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![\emptyset]\!]\ mu\ t = 0} \\
+        &\forall t \in \mathbb{R} {\displaystyle \sum_{u \in U} [\![\emptyset]\!]\ u\ t = 0} \\
         \\
         &\textit{(monoid homomorphism)} \\
-        &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1\oplus prim_2\ args_2]\!]\ mu\ t} = \\
-        &\qquad {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
-          {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \\
+        &{\displaystyle \sum_{u \in U} [\![prim_1\ args_1\oplus prim_2\ args_2]\!]\ u\ t} = \\
+        &\qquad {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \oplus
+          {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \\
         \\
@@
         &\forall t \in \mathbb{R}. \\
-        &{\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t} \\
+        &{\displaystyle \sum_{u \in U} [\![m]\!]\ u\ t} \\
         &\textit{(applying Axioms B)} \\
-        = &{\displaystyle \sum_{mu \in U}
+        = &{\displaystyle \sum_{u \in U}
             ([\![prim_1\ args_1]\!] \oplus
@@
             [\![prim_3\ args_3]\!]\oplus \dotsb)
-        }\ mu\ t\\
+        }\ u\ t\\
         &\textit{(applying monoid homomorphism)} \\
-        = &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1]\!]\ mu\ t} \oplus
-        {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
-        {\displaystyle \sum_{mu \in U} [\![prim_3\ args_3]\!]\ mu\ t} \oplus \dotsb
+        = &{\displaystyle \sum_{u \in U} [\![prim_1\ args_1]\!]\ u\ t} \oplus
+        {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \oplus
+        {\displaystyle \sum_{u \in U} [\![prim_3\ args_3]\!]\ u\ t} \oplus \dotsb
         )\\
@@
 
-???
+Here are the primitives involving a sender ($u_a$) and a receiver ($u_b$) (one to one payments).
 
-\begin{equation}\label{sem_transfer}
+\paragraph{Transfer}
+
+Instant transferring of a fixed amount of monetary value $x$:
+
+\begin{equation}
     \begin{split}
-        [\![&transfer\ from\ to\ amount\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ from = mu \rightarrow -amount \\
-        &|\ to   = mu \rightarrow amount \\
-        &|\ otherwise \rightarrow 0 \\
-        )
+        [\![transfer\ u_a\ u_b\ x]\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow \\
+        &\begin{cases}
+            -x & (u_a = u) \\
+             x & (u_b = u) \\
+             0 & (otherwise)
+        \end{cases}
     \end{split}
@@
 
-\begin{equation}\label{sem_updateConstantFlow}
+\paragraph{(Constant) Flow}
+
+Flowing of monetary value at a constant rate of $r$ at time $t'$:
+
+\begin{equation}
     \begin{split}
-        [\![&updateConstantFlow\ from\ to\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ from = mu \rightarrow -flowRate * (t - t') \\
-        &|\ to   = mu \rightarrow flowRate  * (t - t') \\
-        &|\ otherwise \rightarrow 0 \\
-        )
+        [\![flow\ u_a\ u_b\ r\ t']\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow \\
+        &\begin{cases}
+            -r \cdot (t - t') & (u_a = u) \\
+             r \cdot (t - t') & (u_b = u) \\
+                            0 & (otherwise)
+        \end{cases}
     \end{split}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To make primitives support more than two parties, we introduce an abstraction called \textit{index}.
+
+A \textit{index} has a function $\rho$ which produces a real number for each monetary unit:
+
+\begin{equation}
+    \rho :: k \rightarrow u \rightarrow \mathbb{R}
+\end{equation}
+
+And it must satisfy the following law:
+
+\begin{equation}
+    \displaystyle \sum_{u \in U} \rho\ u = 1
+\end{equation}
+
+Semantically, it represents a proportion of each money unit, and they must add up to 1.
+
+Now let's generalize the one to one payment primitives using index abstraction. We use symbol $k$ for the indexes, and
+$I$ subscript for the indexed versions of the primitives.
+
+\paragraph{Indexed Transfer}
+
+\begin{equation}
+    \begin{split}
+        [\![transfer_I\ k_a\ k_b\ x]\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow \\
+        &-x \cdot \rho\ k_a\ u + x \cdot \rho\ k_b\ u
+    \end{split}
+\end{equation}
+
+\paragraph{Indexed (Constant) Flow}
+
+\begin{equation}
+    \begin{split}
+        [\![flow_I\ k_a\ k_b\ r\ t']\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow \\
+        &-r \cdot (t - t') \cdot \rho\ k_a\ u + r \cdot (t - t') \cdot \rho\ k_b\ u
+    \end{split}
+\end{equation}
+
+\paragraph{Universal Index}
+
+Now one to one payment primitives can be redefined using \textit{universal index} ($ku_{any}$) define as such:
+
+\begin{equation}
+    \rho\ ku_{a} = \lambda u \rightarrow if\ u\ =\ u_a\ then\ 1\ else\ 0
+\end{equation}
+
+It means that it's an index universally available for any monetary unit, and its proportion is always 1 for that
+monetary unit.
 
@@
 \begin{equation}
-    proportion\ sub\ subs = {{ unit\ sub\ subs } \over { \displaystyle \sum_{x \in subs} unit\ x\ subs }}
+    proportion\ sub\ subs = {{unit\ sub\ subs } \over {\displaystyle \sum_{x \in subs} unit\ x\ subs}}
 \end{equation}
@@
         &|\ pub = mu \rightarrow -amount \\
-        &|\ \exists sub \in subs\ { sub = mu } \rightarrow amount * (proportion\ mu\ subs) \\
+        &|\ \exists sub \in subs\ {sub = mu } \rightarrow amount * (proportion\ mu\ subs) \\
         &|\ otherwise \rightarrow 0 \\
@@
         &|\ pub = mu \rightarrow -flowRate * (t - t') \\
-        &|\ \exists sub \in subs\ { sub = mu } \rightarrow flowRate * (t - t') * (proportion\ mu\ subs) \\
+        &|\ \exists sub \in subs\ {sub = mu } \rightarrow flowRate * (t - t') * (proportion\ mu\ subs) \\
         &|\ otherwise \rightarrow 0 \\

### 2022-09-30 packages/spec-haskell/yellowpaper/Paper.tex
complete (mostly) Denotational Semantics section

@@
 payment primitives can provide ``updates'' to its money distribution, so that a money distribution is only a result of a
-sequence of payment primitive updates; then we can have these axioms as the basis for the proof:
+sequence of payment primitive updates; then we can have these axioms as the basis for the proof.
 
-\centerline{\textbf{Axioms of restricted money distributions}}
+\paragraph{Axiom A of Restricted Money Distributions}
+
+First we must impose the law of conservation of value on payment primitives as an axiom, in order to prove inductively
+that such restricted money distribution satisfies the law of conservation of value too.
 
@@
     \begin{split}
-        &\textbf{Axiom A:\ }
-        \textit{law of conservation of value for payment primitives} \\
+        &\textit{law of conservation of value for payment primitives} \\
         &\forall t \in \mathbb{R} ({\displaystyle \sum_{u \in U} [\![prim\ args]\!]\ u\ t = 0}) \\
-        \\
-        &\textbf{Axiom B:\ }
-        \textit{money distribution consists of updates from payment primitives} \\
+    \end{split}
+\end{equation}
+
+\paragraph{Axiom B of Restricted Money Distributions}
+
+\begin{equation}
+    \begin{split}
+        &\textit{money distribution consists of updates from payment primitives} \\
         &[\![m]\!] = [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
@@
 
-This allows us to impose the law of conservation of value on payment primitives, then prove inductively that such
-restricted money distribution obey the law of conservation of value too.
+\paragraph{Proof of Restricted Money Distributions}
 
-\centerline{\textbf{Proof of restricted money distributions satisfying the law of conservation of value}}
+satisfying the law of conservation of value.
 
@@
         &{\displaystyle \sum_{u \in U} [\![m]\!]\ u\ t} \\
-        &\textit{(applying Axioms B)} \\
+        &\textit{(applying Axiom B)} \\
         = &{\displaystyle \sum_{u \in U}
@@
         )\\
-        &\textit{(applying Axioms A)} \\
+        &\textit{(applying Axiom A)} \\
         =&\ 0
@@
 
+It should be easy to prove that they satisfy the \textit{axioms A of restricted money distribution}.
+
 \subsection{Index Abstraction}
@@
 
-A \textit{index} has a function $\rho$ which produces a real number for each monetary unit:
+A \textit{index} (we use symbol $k$ for them) has a function $\rho$ which produces a real number for each monetary unit:
 
 \begin{equation}
-    \rho :: k \rightarrow u \rightarrow \mathbb{R}
+    \rho\ k :: u \rightarrow \mathbb{R}
 \end{equation}
@@
 \begin{equation}
-    \displaystyle \sum_{u \in U} \rho\ u = 1
+    \displaystyle \sum_{u \in U} \rho\ k\ u = 1
 \end{equation}
@@
 
-Now let's generalize the one to one payment primitives using index abstraction. We use symbol $k$ for the indexes, and
-$I$ subscript for the indexed versions of the primitives.
+\subsection{Indexed Primitives}
+
+Let's generalize the one to one payment primitives using index abstraction. We use $I$ subscript for the indexed
+versions of the primitives.
 
@@
 
+It should be straightforward to prove that they also satisfy the \textit{axiom A of restricted money distribution}
+thanks to the law of the index.
+
 \paragraph{Universal Index}
 
-Now one to one payment primitives can be redefined using \textit{universal index} ($ku_{any}$) define as such:
+Now one to one payment primitives can be redefined using \textit{universal index} ($ku_{any}$):
 
@@
 
-It means that it's an index universally available for any monetary unit, and its proportion is always 1 for that
-monetary unit.
+It means that it is an index \textit{universally} available for each monetary unit, and its proportion is always 1 for
+that monetary unit and 0 for all others.
 
@@
 
+A special case of the indexed primitives is to fix the sender side to be an \textit{universal index}.
+
+The semantics of these primitives resembles dividend pay out (distribution) in the security market\footnote{What Is a
+Dividend?  https://www.investopedia.com/terms/d/dividend.asp}. And flow semantics enables a whole new type of dividend
+pay out that is continuous over time.
+
+\subsection{Network Abstraction}
+
+An even more powerful abstraction is to model participants involved a payment primitive a \textit{network} (we use
+symbol $w$ for them).
+
+It has the function $\rho$ as in \textit{index}, bnd it satisfies a different law:
+
 \begin{equation}
-    unit :: sub \rightarrow subs \rightarrow Int
+    \displaystyle \sum_{u \in U} \rho\ w\ u = 0
 \end{equation}
 
+\subsection{Networked Primitives}
+
+Let's generalize the basic payment primitives using network abstraction. We use $N$ subscript for the indexed versions
+of the primitives.
+
+\paragraph{Shift}
+
+We rename $transfer$ to $shift$ for networked instant payment primitive:
+
 \begin{equation}
-    proportion\ sub\ subs = {{unit\ sub\ subs } \over {\displaystyle \sum_{x \in subs} unit\ x\ subs}}
-\end{equation}
-
-\begin{equation}\label{sem_distributeProportionally}
     \begin{split}
-        [\![&distributeProportionally\ pub\ subs\ amount\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ pub = mu \rightarrow -amount \\
-        &|\ \exists sub \in subs\ {sub = mu } \rightarrow amount * (proportion\ mu\ subs) \\
-        &|\ otherwise \rightarrow 0 \\
-        )
+        [\![shift_N\ w\ x]\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow x \cdot \rho\ w\ u
     \end{split}
@@
 
-\begin{equation}\label{sem_distributeProportionally}
+\paragraph{Networked (Constant) Flow}
+
+\begin{equation}
     \begin{split}
-        [\![&updateProportionalDistributionConstantFlow\ pub\ subs\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ pub = mu \rightarrow -flowRate * (t - t') \\
-        &|\ \exists sub \in subs\ {sub = mu } \rightarrow flowRate * (t - t') * (proportion\ mu\ subs) \\
-        &|\ otherwise \rightarrow 0 \\
-        )
+        [\![flow_N\ w\ r\ t']\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow r \cdot (t - t') \cdot \rho\ w\ u
     \end{split}
 \end{equation}
+
+\subsection{Generality vs. Optimization}
+
+The question now is, should we use the most general form of the semantics to guide implementation?
+
+The answer is most likely a no. Not because it is not useful, after all mathematical formula is about truth and perhaps
+also elegance in it, but because of we may miss optimization opportunities needed in implementation when more
+specialized versions are used instead\footnote{We will not though discuss the subjective aspects, including in software
+engineering principles such as YAGNI (\url{https://en.wikipedia.org/wiki/You_aren't_gonna_need_it}), or user experience
+perspective of the payment primitives.}.
+
+In the next chapter, we will look into a reference implementation where these optimizations are applied.
 

### 2022-10-01 packages/spec-haskell/yellowpaper/Paper1.tex
refine payment primitives texts

--- 2022-09-30 packages/spec-haskell/yellowpaper/Paper.tex
@@
 payment primitives. Along with the denotational semantics, a restatement\footnote{It is a borrowed term from common law:
-"restatement of the law". In our case, the denotative mathematical "laws".} of it in \textit{Haskell programming
+``restatement of the law''. In our case, the denotative mathematical laws.} of it in \textit{Haskell programming
     language} (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
@@
 \item \textit{payment execution environment} performs payment primitives,
-\item and \textit{forms of money medium} are the "user interfaces" of money for the bearers.
+\item and \textit{forms of money medium} are the ``user interfaces'' of money for the bearers.
 \end{itemize}
@@
 
-For the purpose of this paper, the model of context is: $\gamma = (t :: Timestamp) \oplus (ctx :: SharedContext)$.
+For the purpose of this paper, the model of context is: $\gamma = t \times ctx$.
 
@@
 
-Payment primitives are functions that takes a money distribution, shared context, some payment instruction (args) and
-timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
-associative binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid. } of money
-distribution and shared context as outputs:
+A payment primitive is a data type with a generator that creates payment primitive data from the shared context $ctx$,
+primitive specific argument $args$ and timestamp, along with an update of the shared context. Here is an example of
+generator for payment primitive \textit{a}:
 
-\begin{minted}[escapeinside=||,mathescape=true]{haskell}
-    somePaymentPrimitive :: ( Timestamp t
-                            , MoneyDistribution md
-                            , SharedContext ctx
-                            , PaymentInstruction args
-                            , Monoid md, Monoid ctx
-                            )
-                         => md |$\times$| ctx -> args -> t -> md |$\times$| ctx
-\end{minted}
+\begin{equation}
+    genPrim_a :: ctx \rightarrow args_a \rightarrow t \rightarrow prim \times ctx
+\end{equation}
+
+Payment primitive data then can be used to create a delta update of money distribution\footnote{Specifically being
+monoidal, that is in short a set that has associative binary operation and an identity element. See
+https://ncatlab.org/nlab/show/monoid.}
+
+\begin{equation}
+    runPrim :: prim \rightarrow md
+\end{equation}
 
@@
 The specifications will be formally defined using denotational semantics, along with a restatement in Haskell also
-applied as a constructive artifact friendly to computer environment\footnote{One may argue for a restatement in
-\textit{Agda} instead, for it has a richer dependently-type system for desirable constructive proofs. This matter will
-be dealt in the ``future investigations'' chapter of this paper.}.
+applied as a constructive artifact friendly to computer environment\footnote{One may argue for a restatement
+in \textit{Agda} instead, for it has a richer dependently-type system for desirable constructive proofs. This matter
+will be dealt in the ``future investigations'' chapter of this paper.}.
 
@@
 
-\subsection{Money Distribution}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{M}$ - Category of Money Distribution}
 
@@
 \begin{itemize}
-\item The meaning of $[\![\mathcal{M}]\!]$ is money distribution.
-\item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ include payment primitives.
+\item The meaning of the mathematical \textit{model} $[\![\mathcal{M}]\!]$ is money distribution.
+\item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ evaluates the syntax of money
+      distribution, payment primitives, etc.
 \end{itemize}
+
+\subsection{Money Distribution}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-A payment primitive \textit{prim} is a semantic function that produces a monoidal money distribution, semantically
+A payment primitive \textit{prim} is a model that produces a monoidal money distribution, semantically
 representing an ``update'' to a money distribution:
@@
 \begin{equation}
-    [\![prim\ args]\!] = [\![\Delta\ m]\!]
+    [\![prim]\!] = [\![\Delta\ m]\!]
 \end{equation}
@@
         &\textit{law of conservation of value for payment primitives} \\
-        &\forall t \in \mathbb{R} ({\displaystyle \sum_{u \in U} [\![prim\ args]\!]\ u\ t = 0}) \\
+        &\forall t \in \mathbb{R} ({\displaystyle \sum_{u \in U} [\![prim]\!]\ u\ t = 0}) \\
     \end{split}
@@
         &\textit{money distribution consists of updates from payment primitives} \\
-        &[\![m]\!] = [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
+        &[\![m]\!] = [\![prim_1]\!] \oplus [\![prim_2]\!] \oplus [\![prim_3]\!] \oplus \dotsb
     \end{split}
@@
         &\textit{(monoid homomorphism)} \\
-        &{\displaystyle \sum_{u \in U} [\![prim_1\ args_1\oplus prim_2\ args_2]\!]\ u\ t} = \\
-        &\qquad {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \oplus
-          {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \\
+        &{\displaystyle \sum_{u \in U} [\![prim_1 \oplus prim_2]\!]\ u\ t} =
+          {\displaystyle \sum_{u \in U} [\![prim_2]\!]\ u\ t} \oplus
+          {\displaystyle \sum_{u \in U} [\![prim_2]\!]\ u\ t} \\
         \\
@@
         = &{\displaystyle \sum_{u \in U}
-            ([\![prim_1\ args_1]\!] \oplus
-            [\![prim_2\ args_2]\!] \oplus
-            [\![prim_3\ args_3]\!]\oplus \dotsb)
-        }\ u\ t\\
+            ([\![prim_1]\!] \oplus
+            [\![prim_2]\!] \oplus
+            [\![prim_3]\!]\oplus \dotsb)
+        }\ u\ t
+        \\
         &\textit{(applying monoid homomorphism)} \\
-        = &{\displaystyle \sum_{u \in U} [\![prim_1\ args_1]\!]\ u\ t} \oplus
-        {\displaystyle \sum_{u \in U} [\![prim_2\ args_2]\!]\ u\ t} \oplus
-        {\displaystyle \sum_{u \in U} [\![prim_3\ args_3]\!]\ u\ t} \oplus \dotsb
-        )\\
+        = &{\displaystyle \sum_{u \in U} [\![prim_1]\!]\ u\ t} \oplus
+        {\displaystyle \sum_{u \in U} [\![prim_2]\!]\ u\ t} \oplus
+        {\displaystyle \sum_{u \in U} [\![prim_3]\!]\ u\ t} \oplus \dotsb
+        \\
         &\textit{(applying Axiom A)} \\
@@
 
-The semantics of these primitives resembles dividend pay out (distribution) in the security market\footnote{What Is a
-Dividend?  https://www.investopedia.com/terms/d/dividend.asp}. And flow semantics enables a whole new type of dividend
-pay out that is continuous over time.
-
 \subsection{Network Abstraction}
@@
 
+\input{PaymentPrimitives.lhs.tex}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Sub Systems}
+\section{Agreement Framework}
 
-\section{Agreement Sub System}
+\section{Hierarchy of Agreements}
 
-\section{Type of Agreements}
-
-\subsection{Transferable Balance Agreement}
+\subsection{Instant Transferable Agreement}
 
@@
 \subsection{Decaying Flow Agreement}
-
-\section{Solvency Sub Systems}
-
-\subsection{Buffer Based Solvency Systems}
-
-\section{Type Of Monetary Units}
 

### 2022-10-01 packages/spec-haskell/yellowpaper/Paper1.tex
realign to different number of chars per line

@@
+%%% -- -*- fill-column: 100; -*-
+
 %% Include a preamble at choice during processing.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% Title Page
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-It should be fair to say, every aspect of money are controversial: the nature of money, the value of money, money and
-banking, and monetary reconstruction. Two major schools of thoughts about theory of money are the \textit{Austrian
-    school} (\cite{von2013theory}) and the \textit{Chicago school} (\cite{friedman1989quantity}). That is before the
-appearance of Internet-era version of monetary reconstruction, broadly defined as cryptocurrency, which challenges
-theories of money further and demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
+It should be fair to say, every aspect of money are controversial: the nature of money, the value of
+money, money and banking, and monetary reconstruction. Two major schools of thoughts about theory of
+money are the \textit{Austrian school} (\cite{von2013theory}) and the \textit{Chicago school}
+(\cite{friedman1989quantity}). That is before the appearance of Internet-era version of monetary
+reconstruction, broadly defined as cryptocurrency, which challenges theories of money further and
+demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
 
-This yellow paper does not intend to address these controversies, but to focus on the function of money. According to
-Von Mises:
+This yellow paper does not intend to address these controversies, but to focus on the function of
+money. According to Von Mises:
 
@@
 
-How do different forms of money perform this function, especially in the information age, when electronic forms of money
-are increasingly used?
+How do different forms of money perform this function, especially in the information age, when
+electronic forms of money are increasingly used?
 
-This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
-can perform its function of medium of exchange.
+This paper adds a new controversy to money, that is to present a survey challenging the preconceived
+notion of how money can perform its function of medium of exchange.
 
-In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal definition of payment
-system and its components. We then select a few relevant approaches used in computer science useful for modeling and
-defining formal specification for the payment system.
+In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal
+definition of payment system and its components. We then select a few relevant approaches used in
+computer science useful for modeling and defining formal specification for the payment system.
 
-One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to define the general
-payment primitives. Along with the denotational semantics, a restatement\footnote{It is a borrowed term from common law:
-``restatement of the law''. In our case, the denotative mathematical laws.} of it in \textit{Haskell programming
-    language} (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
+One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to
+define the general payment primitives. Along with the denotational semantics, a
+restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our case,
+the denotative mathematical laws.} of it in \textit{Haskell programming language}
+(\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
 
-In Chapter 4, a reference implementation of the general payment primitives and its payment system called
+In Chapter 4, a reference implementation of the general payment primitives and its payment system
+called
 \textit{Superfluid Money} is introduced.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Foundation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{itemize}
-\item \textit{money distribution} models how monetary value is distributed amongst bearers\footnote{(Banking \& Finance)
-a person who presents a note or bill for payment. - Collins English Dictionary},
+    \item \textit{money distribution} models how monetary value is distributed amongst
+bearers \footnote{(Banking \& Finance) a person who presents a note or bill for payment. - Collins
+English Dictionary},
+
     \item \textit{payment primitives} updates money distribution,
+
     \item \textit{payment execution environment} performs payment primitives,
+
     \item and \textit{forms of money medium} are the ``user interfaces'' of money for the bearers.
@@
     \item Money can be distributed continuously over time, as opposed to be discrete.
-\item Payment primitives can involve more than two parties, as opposed to be only for a sender and a receiver.
+
+    \item Payment primitives can involve more than two parties, as opposed to be only for a sender
+and a receiver.
+
     \item Financial system should be compositional.
@@
 
-A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the following components:
+A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the
+following components:
 
@@
     \item U is the set of monetary units.
-\item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of every value unit u. The set
-    $\mathbb{N}$ is the set of all natural numbers, but instead, we can use any set of numerals that is totally ordered
-    (\eg\ integers, real numbers).
-\item $\beta : U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
-    $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal construction defining any type of legal
-    entity, such as a person, a family, a company, a state institution, etc.
+
+    \item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of
+every value unit u. The set $\mathbb{N}$ is the set of all natural numbers, but instead, we can use
+any set of numerals that is totally ordered (\eg\ integers, real numbers).
+
+    \item $\beta : U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$
+of a unit. The set $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal
+construction defining any type of legal entity, such as a person, a family, a company, a state
+institution, etc.
 \end{itemize}
 
-This discrete nature of this money distribution model is schematically depicted in~\ref{fig:discrete-md}:
+This discrete nature of this money distribution model is schematically depicted
+in~\ref{fig:discrete-md}:
 
@@
 
-But the discrete nature of the model does not provide the necessary element for us to add the desired properties to the
-payment system. Here we propose a modification that involves the usage of \textit{context ($\gamma$)}:
+But the discrete nature of the model does not provide the necessary element for us to add the
+desired properties to the payment system. Here we propose a modification that involves the usage
+of \textit{context ($\gamma$)}:
 
@@
 
-Note that in this model, context can be updated independently while value functions of the same money distribution can
-produce different monetary values.
+Note that in this model, context can be updated independently while value functions of the same
+money distribution can produce different monetary values.
 
@@
 \begin{itemize}
-\item If time (t) is included the context, then monetary value of each monetary unit can vary continuously over
-    time. Time is part of the physical reality, hence not changeable by the actors in the payment system.
-\item Any subset of monetary units can also have their value functions depending on the same information in
-    context. This could enable payment primitives that involve many parties. This set of information in context is
-    referred to as \textit{ctx :: SharedContext}, they can be changed over time by the actors in the payment system.
+    \item If time (t) is included the context, then monetary value of each monetary unit can vary
+continuously over time. Time is part of the physical reality, hence not changeable by the actors in
+the payment system.
+
+    \item Any subset of monetary units can also have their value functions depending on the same
+information in context. This could enable payment primitives that involve many parties. This set of
+information in context is referred to as \textit{ctx :: SharedContext}, they can be changed over
+time by the actors in the payment system.
 \end{itemize}
@@
 
-A payment primitive is a data type with a generator that creates payment primitive data from the shared context $ctx$,
-primitive specific argument $args$ and timestamp, along with an update of the shared context. Here is an example of
-generator for payment primitive \textit{a}:
+A payment primitive is a data type with a generator that creates payment primitive data from the
+shared context $ctx$, primitive specific argument $args$ and timestamp, along with an update of the
+shared context. Here is an example of generator for payment primitive \textit{a}:
 
@@
 
-Payment primitive data then can be used to create a delta update of money distribution\footnote{Specifically being
-monoidal, that is in short a set that has associative binary operation and an identity element. See
-https://ncatlab.org/nlab/show/monoid.}
+Payment primitive data then can be used to create a delta update of money
+distribution\footnote{Specifically being monoidal, that is in short a set that has associative
+binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid.}
 
@@
 
-Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
-in the same money distribution; additionally primitives should be the only constructs in a payment system that can
-update money distribution.
+Loosely speaking, it is considered a primitive, if it can not be broken down into other existing
+primitives which result in the same money distribution; additionally primitives should be the only
+constructs in a payment system that can update money distribution.
 
-Updates are \textit{monoidal}, so that they can be incremental and their parallel executions can be modeled.
+Updates are \textit{monoidal}, so that they can be incremental and their parallel executions can be
+modeled.
 
-The best known primitive is instant transfer of monetary value between one monetary unit to another. The introduction of
-context enables more primitives to be defined, and this will be discussed in later chapters.
+The best known primitive is instant transfer of monetary value between one monetary unit to
+another. The introduction of context enables more primitives to be defined, and this will be
+discussed in later chapters.
 
@@
 
-The purpose of a payment execution environment is to perform the actual payment primitives, where their computation
-interface, parallel evaluation strategies and payment system solvency are defined.
+The purpose of a payment execution environment is to perform the actual payment primitives, where
+their computation interface, parallel evaluation strategies and payment system solvency are defined.
 
-It is out of scope for this paper to survey in-depth the problem space of the operation semantics of payment execution
-environments. Nonetheless, a simplified model and some potential extensions to it is discussed briefly.
+It is out of scope for this paper to survey in-depth the problem space of the operation semantics of
+payment execution environments. Nonetheless, a simplified model and some potential extensions to it
+is discussed briefly.
 
@@
 
-While money distribution does not assign meaning to the range of monetary values, in real world applications, negative
-values can have special meanings. In the following analysis, we call any money unit that has a negative monetary value
-insolvent.
+While money distribution does not assign meaning to the range of monetary values, in real world
+applications, negative values can have special meanings. In the following analysis, we call any
+money unit that has a negative monetary value insolvent.
 
@@
 
-In a nondeterministic execution environment, we cannot determine when any financial contract will actually be
-executed. That means, there is always a chance a monetary unit could reach negative monetary value.
+In a nondeterministic execution environment, we cannot determine when any financial contract will
+actually be executed. That means, there is always a chance a monetary unit could reach negative
+monetary value.
 
-To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value which is set aside in a solvency conditional financial contract, such that if a solvency
-condition arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the execution.
+To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value
+which is set aside in a solvency conditional financial contract, such that if a solvency condition
+arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the
+execution.
 
@@
 
-Since \textit{fcNext} returns what is the next financial contract executable at a specific time, this deterministic
-property eliminates the need for the buffer.
+Since \textit{fcNext} returns what is the next financial contract executable at a specific time,
+this deterministic property eliminates the need for the buffer.
 
-But it introduces a different type of systemic risk, that is denial-of-service, since the system cannot advance the
-system time until all next executable contracts are executed.
+But it introduces a different type of systemic risk, that is denial-of-service, since the system
+cannot advance the system time until all next executable contracts are executed.
 
@@
 \begin{displayquote}
-A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
-digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
-etc. \footfullcite[][P3]{buldas2021unifying}
+A useful observation about existing money schemes is that they all have some kind of monetary units
+that are physical or digital representations of money. Examples are bills, coins, bank accounts,
+Bitcoin UTXOs, etc. \footfullcite[][P3]{buldas2021unifying}
 \end{displayquote}
@@
 \begin{itemize}
-\item \textit{Token and its Accounts} - \eg\ bank currency accounts. Each token is its own centralized execution
-    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
-    token.
-\item \textit{Note} - \eg\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
-    independent of the notes, but it needs notes to complete the execution of financial contracts.
+    \item \textit{Token and its Accounts} - \eg\ bank currency accounts. Each token is its own
+centralized execution environment, bearers access their monetary value through their accounts, and
+execute financial contracts through the token.
+
+    \item \textit{Note} - \eg\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The
+execution environment is independent of the notes, but it needs notes to complete the execution of
+financial contracts.
 \end{itemize}
 
-One of the main differences is from the ``user interface'' perspective. A bearer expects to keep many notes at hand,
-while maybe only needs a few accounts for each token. Also it is up to bearers to keep track of all their notes, while
-token can keep track of most of the states for bearers; hence notes are more decentralized and tokens are more
-centralized. Some also argue note-like model is better for complex concurrent and distributed computing environment
+One of the main differences is from the ``user interface'' perspective. A bearer expects to keep
+many notes at hand, while maybe only needs a few accounts for each token. Also it is up to bearers
+to keep track of all their notes, while token can keep track of most of the states for bearers;
+hence notes are more decentralized and tokens are more centralized. Some also argue note-like model
+is better for complex concurrent and distributed computing environment
 \footfullcite[][P2]{chakravarty2020extended}.
@@
 
-The focus of this paper is to formally define a set of payment primitives that modernize our payment systems. To prevent
-reinventing wheels, it is relevant to discuss first some approaches in computer science that are believed to help
-solving this challenge.
+The focus of this paper is to formally define a set of payment primitives that modernize our payment
+systems. To prevent reinventing wheels, it is relevant to discuss first some approaches in computer
+science that are believed to help solving this challenge.
 
@@
 
-Recall that we want our modernized payment systems to handle money distribution continuously over time, and its financial
-contracts compositional. A very closely related software design paradigm best known to address those needs is
-\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving
-multimedia animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
-\cite{wan2000functional} making FRP a more general framework for programming hybrid system with continuous behaviors in
-a high-level, declarative manner.
+Recall that we want our modernized payment systems to handle money distribution continuously over
+time, and its financial contracts compositional. A very closely related software design paradigm
+best known to address those needs is \textit{functional reactive programming (FRP)}.  It was first
+introduced by Conal Elliott \& Paul Hudak in solving multimedia
+animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
+\cite{wan2000functional} making FRP a more general framework for programming hybrid system with
+continuous behaviors in a high-level, declarative manner.
 
-After FRP got more adoption, it evolved to some variations that support discrete semantics, and some variations better
-suited more for interactive systems. In this paper we will stick to and revisit the basic constructions of the original
-formulation used in \cite{elliott1997functional} where we will draw inspirations from.
+After FRP got more adoption, it evolved to some variations that support discrete semantics, and some
+variations better suited more for interactive systems. In this paper we will stick to and revisit
+the basic constructions of the original formulation used in \cite{elliott1997functional} where we
+will draw inspirations from.
 
@@
 
-Values that vary over continuous time are called \textit{behaviors}. They are first-class values, and are built up
-compositionally. In modernized payment systems, we should want the monetary values of monetary units capable of varying over
-continuous time. The semantic function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given
-time:
+Values that vary over continuous time are called \textit{behaviors}. They are first-class values,
+and are built up compositionally. In modernized payment systems, we should want the monetary values
+of monetary units capable of varying over continuous time. The semantic function of
+$\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given time:
 
@@
 
-Like behaviors, \textit{events} are first-class values too. The semantic function of $\alpha$-event describes the time and
-information associated with an \textit{occurrence} of the event:
+Like behaviors, \textit{events} are first-class values too. The semantic function of $\alpha$-event
+describes the time and information associated with an \textit{occurrence} of the event:
 
@@
 
-In modernized payment systems, the payment primitives executed in payment execution environments are one type of
-events. More types of events can be read from the original paper \footfullcite[][section 2.3 Semantics of
-    Events]{elliott1997functional}.
+In modernized payment systems, the payment primitives executed in payment execution environments are
+one type of events. More types of events can be read from the original paper \footfullcite[][section
+2.3 Semantics of Events]{elliott1997functional}.
 
@@
 
-They key to modeling the payment execution environment using FRP is the \textit{reactivity}, which makes behaviors
-reactive. Specifically, the behavior \textit{b untilB e} exhibits b's behavior until \textit{e} occurs, and then swiches
-to a new behavior encoded in \textit{e}:
+They key to modeling the payment execution environment using FRP is the \textit{reactivity}, which
+makes behaviors reactive. Specifically, the behavior \textit{b untilB e} exhibits b's behavior
+until \textit{e} occurs, and then swiches to a new behavior encoded in \textit{e}:
 
@@
 
-In the context of modernized payment systems, the occurrences of payment primitives (events) change the behaviors of
-monetary units in how much monetary values it has over continuous. The building blocks of the financial contracts should
-be about modeling these events and their reactivity declaratively.
+In the context of modernized payment systems, the occurrences of payment primitives (events) change
+the behaviors of monetary units in how much monetary values it has over continuous. The building
+blocks of the financial contracts should be about modeling these events and their reactivity
+declaratively.
 
@@
 
-We also want a formal and precise specification of payment primitives. The title of the paper includes
-\textit{denotational semantics}: ``it is a \textit{compositional} style for precisely specifying the meanings of
-languages, invented by Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward})'', and Conal Elliott
-proposed that denotational semantics can also be applied to \textit{data types within a programming language}
+We also want a formal and precise specification of payment primitives. The title of the paper
+includes \textit{denotational semantics}: ``it is a \textit{compositional} style for precisely
+specifying the meanings of languages, invented by Christopher Strachey and Dana Scott in the 1960s
+(\cite{scott1971toward})'', and Conal Elliott proposed that denotational semantics can also be
+applied to \textit{data types within a programming language}
 \footfullcite[][section 2, denotational semantics and data types]{Elliott2009-type-class-morphisms-TR}.
@@
 
-The syntactic category we are interested in is \textit{payment primitives}, which we should treat them as FRP-style
-\textit{Behavior} data types. In the following chapters, it is also unambiguously referred to in short as
-$[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie must be defined by structural recursion.
+The syntactic category we are interested in is \textit{payment primitives}, which we should treat
+them as FRP-style \textit{Behavior} data types. In the following chapters, it is also unambiguously
+referred to in short as $[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie must be defined
+by structural recursion.
 
-It is important to note that our purpose of using the denotational semantics is to give precise meaning to payment
-primitives, independent of its implementation (which deals with performance, optimization, side effects, etc.). We will
-spend the next chapter exploring the denotational semantics for general payment primitives in modernized payment
-systems.
+It is important to note that our purpose of using the denotational semantics is to give precise
+meaning to payment primitives, independent of its implementation (which deals with performance,
+optimization, side effects, etc.). We will spend the next chapter exploring the denotational
+semantics for general payment primitives in modernized payment systems.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{General Payment Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The set of payment primitives supported in a payment system is general, if (a) monetary value of each monetary unit can
-vary continuously over time (b) monetary values can logically be shifted between two or more monetary units.
+The set of payment primitives supported in a payment system is general, if (a) monetary value of
+each monetary unit can vary continuously over time (b) monetary values can logically be shifted
+between two or more monetary units.
 
-The extent of the generality of each payment system may vary. This paper introduces a set of payment primitives that is
-general and serves as a starting point for the readers to explore the space of modern payment system.
+The extent of the generality of each payment system may vary. This paper introduces a set of payment
+primitives that is general and serves as a starting point for the readers to explore the space of
+modern payment system.
 
-The specifications will be formally defined using denotational semantics, along with a restatement in Haskell also
-applied as a constructive artifact friendly to computer environment\footnote{One may argue for a restatement
-in \textit{Agda} instead, for it has a richer dependently-type system for desirable constructive proofs. This matter
-will be dealt in the ``future investigations'' chapter of this paper.}.
+The specifications will be formally defined using denotational semantics, along with a restatement
+in Haskell also applied as a constructive artifact friendly to computer environment\footnote{One may
+argue for a restatement in \textit{Agda} instead, for it has a richer dependently-type system for
+desirable constructive proofs. This matter will be dealt in the ``future investigations'' chapter of
+this paper.}.
 
@@
 
-Recall the definition of payment system previously, money distribution sits in the core of the system, and that is the
-syntactic category $\mathcal{M}$ we will be dealing with:
+Recall the definition of payment system previously, money distribution sits in the core of the
+system, and that is the syntactic category $\mathcal{M}$ we will be dealing with:
 
@@
     \item The meaning of the mathematical \textit{model} $[\![\mathcal{M}]\!]$ is money distribution.
-\item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ evaluates the syntax of money
-      distribution, payment primitives, etc.
+
+    \item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ evaluates
+the syntax of money distribution, payment primitives, etc.
 \end{itemize}
@@
         [\![\emptyset]\!] &= \lambda u \rightarrow \lambda t\ \rightarrow \emptyset \\
-        [\![m_a \oplus m_b]\!] &= \lambda u \rightarrow \lambda t\ \rightarrow [\![m_a]\!]\ u\ t\ +\ [\![m_b]\!]\ u\ t \\
+        [\![m_a \oplus m_b]\!] &= \lambda u \rightarrow \lambda t\ \rightarrow
+            [\![m_a]\!]\ u\ t\ +\ [\![m_b]\!]\ u\ t \\
     \end{split}
@@
 
-A payment primitive \textit{prim} is a model that produces a monoidal money distribution, semantically
-representing an ``update'' to a money distribution:
+A payment primitive \textit{prim} is a model that produces a monoidal money distribution,
+semantically representing an ``update'' to a money distribution:
 
@@
 
-That is to say, at any given time, the sum of monetary value of all monetary units shall always equal to zero. Zero is
-used to keep the semantical meaning of payment system simple and elegant. In its applications, a payment system may use
-some special monetary unit accounting negative monetary values to accommodate concepts such as mining, minting, money
-printing, etc.
+That is to say, at any given time, the sum of monetary value of all monetary units shall always
+equal to zero. Zero is used to keep the semantical meaning of payment system simple and elegant. In
+its applications, a payment system may use some special monetary unit accounting negative monetary
+values to accommodate concepts such as mining, minting, money printing, etc.
 
@@
 
-To come up with such lawful money distribution, we can divide and conquer. In a payment system, if we restrict that only
-payment primitives can provide ``updates'' to its money distribution, so that a money distribution is only a result of a
-sequence of payment primitive updates; then we can have these axioms as the basis for the proof.
+To come up with such lawful money distribution, we can divide and conquer. In a payment system, if
+we restrict that only payment primitives can provide ``updates'' to its money distribution, so that
+a money distribution is only a result of a sequence of payment primitive updates; then we can have
+these axioms as the basis for the proof.
 
@@
 
-First we must impose the law of conservation of value on payment primitives as an axiom, in order to prove inductively
-that such restricted money distribution satisfies the law of conservation of value too.
+First we must impose the law of conservation of value on payment primitives as an axiom, in order to
+prove inductively that such restricted money distribution satisfies the law of conservation of value
+too.
 
@@
 
-A \textit{index} (we use symbol $k$ for them) has a function $\rho$ which produces a real number for each monetary unit:
+A \textit{index} (we use symbol $k$ for them) has a function $\rho$ which produces a real number for
+each monetary unit:
 
@@
 
-Let's generalize the one to one payment primitives using index abstraction. We use $I$ subscript for the indexed
-versions of the primitives.
+Let's generalize the one to one payment primitives using index abstraction. We use $I$ subscript for
+the indexed versions of the primitives.
 
@@
 
-It should be straightforward to prove that they also satisfy the \textit{axiom A of restricted money distribution}
-thanks to the law of the index.
+It should be straightforward to prove that they also satisfy the \textit{axiom A of restricted money
+distribution} thanks to the law of the index.
 
@@
 
-It means that it is an index \textit{universally} available for each monetary unit, and its proportion is always 1 for
-that monetary unit and 0 for all others.
+It means that it is an index \textit{universally} available for each monetary unit, and its
+proportion is always 1 for that monetary unit and 0 for all others.
 
@@
 
-An even more powerful abstraction is to model participants involved a payment primitive a \textit{network} (we use
-symbol $w$ for them).
+An even more powerful abstraction is to model participants involved a payment primitive
+a \textit{network} (we use symbol $w$ for them).
 
@@
 
-Let's generalize the basic payment primitives using network abstraction. We use $N$ subscript for the indexed versions
-of the primitives.
+Let's generalize the basic payment primitives using network abstraction. We use $N$ subscript for
+the indexed versions of the primitives.
 
@@
 
-The answer is most likely a no. Not because it is not useful, after all mathematical formula is about truth and perhaps
-also elegance in it, but because of we may miss optimization opportunities needed in implementation when more
-specialized versions are used instead\footnote{We will not though discuss the subjective aspects, including in software
-engineering principles such as YAGNI (\url{https://en.wikipedia.org/wiki/You_aren't_gonna_need_it}), or user experience
-perspective of the payment primitives.}.
+The answer is most likely a no. Not because it is not useful, after all mathematical formula is
+about truth and perhaps also elegance in it, but because of we may miss optimization opportunities
+needed in implementation when more specialized versions are used instead\footnote{We will not though
+discuss the subjective aspects, including in software engineering principles such as YAGNI
+(\url{https://en.wikipedia.org/wiki/You_aren't_gonna_need_it}), or user experience perspective of
+the payment primitives.}.
 
-In the next chapter, we will look into a reference implementation where these optimizations are applied.
+In the next chapter, we will look into a reference implementation where these optimizations are
+applied.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Superfluid Money - A Reference Implementation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{Distribution Agreement}
+\subsection{Distribution Agreements}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Future Investigations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\section{Combinator Library for Financial Contracts}
+
 \section{Payment in General Accounting Domains}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
 \printbibliography{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-01 packages/spec-haskell/utils/lhs2tex.sh

@@ -7,8 +7,8 @@ cd "$(dirname "$0")"/..
 
 {
     cat $1
-} | awk '
-    # process haddock documentation
+} | sed "1 d" | # remove emacs mode-line
+    awk '
     /\\begin{haddock}/ { h = 1; next }
     /\\end{haddock}/   { h = 0; next }
     /\\begin{code}/    { if (h) next }
@@ -16,5 +16,5 @@ cd "$(dirname "$0")"/..
     /^{-/  { if (h) next }
     /^-}/  { if (h) next }
     /^--}/ { if (h) next }
-    { print $0 }
-' | cat
+    { print $0 }' | # process haddock documentation
+    cat # nop, just to rhyme.

### 2022-10-02 packages/spec-haskell/yellowpaper/Paper1.tex
cleanup chapter 2

@@
 For the purpose of this paper, the model of context is: $\gamma = t \times ctx$.
+
+\subsubsection{Haskell Code Conventions Used}
+
+Before first time in this paper listing specification in Haskell, here are some highlights of
+conventions in the style of the code used.
+
+The specification is written in Haskell with \textit{GHC2021 language set}\footnote{The complete set
+of the extensions is enumerated in
+\url{https://downloads.haskell.org/ghc/latest/docs/users_guide/exts/control.html\#extension-GHC2021}.}.
+
+\paragraph{Indexed Types and Type Equality}
+
+In order to make the specification free of specific choices of core data types in
+implementation, \textit{FunctionalDependencies}, \textit{TypeFamilies}
+and \textit{TypeFamilyDependencies} are extensively used. And in order to make the code less
+cluttered, type quality operator $(\sim)$
+used. Here is an example:
+
+\begin{code}
+    type (~) :: forall k. k -> k -> Constraint
+
+    monetaryValue :: ( mv  ~ MD_MVAL md
+                     , mu  ~ MD_MU md
+                     , ctx ~ MD_CTX md
+                     )
+                  => md -> (mu, ctx) -> mv
+\end{code}
+
+The otherwise tedious type family synonyms ``\mintinline{haskell}{MD_XYZ md}'' are rewritten with $mv$
+$mu$ $ctx$ with the help of $(\sim)$ operator.
 

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
Real Time Balance section

@@
 
-%% Include a preamble at choice during processing.
+%% Include the preamble at choice during processing.
 \input{preamble.tex}
+
 \begin{document}
@@
 In Chapter 4, a reference implementation of the general payment primitives and its payment system
-called
-\textit{Superfluid Money} is introduced.
+called \textit{Superfluid Protocol} is introduced.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Superfluid Money - A Reference Implementation}
+\chapter{Superfluid Protocol - A Reference Implementation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+Superfluid protocol (``the protocol'')\footnote{The code base is available
+at \url{https://github.com/superfluid-finance/protocol-monorepo/}.} is the first implementation of
+the \textit{denotational semantics of payment primitives} (though before it was formalized and named
+so) on \textit{Ethereum Virtual Machine} \cite{wood2014ethereum}. The first version of the protocol
+is written in Solidity programming language \footnote{\url{https://soliditylang.org/}}.
+
+To better serve as a reference implementation of the \textit{modern payment system} formalized by
+this paper and its sequels, an implementation in Haskell was created. It aims to implement the full
+specifications of (a) denotational semantics of payment primitives (b) compositional financial
+contracts for the payment primitives (c) token \& note model of money mediums, and their execution
+environment.
+
+This paper covers the implementation of (a).
+
 \section{Real Time Balance}
+
+For the purpose of compositional financial contracts, it is useful to separate monetary values that
+bearers can use immediately from ones that are set aside for other financial purpose. The concept
+of \textit{real time balance} is thus created. \textit{Real time balance} is a
+functorful\footnote{Bartosz Milewski has an excellent series on these
+topics: \url{https://bartoszmilewski.com/2015/01/20/functors/}, and he uses the term ``functorful''
+to convey the idea of generalized container.} of monetary values. It can be converted to a single
+monetary value.
+
+Although since this is not the subject of this paper, it suffices to just show its definition
+instead:
+
+\begin{code}
+-- Note that we omit the definition of AnyTypedValue here,
+-- since it is not relevant to the idea here.
+
+class ( MonetaryValue v
+      , Foldable rtbF
+      , Monoid (rtbF v)
+      , Eq (rtbF v)
+      ) => RealTimeBalance rtbF v | rtbF -> v where
+
+    -- | Convert a single monetary value to a RTB value.
+    valueToRTB :: Proxy rtbF -> v -> rtbF v
+
+    -- | Net monetary value of a RTB value.
+    netValueOfRTB :: rtbF v -> v
+    netValueOfRTB = foldr (+) def
+
+    -- | Convert typed values to a RTB value.
+    typedValuesToRTB :: [AnyTypedValue v] -> rtbF v
+
+    -- | Get typed values from a RTB value.
+    typedValuesFromRTB :: rtbF v -> [AnyTypedValue v]
+\end{code}
+
+In the paper, we refer to the real time balance values as $rtb$, and its function $netValueOfRTB$ is
+what matters the most here, it converts any $rtb$ to the \textit{monetary value} which is what the
+model of money distribution needs.
 

### 2022-10-03 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/CoreTypes/RealTimeBalance.hs

@@ -32,7 +32,6 @@ class ( MonetaryValue v
       , Monoid (rtbF v)
       , Eq (rtbF v)
       ) => RealTimeBalance rtbF v | rtbF -> v where
-
     -- | Convert a single monetary value to a RTB value.
     valueToRTB :: Proxy rtbF -> v -> rtbF v
 

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
Agreement Framework

@@
 
-\section{Hierarchy of Agreements}
+The main tasks of the implementer of \textit{denotational payment primitives} are:
+
+\begin{itemize}
+    \item preserve the program correctness (and if possible, with proof of equivalence),
+    \item optimize for efficient computation,
+    \item and provide a software interface for using it.
+\end{itemize}
+
+The protocol introduces \textit{agreement framework} to address the optimization needs and to
+provide a consistent software interface called ``agreement'' with agreement laws for reasoning about
+the correctness.
+
+\paragraph{Monetary Unit Data}
+
+Recall that all monetary units have a monetary value function: $$ \nu :: u \rightarrow \mathbb{N}$$.
+
+Agreement framework defines a concept called \textit{monetary unit data}, and each monetary unit has
+a set of them:
+
+\begin{code}
+class ( SuperfluidCoreTypes sft
+      ) => MonetaryUnitDataClass mud sft | mud -> sft where
+    -- | π function - balance provided (hear: π) by the monetary unit data.
+    balanceProvided
+        :: forall t rtb.
+           -- indexed type aliases
+           ( t ~ SFT_TS sft
+           , rtb ~ SFT_RTB sft
+           )
+        => mud -> t -> rtb
+\end{code}
+
+The $\pi$ function produces \textit{real time balance} at a particular time for \textit{monetary
+unit data}. How a monetary unit produces monetary value from its set of monetary unit data is
+described in the ``hierarchy of agreements'' section.
+
+\paragraph{Agreement Contract}
+
+Recall how a \textit{payment primitive} generator should look like:
+
+\begin{equation}
+    genPrim_a :: ctx \rightarrow args_a \rightarrow t \rightarrow prim \times ctx
+\end{equation}
+
+Shared context $ctx$ is clearly the only data can be used by optimization, since it is updated each
+time a primitive is generated. In the agreement framework, a data type \textit{agreement contract}
+in the shared context is to fulfill this role:
+
+\begin{code}
+-- | Agreement contract type class.
+class ( SuperfluidCoreTypes sft
+      , Default ac
+      , MonetaryUnitDataClass ac sft
+      , Default (AgreementOperationOutput ac)
+      , Traversable (AgreementOperationOutputF ac) -- <= Foldable Functor
+      ) => AgreementContract ac sft | ac -> sft where
+
+    -- | ω function - apply agreement operation ~ao~ (hear: ω) to the agreement
+    --                operation data ~ac~ to get a tuple of:
+    --
+    --   1. An updated ~ac'~.
+    --
+    --   2. A functorful delta of agreement monetary unit data ~mudsΔ~, which
+    --      then can be monoid-appended to existing
+    --      ~mudΔ~.  This is what can make an agreement scalable.
+    applyAgreementOperation
+        :: forall t ao aoo.
+           -- indexed type aliases
+           ( t ~ SFT_TS sft
+           , ao ~ AgreementOperation ac
+           , aoo ~ AgreementOperationOutput ac
+           )
+        => ac -> ao -> t -> (ac, aoo)
+    data family AgreementOperation ac :: Type
+    data family AgreementOperationOutputF ac :: Type -> Type
+    type family AgreementOperationOutput ac = (mmuds :: Type) | mmuds -> ac
+\end{code}
+
+The $\omega$ function ($applyAgreementOperation$) is the $genPrim$ in the agreement framework. It
+takes in a agreement contract, an operation onto it and the current time; then it spits out an
+update of the agreement contract and a functorful of new monoidal monetary unit data.
+
+Here is a visualization of ``machinery'' of the $\omega$ function:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{../assets/agreement-contract-omega-function.png}
+    \caption{Agreement Contract $\omega$ Function}
+    \label{fig:ac-omega}
+\end{figure}
+
+It also illustrates that it is expected the process should respect the \textit{law of conservation
+of value} mandated by the \textit{restricted money distribution} model.
+
+It is also important to note that $AgreementContract$ itself is also a $MonetaryUnitDataClass$, but
+it is not a monoid, hence it is used to replace the previous agreement contract data. This has
+optimization implications, as in that if agreement contracts do not produce zero balance then they
+must be included in the $\nu$ function, that can make the $\nu$ function $O(N)$ to the number of
+agreement contracts a monetary unit is associated with.
+
+It may also have been self evident that agreement contract is a analogy to the fact that it encodes
+``ongoing relationships'' like legal contracts do between bearers.
+
+\subsection{Hierarchy of Agreements}
 

### 2022-10-03 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Concepts/Agreement.hs

@@ -39,14 +39,13 @@ class ( SuperfluidCoreTypes sft
     --   2. A functorful delta of agreement monetary unit data ~mudsΔ~, which then can be monoid-appended to existing
     --      ~mudΔ~.  This is what can make an agreement scalable.
     applyAgreementOperation
-        :: forall t ao aoo acs.
+        :: forall t ao aoo.
            -- indexed type aliases
            ( t ~ SFT_TS sft
            , ao ~ AgreementOperation ac
            , aoo ~ AgreementOperationOutput ac
-           , acs ~ (ac, aoo)
            )
-        => ac -> ao -> t -> acs
+        => ac -> ao -> t -> (ac, aoo)
 
     -- | φ' function - functorize the existential semigroup monetary unit data of agreement operation output
     functorizeAgreementOperationOutput
@@ -73,7 +72,7 @@ class ( SuperfluidCoreTypes sft
     data family AgreementOperationOutputF ac :: Type -> Type
 
     -- Note: since ~ac~ is injected, hence this can be associated type alias.
-    type family AgreementOperationOutput ac = (muds :: Type) | muds -> ac
+    type family AgreementOperationOutput ac = (smuds :: Type) | smuds -> ac
 
 -- * Null Agreement
 

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
chapter done! Superfluid Protocol - A Reference Implementation

@@
 
-This paper covers the implementation of (a).
+This paper covers the overview of the implementation of (a).
 
@@
 For the purpose of compositional financial contracts, it is useful to separate monetary values that
-bearers can use immediately from ones that are set aside for other financial purpose. The concept
-of \textit{real time balance} is thus created. \textit{Real time balance} is a
-functorful\footnote{Bartosz Milewski has an excellent series on these
+bearers can use immediately (called \textit{untappedValue} in code) from ones that are set aside for
+other financial purpose. The concept of \textit{real time balance} is thus created. \textit{Real
+time balance} is a functorful\footnote{Bartosz Milewski has an excellent series on these
 topics: \url{https://bartoszmilewski.com/2015/01/20/functors/}, and he uses the term ``functorful''
@@
 
-\paragraph{Monetary Unit Data}
+\paragraph{Monetary Unit Data (MUD)}
 
@@
     --   2. A functorful delta of agreement monetary unit data ~mudsΔ~, which
-    --      then can be monoid-appended to existing
-    --      ~mudΔ~.  This is what can make an agreement scalable.
+    --      then can be appended to existing ~mudΔ~.  This is what can make an
+    --      agreement scalable.
     applyAgreementOperation
@@
     data family AgreementOperationOutputF ac :: Type -> Type
-    type family AgreementOperationOutput ac = (mmuds :: Type) | mmuds -> ac
+    type family AgreementOperationOutput ac = (smuds :: Type) | smuds -> ac
 \end{code}
@@
 takes in a agreement contract, an operation onto it and the current time; then it spits out an
-update of the agreement contract and a functorful of new monoidal monetary unit data.
+update of the agreement contract and a functorful of new delta of monetary unit data.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{../assets/agreement-contract-omega-function.png}
+    \includegraphics[width=1\textwidth]{../assets/agreement-contract-omega-function.png}
     \caption{Agreement Contract $\omega$ Function}
@@
 It is also important to note that $AgreementContract$ itself is also a $MonetaryUnitDataClass$, but
-it is not a monoid, hence it is used to replace the previous agreement contract data. This has
+it is not a semigroup, hence it is used to replace the previous agreement contract data. This has
 optimization implications, as in that if agreement contracts do not produce zero balance then they
@@
 
-It may also have been self evident that agreement contract is a analogy to the fact that it encodes
+It may have been self evident that agreement contract is a analogy to the fact that it encodes
 ``ongoing relationships'' like legal contracts do between bearers.
 
+\subsection{Lens Data Accessors}
+
+In order to support \textit{index abstraction} in the denotational payment primitives, Monetary unit
+data are created with \textit{lens data accessors}\footfullcite{clarke2020profunctor}:
+
+\begin{code}
+-- representation of lenses
+data Lens a b s t = Lens { view :: s -> a, update :: (b, s) -> t }
+-- the pro-functor version of it
+type Lens s t a b = forall f. Functor f => (a -> f b) -> s -> f t
+\end{code}
+
+The pro-functor version of might seem very obscure at first, but its data representation is rather
+self-explanatory: a lens is simply a pair of getter ($view$) and setter ($update$) encoded in the
+data.
+
+With the help of Lens, then we can create the payment primitives independent of the choices between
+1-to-1, 1-to-N, etc. Here are how they are defined for each class of payment primitives:
+
+\paragraph{Instant Value MUD}
+
+This is for agreements where value is instantly transferred.
+
+\begin{code}
+class ( Default amuLs
+      , SuperfluidSystemTypes sft
+      ) => MonetaryUnitLenses amuLs sft | amuLs -> sft where
+    untappedValue :: Lens' amuLs (UntappedValue (SFT_MVAL sft))
+
+type MonetaryUnitData :: Type -> Type -> Type
+newtype MonetaryUnitData amuLs sft =
+    MkMonetaryUnitData { getMonetaryUnitLenses :: amuLs }
+    deriving (Default)
+
+instance MonetaryUnitLenses amuLs sft
+    => Semigroup (MonetaryUnitData amuLs sft) where
+    MkMonetaryUnitData a <> MkMonetaryUnitData b =
+        let c = a & over untappedValue (+ b^.untappedValue)
+        in MkMonetaryUnitData c
+
+instance MonetaryUnitLenses amuLs sft
+    => MonetaryUnitDataClass (MonetaryUnitData amuLs sft) sft where
+    balanceProvided (MkMonetaryUnitData a) _ =
+        typedValuesToRTB [mkAnyTypedValue $ a^.untappedValue]
+\end{code}
+
+Note that (a) $^.$ is the view function (getter) for Lens types. (b) semigroup operator $(<>)$ defines
+how two monetary unit data can be combined into one.
+
+\paragraph{Constant Flow Agreement (CFA) MUD}
+
+A more interesting case is where monetary value is changing continuously over time at a constant
+rate:
+
+\begin{code}
+class ( Default amuLs
+      , SuperfluidSystemTypes sft
+      ) => MonetaryUnitLenses amuLs sft | amuLs -> sft where
+    settledAt    :: Lens' amuLs (SFT_TS sft)
+    settledValue :: Lens' amuLs (UntappedValue (SFT_MVAL sft))
+    netFlowRate  :: Lens' amuLs (SFT_MVAL sft)
+
+type MonetaryUnitData :: Type -> Type -> Type
+newtype MonetaryUnitData amuLs sft =
+    MkMonetaryUnitData { getMonetaryUnitLenses :: amuLs }
+    deriving (Default)
+
+instance MonetaryUnitLenses amuLs sft
+    => Semigroup (MonetaryUnitData amuLs sft) where
+    MkMonetaryUnitData a <> MkMonetaryUnitData b =
+        let t  = a^.settledAt
+            t' = b^.settledAt
+            settledΔ = MkUntappedValue $ a^.netFlowRate * fromIntegral (t' - t)
+            c = a & set  settledAt    t'
+                  & over netFlowRate  (+ b^.netFlowRate)
+                  & over settledValue (+ (b^.settledValue + settledΔ))
+        in MkMonetaryUnitData c
+
+instance MonetaryUnitLenses amuLs sft
+    => MonetaryUnitDataClass (MonetaryUnitData amuLs sft) sft where
+    balanceProvided (MkMonetaryUnitData a) t =
+        let b = uval_s + coerce (fr * fromIntegral (t - t_s))
+        in  typedValuesToRTB [ mkAnyTypedValue b ]
+        where t_s    = a^.settledAt
+              uval_s = a^.settledValue
+              fr     = a^.netFlowRate
+\end{code}
+
+Note the implementation of semigroup binary operator, this is where the optimization occurs: to use
+$netFlowRate$ to fold monetary unit data into a single value.
+
+\paragraph{Decaying Flow Agreement (CFA) MUD}
+
+\begin{code}
+class ( Default amuLs
+      , SuperfluidSystemTypes sft
+      ) => MonetaryUnitLenses amuLs sft | amuLs -> sft where
+    decayingFactor  :: Lens' amuLs (SFT_FLOAT sft)
+    settledAt       :: Lens' amuLs (SFT_TS sft)
+    αVal            :: Lens' amuLs (SFT_FLOAT sft)
+    εVal            :: Lens' amuLs (SFT_FLOAT sft)
+
+type MonetaryUnitData :: Type -> Type -> Type
+newtype MonetaryUnitData amuLs sft =
+    MkMonetaryUnitData { getMonetaryUnitLenses :: amuLs }
+    deriving (Default)
+
+instance MonetaryUnitLenses amuLs sft
+    => Semigroup (MonetaryUnitData amuLs sft) where
+    MkMonetaryUnitData a <> MkMonetaryUnitData b =
+        let c = a & set  settledAt     (b^.settledAt)
+                  & over αVal          (\α -> α * exp (-λ * t_Δ) - ε')
+                  & over εVal          (+ ε')
+        in MkMonetaryUnitData c
+        where ε'  = b^.εVal
+              λ   = b^.decayingFactor
+              t_Δ = fromIntegral (b^.settledAt - a^.settledAt)
+
+instance MonetaryUnitLenses amuLs sft
+    => MonetaryUnitDataClass (MonetaryUnitData amuLs sft) sft where
+    balanceProvided (MkMonetaryUnitData a) t =
+        let b = ceiling $ α * exp (-λ * t_Δ) + ε
+        in  typedValuesToRTB [ (mkAnyTypedValue . MkUntappedValue) b ]
+        where t_s   = a^.settledAt
+              α     = a^.αVal
+              ε     = a^.εVal
+              λ     = a^.decayingFactor
+              t_Δ   = fromIntegral (t - t_s)
+\end{code}
+
+\paragraph{Universal Index (UIDX)}
+
+An universal index then can be implemented trivially by representing lenses using the record syntax
+directly. For example, for constant flow monetary unit data:
+
+\begin{code}
+data MonetaryUnitLenses sft = MonetaryUnitLenses
+    { settled_at    :: SFT_TS sft
+    , settled_value :: UntappedValue (SFT_MVAL sft)
+    , net_flow_rate :: SFT_MVAL sft
+    } deriving (Generic)
+
+deriving instance SuperfluidSystemTypes sft
+    => Default (MonetaryUnitLenses sft)
+
+-- | Monetary unit lenses for the universal index.
+instance SuperfluidSystemTypes sft
+    => CFMUD.MonetaryUnitLenses (MonetaryUnitLenses sft) sft where
+    settledAt          = $(field 'settled_at)
+    settledValue       = $(field 'settled_value)
+    netFlowRate        = $(field 'net_flow_rate)
+\end{code}
+
+The $field$ is a template Haskell function to generate lens from record fields.
+
+\paragraph{Proportional Distribution Index (PDIDX)}
+
+Proportional distribution index describes on-going \textit{subscription} agreement contracts between
+one \textit{publisher} and many \textit{subscribers} to the publisher's \textit{distribution}.
+
+Its instant value variance is called \textit{``Instant Distribution Agreement (IDA)''}.
+
+Its constant flow variance is called \textit{``Constant Flow Distribution Agreement (CFDA)''}.
+
 \subsection{Hierarchy of Agreements}
 
-\subsection{Instant Transferable Agreement}
-
-\subsection{Constant Flow Agreement}
-
-\subsection{Distribution Agreements}
-
-\subsection{Decaying Flow Agreement}
+To finish, here is the illustration of data structures for the denotational payment primitives
+implemented with agreement framework:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{../assets/agreement-data-structures.png}
+    \caption{Agreement Data Structures}
+    \label{fig:ac-omega}
+\end{figure}
+
+Note that with \textit{Root MUD}, any monetary unit can traverse all its MUDs; and with \textit{Root
+Contract} relations between monetary units can also be searched by a simple algorithm.
+
+This concludes the overview of the Superfluid protocol implementation. For more details, one should
+refer to the code repository mentioned before.
 
@@
 \section{Payment in General Accounting Domains}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-03 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Concepts/Agreement.hs

@@ -36,8 +36,8 @@ class ( SuperfluidCoreTypes sft
     --
     --   1. An updated ~ac'~.
     --
-    --   2. A functorful delta of agreement monetary unit data ~mudsΔ~, which then can be monoid-appended to existing
-    --      ~mudΔ~.  This is what can make an agreement scalable.
+    --   2. A functorful delta of agreement monetary unit data ~mudsΔ~, which then can be appended to existing ~mudΔ~.
+    --      This is what can make an agreement scalable.
     applyAgreementOperation
         :: forall t ao aoo.
            -- indexed type aliases

### 2022-10-03 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/MonetaryUnitData/MintedValue.hs

@@ -32,7 +32,7 @@ newtype MonetaryUnitData amuLs sft = MkMonetaryUnitData { getMonetaryUnitLenses 
     deriving (Default)
 
 instance MonetaryUnitLenses amuLs sft => Semigroup (MonetaryUnitData amuLs sft) where
-    (<>) (MkMonetaryUnitData a) (MkMonetaryUnitData b) =
+    MkMonetaryUnitData a <> MkMonetaryUnitData b =
         let c = a & over untappedValue (+ b^.untappedValue)
                   & over mintedValue   (+ b^.mintedValue)
         in MkMonetaryUnitData c

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
final words chapter DONE

@@
 
-In Chapter 5, some possible further investigations are included for future study purpose.
+In Chapter 5, some possible further investigations are also included as notes.
 
@@
 
-Here is a visualization of ``machinery'' of the $\omega$ function:
+Figure \ref{fig:ac-omega} is a visualization of ``machinery'' of the $\omega$ function:
 
@@
 
-To finish, here is the illustration of data structures for the denotational payment primitives
-implemented with agreement framework:
-
-\begin{figure}[h]
+To finish, figure \ref{fig:ac-agreement-data-structures} is the illustration of data structures for
+the denotational payment primitives implemented with agreement framework:
+
+\begin{figure}[p]
     \centering
-    \includegraphics[width=1\textwidth]{../assets/agreement-data-structures.png}
+    \includegraphics[width=0.9\textwidth]{../assets/agreement-data-structures.png}
     \caption{Agreement Data Structures}
-    \label{fig:ac-omega}
+    \label{fig:ac-agreement-data-structures}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Future Investigations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Restatement in Agda, Correctness and Equivalence Proofs}
-
-\section{Combinator Library for Financial Contracts}
-
-\section{Payment in General Accounting Domains}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Acknowledgments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Final Words}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Notes on Future Investigations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Restatement in Agda, Correctness and Equivalence Proofs}
+
+One of the advantages of using Haskell language was chosen to write the reference implementation is
+that it is a language with industrial strength, and the implementation could be easily integrated
+into a production code base without much performance compromises.
+
+However, a major disadvantage is that it is not equipped with sufficient apparatus for program
+correctness proofs. The best it can offer without engaging more experimental Haskell features is to
+use \textit{QuickCheck}\footnote{\url{https://wiki.haskell.org/QuickCheck} - Haskell wiki page for
+QuickCheck.} to the necessary laws are not violated using randomized test vector.
+
+To amend this deficiency, \textit{Agda programming language} comes as a great candidate for a
+different constructive restatement of the formal specification.
+
+It is based on the insight of the deep connection (equivalence/isomorphism) between logic and
+dependently typed programming, often called "the Curry–Howard correspondence", as discovered and
+developed during the 20th century (explained in \cite by Phillip Wadler as ``Propositions as
+Types''). Agda being a dependently typed functional programming language fully embodies this
+insight, hence a good candidate for creating provable correct program.
+
+To learn more about Agda, see refer to these footnotes\footnote{\url{https://plfa.github.io/} -
+Programming Language Foundations in
+Agda.} \footnote{\url{https://wiki.portal.chalmers.se/agda/pmwiki.php} - Agda
+Wiki.} \footnote{\url{https://wiki.portal.chalmers.se/agda/Main/Community} - Agda community page.}.
+
+\subsection{Future Papers on Modern Payment System}
+
+The next yellow paper will formalize how the denotational payment primitives can be stitched
+together using a powerful combinator library pattern briefly described
+in \cite{peyton2000composing}.
+
+The execution environments for these financial contracts are also fertile ground for new ideas, from
+deterministic execution to avoid the usage of buffer, to using distributed ledger technology to
+deep-embed these financial contracts in the consensus layer.
+
+\subsection{General Accounting Domains \& Real Time Finance}
+
+\begin{displayquote}
+Accounting, also known as accountancy, is the measurement, processing, and communication of
+financial and non financial information about economic entities such as businesses and
+corporations. \footfullcite{needles2013principles}
+\end{displayquote}
+
+The \textit{real time balance} introduced in this paper can be seen as a instance in
+the \textit{general accounting domain} specifically for financial contracts in dealing with payment
+primitives, a real time version of the cash flow accounting. It is a long with other types,
+including balance sheet accounting, income statement accounting. The conversion between these
+instances of general accounting domains are often called ``reconciliations''.
+
+More work can be done on how to create a simple and elegant automation system for the
+reconciliations.
+
+\section{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%
+
+\emph{
+We define the term \textbf{real time finance} to mean a financial system where its payment system is
+modernized to handle money distribution continuously over time, its financial contracts are
+compositional, and its general accounting domain are automated and processed in real time.
+}
+
+This paper defines the what constitutes a modern payment system formally specified using
+denotational semantics and restated using Haskell programming language.
+
+In future work, we will look into deeper other topics of real time finance, and continue to refine
+the methodology used to achieve \textit{simple and precise} specifications guiding correct and
+efficient engineering.
+
+\section{Acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+(To be confirmed.)
 

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
alright, abstract done, will do a proof reading before sending out

@@
 \begin{abstract}
-    \begin{center}
-        (Some distant lyrics as the placeholder for the actual abstract)
-
-        Money, money, money
-
-        Must be funny
-
-        In the rich man's world
-
-        Money, money, money
-
-        Always sunny
-
-        In the rich man's world
-
-        \
-
-        Ah, all the things I could do
-
-        If I had a little money
-
-        It's a rich man's world
-
-        It's a rich man's world
-    \end{center}
+Payment systems in information age are still largely modeled after their analog predecessors. While
+some electronic money payment systems do utilize computing technology and Internet, this paper
+presents a case that a true modernization can still be done by (a) making payments happening
+continuously over time (b) involving more than two parties in a payment if necessary (c) having
+compositional financial contracts.
+
+This paper first explores the foundation of modern payment system, which consists of a money
+distribution model, payment primitives, payment execution systems of financial contracts and
+different forms of money mediums. Then the paper uses \textit{denotational semantics} to formally
+define payment primitives for modern payment system. Lastly, this paper also includes an overview
+of \textit{Superfluid protocol}, a reference implementation of the payment primitives and a its
+payment system.
+
+This paper also includes literate Haskell code that compiles as the constructive artifact for the
+formal specifications.
+
 \end{abstract}
@@
 
-\subsection{$\mathcal{M}$ - Category of Money Distribution}
+\subsection{$\mathcal{M}$ - Syntax for Money Distribution}
 

### 2022-10-04 packages/spec-haskell/yellowpaper/Paper1.tex
change article outline style and biblatex style

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\part*{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal
-definition of payment system and its components. We then select a few relevant approaches used in
-computer science useful for modeling and defining formal specification for the payment system.
-
-One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to
-define the general payment primitives. Along with the denotational semantics, a
+In part\ref{part:foundation}, we shall first explore the foundation for the survey. Here we present
+a formal definition of payment system and its components. We then select a few relevant approaches
+used in computer science useful for modeling and defining formal specification for the payment
+system.
+
+One of the approaches is \textit{denotational semantics}, which is used in part \ref{part:gpp} of
+the paper to define the general payment primitives. Along with the denotational semantics, a
 restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our case,
@@
 
-In Chapter 4, a reference implementation of the general payment primitives and its payment system
-called \textit{Superfluid Protocol} is introduced.
-
-In Chapter 5, some possible further investigations are also included as notes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Foundation}
+In part \ref{part:sf}, a reference implementation of the general payment primitives and its payment
+system called \textit{Superfluid Protocol} is introduced.
+
+Notes on possible further investigations are also included in the end of the paper.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\part{Foundation}\label{part:foundation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the
-following components:
+A representation of money and its distribution proposed in ``a unifying theory''
+from \citeauthor{buldas2021unifying} involves the following components:
 
@@
 This discrete nature of this money distribution model is schematically depicted
-in~\ref{fig:discrete-md}:
+in figure \ref{fig:discrete-md}:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{General Payment Primitives}
+\part{General Payment Primitives}\label{part:gpp}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Superfluid Protocol - A Reference Implementation}
+\part{Superfluid Protocol - A Reference Implementation}\label{part:sf}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}[p]
+\begin{figure}[h!]
     \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Final Words}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Notes on Future Investigations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Restatement in Agda, Correctness and Equivalence Proofs}
+\part*{Notes on Future Investigations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Restatement in Agda, Correctness and Equivalence Proofs}
 
@@
 
-\subsection{Future Papers on Modern Payment System}
+\section{Future Papers on Modern Payment System}
 
@@
 
-\subsection{General Accounting Domains \& Real Time Finance}
+\section{General Accounting Domains \& Real Time Finance}
 
@@
 
-\section{Conclusions}
-%%%%%%%%%%%%%%%%%%%%%
-
 \emph{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\part*{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This paper defines the what constitutes a modern payment system formally specified using
@@
 
-\section{Acknowledgments}
-%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\part*{Acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-04 packages/spec-haskell/yellowpaper/Paper1.tex
fixed a round of proof-readings

@@
 Payment systems in information age are still largely modeled after their analog predecessors. While
-some electronic money payment systems do utilize computing technology and Internet, this paper
-presents a case that a true modernization can still be done by (a) making payments happening
-continuously over time (b) involving more than two parties in a payment if necessary (c) having
-compositional financial contracts.
+electronic money payment systems do utilize computing technology and Internet, this paper presents a
+case that a true modernization can be reached by (a) making payments happening continuously over
+time, (b) involving more than two parties in a payment if necessary, (c) having compositional
+financial contracts.
 
@@
 define payment primitives for modern payment system. Lastly, this paper also includes an overview
-of \textit{Superfluid protocol}, a reference implementation of the payment primitives and a its
+of \textit{Superfluid protocol}, a reference implementation of the payment primitives and its
 payment system.
 
-This paper also includes literate Haskell code that compiles as the constructive artifact for the
-formal specifications.
+This paper includes literate Haskell code that compiles as the constructive artifact for the formal
+specifications.
+
+This paper is the first one of the series yellow papers about modern payment system dubbed
+``semantic money''.
 
@@
 
-It should be fair to say, every aspect of money are controversial: the nature of money, the value of
+It should be fair to say, every aspect of money is controversial: the nature of money, the value of
 money, money and banking, and monetary reconstruction. Two major schools of thoughts about theory of
@@
 
-This yellow paper does not intend to address these controversies, but to focus on the function of
-money. According to Von Mises:
+This yellow paper does not intend to address these controversies, instead it focuses on the function
+of money. According to Von Mises:
 
@@
 
-This paper adds a new controversy to money, that is to present a survey challenging the preconceived
-notion of how money can perform its function of medium of exchange.
-
-In part\ref{part:foundation}, we shall first explore the foundation for the survey. Here we present
-a formal definition of payment system and its components. We then select a few relevant approaches
-used in computer science useful for modeling and defining formal specification for the payment
-system.
+This paper adds a new controversy to money, that is to present a foundation of what constitutes of
+a \textit{modern payment system} and a set of \textit{payment primitives} for the system, in order
+to challenge the preconceived notions of how money can perform its function of medium of exchange.
+
+In part\ref{part:foundation}, we shall first explore the foundation. Here we present a formal
+definition of payment system and its components. We then select a few relevant approaches used in
+computer science useful for modeling and defining formal specification for the payment system.
 
 One of the approaches is \textit{denotational semantics}, which is used in part \ref{part:gpp} of
-the paper to define the general payment primitives. Along with the denotational semantics, a
-restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our case,
-the denotative mathematical laws.} of it in \textit{Haskell programming language}
+the paper to define the \textit{general payment primitives}. Along with the denotational semantics,
+a restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our
+case, the denotative mathematical laws.} of it in \textit{Haskell programming language}
 (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
@@
 In part \ref{part:sf}, a reference implementation of the general payment primitives and its payment
-system called \textit{Superfluid Protocol} is introduced.
+system called \textit{Superfluid Protocol} is introduced with an overview of it.
 
@@
 
-It can be solely defined by these components:
+It is solely defined by these components:
 
@@
 
-    \item \textit{payment execution environment} performs payment primitives,
+    \item \textit{payment execution environment} performs payment primitives encoded
+    in \textit{financial contracts},
 
@@
 \begin{itemize}
-    \item Money can be distributed continuously over time, as opposed to be discrete.
+    \item Money can be distributed continuously over time, as opposed to be in discrete chunks.
 
@@
 This discrete nature of this money distribution model is schematically depicted
-in figure \ref{fig:discrete-md}:
+in figure \ref{fig:discrete-md}.
 
@@
 
-\subsubsection{Using Context}
+\subsubsection{Adding Context $\gamma$}
 
@@
 
-Before first time in this paper listing specification in Haskell, here are some highlights of
+Before the first time in this paper listing specification in Haskell, here are some highlights of
 conventions in the style of the code used.
+
+\paragraph{Language Extensions}
 
@@
 
+Other notable extensions used in the paper are: $FunctionalDependencies$, $TypeFamilies$,
+$TypeFamilyDependencies$, $GADTs$, $MultiWayIf$.
+
 \paragraph{Indexed Types and Type Equality}
@@
 implementation, \textit{FunctionalDependencies}, \textit{TypeFamilies}
-and \textit{TypeFamilyDependencies} are extensively used. And in order to make the code less
-cluttered, type quality operator $(\sim)$
-used. Here is an example:
+and \textit{TypeFamilyDependencies} are extensively used. As a consequence, the type signature can
+look very cluttered. In order to address that, type quality operator $(\sim)$ is also used. Here is
+an example snippets:
 
@@
 
-A payment primitive is a data type with a generator that creates payment primitive data from the
-shared context $ctx$, primitive specific argument $args$ and timestamp, along with an update of the
-shared context. Here is an example of generator for payment primitive \textit{a}:
-
-\begin{equation}
+A payment primitive is a data type with a generator function that produces payment primitive from
+the shared context $ctx$, primitive specific argument $args$ and timestamp $t$, along with an update
+of the shared context. Type signature \ref{eq:genPrim} is for the generator of payment
+primitive \textit{a}:
+
+\begin{equation}\label{eq:genPrim}
     genPrim_a :: ctx \rightarrow args_a \rightarrow t \rightarrow prim \times ctx
@@
 distribution\footnote{Specifically being monoidal, that is in short a set that has associative
-binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid.}
+binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid.}:
 
@@
 
-The best known primitive is instant transfer of monetary value between one monetary unit to
+The most known primitive is instant transfer of monetary value between one monetary unit to
 another. The introduction of context enables more primitives to be defined, and this will be
-discussed in later chapters.
+discussed in part \ref{part:gpp}.
 
@@
 
-It is out of scope for this paper to survey in-depth the problem space of the operation semantics of
-payment execution environments. Nonetheless, a simplified model and some potential extensions to it
-is discussed briefly.
+It is out of scope for this paper to survey in-depth the problem space of the operational semantics
+of payment execution environments. Nonetheless, a simplified model and some potential extensions to
+it is discussed briefly to place payment primitives in the big picture.
 
@@
 applications, negative values can have special meanings. In the following analysis, we call any
-money unit that has a negative monetary value insolvent.
+money unit that has a negative monetary value \textit{insolvent}.
 
@@
 
-To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value
-which is set aside in a solvency conditional financial contract, such that if a solvency condition
-arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the
-execution.
+To mitigate this uncertainty, a concept called \textit{buffer} is introduced. A buffer has a
+monetary value which is set aside in a solvency conditional financial contract, such that if a
+solvency condition arises, the buffer maybe drawn to cover the loss introduced by the
+nondeterministic timing of the execution.
 
@@
 
-But it introduces a different type of systemic risk, that is denial-of-service, since the system
-cannot advance the system time until all next executable contracts are executed.
+On the other hand, it introduces a different type of systemic risk, that is a kind of
+denial-of-service. It is due to that the complexity of $fcUpdate$ is $O(log(n))$, the system may not
+be able to advance its system time until all next executable contracts are executed.
 
@@
 systems. To prevent reinventing wheels, it is relevant to discuss first some approaches in computer
-science that are believed to help solving this challenge.
+science that are believed to help tackling this challenge.
 
@@
 
-Recall that we want our modernized payment systems to handle money distribution continuously over
-time, and its financial contracts compositional. A very closely related software design paradigm
-best known to address those needs is \textit{functional reactive programming (FRP)}.  It was first
-introduced by Conal Elliott \& Paul Hudak in solving multimedia
-animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
+Recall that we want our modern payment system to handle money distribution continuously over time,
+and its financial contracts compositional. A very closely related software design paradigm best
+known to address those needs is \textit{functional reactive programming (FRP)}.  It was first
+introduced by Conal Elliott \& Paul Hudak in solving multimedia animations
+(\cite{elliott1997functional}). Later on, Hudak also worked on \cite{hudak2002arrows} and
 \cite{wan2000functional} making FRP a more general framework for programming hybrid system with
@@
 After FRP got more adoption, it evolved to some variations that support discrete semantics, and some
-variations better suited more for interactive systems. In this paper we will stick to and revisit
-the basic constructions of the original formulation used in \cite{elliott1997functional} where we
-will draw inspirations from.
+variations better suited for interactive systems. In this paper we will stick to and revisit the
+basic constructs of the original formulation used in \cite{elliott1997functional} where we will draw
+inspirations from.
 
@@
 Values that vary over continuous time are called \textit{behaviors}. They are first-class values,
-and are built up compositionally. In modernized payment systems, we should want the monetary values
-of monetary units capable of varying over continuous time. The semantic function of
-$\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given time:
+and are built up compositionally. That is what we want in modern payment system also. The semantic
+function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given time:
 
@@
 
-In modernized payment systems, the payment primitives executed in payment execution environments are
+In modern payment system, the payment primitives executed in payment execution environments are
 one type of events. More types of events can be read from the original paper \footfullcite[][section
@@
 
-In the context of modernized payment systems, the occurrences of payment primitives (events) change
-the behaviors of monetary units in how much monetary values it has over continuous. The building
-blocks of the financial contracts should be about modeling these events and their reactivity
-declaratively.
+In the context of modern payment system, the occurrences of payment primitives (events) change the
+behaviors of monetary units in how much monetary values it has over continuous. The building blocks
+of the financial contracts should be about modeling these events and their reactivity declaratively.
 
@@
 them as FRP-style \textit{Behavior} data types. In the following chapters, it is also unambiguously
-referred to in short as $[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie must be defined
+referred to in short as $[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie\ must be defined
 by structural recursion.
@@
 meaning to payment primitives, independent of its implementation (which deals with performance,
-optimization, side effects, etc.). We will spend the next chapter exploring the denotational
-semantics for general payment primitives in modernized payment systems.
+optimization, side effects, etc.). We will spend the part \ref{part:gpp} exploring the denotational
+semantics for general payment primitives in modern payment system.
 
@@
 argue for a restatement in \textit{Agda} instead, for it has a richer dependently-type system for
-desirable constructive proofs. This matter will be dealt in the ``future investigations'' chapter of
+desirable constructive proofs. This matter will be dealt in the ``future investigations'' section of
 this paper.}.
@@
     \item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ evaluates
-the syntax of money distribution, payment primitives, etc.
+the expression of money distribution, payment primitives, etc.
 \end{itemize}
@@
 
-And it must satisfy the following law:
+To make it meaningful, it must satisfy the following law:
 
@@
 
-\subsection{Proportional Distribution Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A special case of the indexed primitives is to fix the sender side to be an \textit{universal index}.
+\paragraph{Proportional Distribution Primitives}
+
+A special case of the indexed primitives is to fix the sender side to be an \textit{universal
+index}.
 
@@
 
-An even more powerful abstraction is to model participants involved a payment primitive
+An even more general abstraction is to model participants involved a payment primitive
 a \textit{network} (we use symbol $w$ for them).
@@
 needed in implementation when more specialized versions are used instead\footnote{We will not though
-discuss the subjective aspects, including in software engineering principles such as YAGNI
+discuss the subjective aspects, \eg\ in software engineering principles such as YAGNI
 (\url{https://en.wikipedia.org/wiki/You_aren't_gonna_need_it}), or user experience perspective of
@@
 
-In the next chapter, we will look into a reference implementation where these optimizations are
-applied.
+In part \ref{part:sf}, we will look into a reference implementation where these optimizations are
+made.
 
@@
 
-Superfluid protocol (``the protocol'')\footnote{The code base is available
+\textit{Superfluid protocol} (``the protocol'')\footnote{The code base is available
 at \url{https://github.com/superfluid-finance/protocol-monorepo/}.} is the first implementation of
 the \textit{denotational semantics of payment primitives} (though before it was formalized and named
-so) on \textit{Ethereum Virtual Machine} \cite{wood2014ethereum}. The first version of the protocol
-is written in Solidity programming language \footnote{\url{https://soliditylang.org/}}.
+so) on \textit{Ethereum Virtual Machine} (\cite{wood2014ethereum}). The first version of the protocol
+is written in Solidity programming language \footnote{\url{https://soliditylang.org/} - About
+Solidity programming language.}.
 
@@
 this paper and its sequels, an implementation in Haskell was created. It aims to implement the full
-specifications of (a) denotational semantics of payment primitives (b) compositional financial
-contracts for the payment primitives (c) token \& note model of money mediums, and their execution
+specifications of (a) denotational semantics of payment primitives, (b) compositional financial
+contracts for the payment primitives, (c) token \& note model of money mediums, and their execution
 environment.
 
-This paper covers the overview of the implementation of (a).
+This paper covers the overview of the implementation with regards to (a).
 
@@
 other financial purpose. The concept of \textit{real time balance} is thus created. \textit{Real
-time balance} is a functorful\footnote{Bartosz Milewski has an excellent series on these
-topics: \url{https://bartoszmilewski.com/2015/01/20/functors/}, and he uses the term ``functorful''
-to convey the idea of generalized container.} of monetary values. It can be converted to a single
-monetary value.
-
-Although since this is not the subject of this paper, it suffices to just show its definition
-instead:
+time balance} is a functorful\footnote{Bartosz Milewski has an excellent series on
+functors: \url{https://bartoszmilewski.com/2015/01/20/functors/}, where he uses the term
+``functorful'' to convey the idea of generalized container.} of monetary values. It can be converted
+to a single monetary value.
+
+Since this is not the subject of this paper, it suffices to show its definition instead:
 
@@
     \item preserve the program correctness (and if possible, with proof of equivalence),
-    \item optimize for efficient computation,
-    \item and provide a software interface for using it.
+    \item optimize for efficient computations,
+    \item and provide a software interface for it.
 \end{itemize}
@@
 
-\paragraph{Monetary Unit Data (MUD)}
-
-Recall that all monetary units have a monetary value function: $$ \nu :: u \rightarrow \mathbb{N}$$.
+\subsection{Monetary Unit Data (MUD)}
+
+Recall that all monetary units have a monetary value function: $ \nu :: u \rightarrow \mathbb{N}$.
 
@@
         => mud -> t -> rtb
+
+-- | A semigroup constrained monetary unit data type class.
+--
+-- Note: a. ~mud~ that doesn't have a binary function may also be referred
+--          to as "non-scalable" ~mud~.
+--
+--       a. What can make a ~mud~ "scalable" then is exactly when it is an
+--          actual semigroup. Since a new state can be merged onto the
+--          previous state to a new single state. It is still worth mentioning
+--          that it is only a sufficient condition, since a monoid could still
+--          "cheat" by linearly grow its data size on each binary operation.
+class ( MonetaryUnitDataClass smud sft
+      , Semigroup smud
+      ) => SemigroupMonetaryUnitData smud sft
 \end{code}
@@
 
-\paragraph{Agreement Contract}
+\subsection{Agreement Contract}
 
@@
       , MonetaryUnitDataClass ac sft
-      , Default (AgreementOperationOutput ac)
       , Traversable (AgreementOperationOutputF ac) -- <= Foldable Functor
+      , Monoid (AgreementOperationOutput ac)
       ) => AgreementContract ac sft | ac -> sft where
@@
         => ac -> ao -> t -> (ac, aoo)
+
+    -- | φ' function - functorize the existential semigroup monetary unit data
+    --                 of agreement operation output
+    functorizeAgreementOperationOutput
+        :: forall any_smud muds f.
+           ( any_smud `IsAnyTypeOf` MPTC_Flip SemigroupMonetaryUnitData sft
+           , MonetaryUnitDataClass any_smud sft
+           -- indexed type aliases
+           , muds ~ AgreementOperationOutput ac
+           , f ~ AgreementOperationOutputF ac
+           )
+        => Proxy any_smud
+        -> muds -> f any_smud
+
     data family AgreementOperation ac :: Type
@@
 
-Figure \ref{fig:ac-omega} is a visualization of ``machinery'' of the $\omega$ function:
-
-\begin{figure}[h]
+Figure \ref{fig:ac-omega} is a illustration of the $\omega$ function ``machinery''.
+
+\begin{figure}[H]
     \centering
@@
 
-It is also important to note that $AgreementContract$ itself is also a $MonetaryUnitDataClass$, but
-it is not a semigroup, hence it is used to replace the previous agreement contract data. This has
-optimization implications, as in that if agreement contracts do not produce zero balance then they
-must be included in the $\nu$ function, that can make the $\nu$ function $O(N)$ to the number of
-agreement contracts a monetary unit is associated with.
+It is also important to note that \textit{AgreementContract} itself is also
+a \textit{MonetaryUnitDataClass}, but it is not a semigroup, hence it is used to replace the
+previous agreement contract data. This has optimization implications, as in that if agreement
+contracts do not produce zero balance then they must be included in the $\nu$ function, that can
+make the $\nu$ function $O(N)$ to the number of agreement contracts a monetary unit is
+associated with.
 
@@
 
-\subsection{Lens Data Accessors}
+\section{Lens Data Accessors}
 
@@
 
-The pro-functor version of might seem very obscure at first, but its data representation is rather
-self-explanatory: a lens is simply a pair of getter ($view$) and setter ($update$) encoded in the
-data.
+The pro-functor version of lens might seem very obscure at first, but its data representation is
+rather self-explanatory: a lens is simply a pair of getter ($view$) and setter ($update$) encoded in
+the data.
 
@@
 
-\paragraph{Instant Value MUD}
+\section{Useful Agreements}
+
+\subsection{Instant Value MUD}
 
@@
 
-Note that (a) $^.$ is the view function (getter) for Lens types. (b) semigroup operator $(<>)$ defines
-how two monetary unit data can be combined into one.
-
-\paragraph{Constant Flow Agreement (CFA) MUD}
+Note that (a) lens \textbf{operator (\string^.)} is the view function (getter) of data, (b)
+semigroup \textbf{operator ($<>$)} defines how two monetary unit data can be combined into one.
+
+\subsection{Constant Flow Agreement (CFA) MUD}
 
@@
 
-\paragraph{Decaying Flow Agreement (CFA) MUD}
+\subsection{Decaying Flow Agreement (CFA) MUD}
 
@@
 
-\paragraph{Universal Index (UIDX)}
+\subsection{Universal Index (UIDX)}
 
@@
 
-\paragraph{Proportional Distribution Index (PDIDX)}
+\subsection{Proportional Distribution Index (PDIDX)}
 
@@
 
-\subsection{Hierarchy of Agreements}
+\section{Hierarchy of Agreements}
 
 To finish, figure \ref{fig:ac-agreement-data-structures} is the illustration of data structures for
-the denotational payment primitives implemented with agreement framework:
-
-\begin{figure}[h!]
+the denotational payment primitives implemented with agreement framework.
+
+\begin{figure}[H]
     \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\part*{Notes on Future Investigations}
+\part{Notes on Future Investigations}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-One of the advantages of using Haskell language was chosen to write the reference implementation is
-that it is a language with industrial strength, and the implementation could be easily integrated
-into a production code base without much performance compromises.
-
-However, a major disadvantage is that it is not equipped with sufficient apparatus for program
-correctness proofs. The best it can offer without engaging more experimental Haskell features is to
+One of the advantages of using Haskell language to write the reference implementation was its
+industrial strength. Because of that, the implementation could be easily integrated into a
+production code base without significant performance compromises.
+
+However, one major disadvantage is that it is not equipped with sufficient apparatus for program
+correctness proofs. The best it can offer without using more experimental Haskell features is to
 use \textit{QuickCheck}\footnote{\url{https://wiki.haskell.org/QuickCheck} - Haskell wiki page for
-QuickCheck.} to the necessary laws are not violated using randomized test vector.
+QuickCheck.} to test the necessary laws are not violated using randomized test vector.
 
@@
 dependently typed programming, often called "the Curry–Howard correspondence", as discovered and
-developed during the 20th century (explained in \cite by Phillip Wadler as ``Propositions as
-Types''). Agda being a dependently typed functional programming language fully embodies this
-insight, hence a good candidate for creating provable correct program.
-
-To learn more about Agda, see refer to these footnotes\footnote{\url{https://plfa.github.io/} -
-Programming Language Foundations in
-Agda.} \footnote{\url{https://wiki.portal.chalmers.se/agda/pmwiki.php} - Agda
-Wiki.} \footnote{\url{https://wiki.portal.chalmers.se/agda/Main/Community} - Agda community page.}.
+developed during the 20th century (explained in \cite{wadler2015propositions} by Phillip Wadler as
+``Propositions as Types''). Agda being a dependently typed functional programming language fully
+embodies this insight, hence a good candidate for creating provable correct program.
+
+To learn more about Agda, refer to these footnotes
+\footnote{\url{https://plfa.github.io/} - Programming Language Foundations in Agda.}
+\footnote{\url{https://wiki.portal.chalmers.se/agda/pmwiki.php} - Agda Wiki.}
+\footnote{\url{https://wiki.portal.chalmers.se/agda/Main/Community} - Agda community page.}.
 
@@
 The execution environments for these financial contracts are also fertile ground for new ideas, from
-deterministic execution to avoid the usage of buffer, to using distributed ledger technology to
+deterministic execution avoiding the usage of buffer, to using distributed ledger technology to
 deep-embed these financial contracts in the consensus layer.
@@
 the \textit{general accounting domain} specifically for financial contracts in dealing with payment
-primitives, a real time version of the cash flow accounting. It is a long with other types,
-including balance sheet accounting, income statement accounting. The conversion between these
-instances of general accounting domains are often called ``reconciliations''.
+primitives, which can be seen as a real time version of the cash flow accounting. Along with balance
+sheet accounting, income statement accounting, the conversion between these instances of general
+accounting domains are often called ``reconciliations''.
 
@@
 reconciliations.
+
+\paragraph{Real Time Finance}
 
@@
 modernized to handle money distribution continuously over time, its financial contracts are
-compositional, and its general accounting domain are automated and processed in real time.
-}
+compositional, and its general accounting domain are automated and processed in real time.  }
 
@@
 
-This paper defines the what constitutes a modern payment system formally specified using
-denotational semantics and restated using Haskell programming language.
+This paper defines the what constitutes a modern payment system, with its payment primitives
+formally specified using denotational semantics and restated using Haskell programming
+language. Along with a reference implementation of the specification, we want to make a case that
+marrying with the progress of computer science, the notation of money can perform its function of
+medium of exchange can have a modern upgrade.
+
+Absent of any claim on whether if such modern upgrade is needed, we ask the readers ask
+ourselves a question together: with electronic money increasingly being used, should we keep
+emulating the function money of its traditional quality, or could we rethink what it may be in the
+information age?
 

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Concepts/Agreement.hs

@@ -28,8 +28,9 @@ import           Money.Systems.Superfluid.CoreTypes
 class ( SuperfluidCoreTypes sft
       , Default ac
       , MonetaryUnitDataClass ac sft
-      , Default (AgreementOperationOutput ac)
       , Traversable (AgreementOperationOutputF ac) -- <= Foldable Functor
+      -- , Monoid (AgreementOperationOutput ac)
+      , Default (AgreementOperationOutput ac)
       ) => AgreementContract ac sft | ac -> sft where
 
     -- | ω function - apply agreement operation ~ao~ (hear: ω) to the agreement operation data ~ac~ to get a tuple of:

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/ProportionalDistribution/ConstantFlowDistributionAgreement.hs
agreement operation output is monoid

@@ -123,9 +123,6 @@ instance SuperfluidSystemTypes sft => AgreementContract (PublisherContract sft) 
                                    , dc_flow_rate      = dcfr
                                    } = dc
 
-    concatAgreementOperationOutput (PublisherOperationOutputF a) (PublisherOperationOutputF a') =
-        PublisherOperationOutputF (a <> a')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (PublisherContract sft) = UpdateDistributionFlowRate (SFT_MVAL sft)
@@ -140,6 +137,9 @@ type PublisherOperationOutput sft = AgreementOperationOutputF (PublisherContract
     (PublisherMonetaryUnitData sft)
 
 instance SuperfluidSystemTypes sft => Default (PublisherOperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (PublisherOperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (PublisherOperationOutput sft) where
+    PublisherOperationOutputF a <> PublisherOperationOutputF a' = PublisherOperationOutputF (a <> a')
 
 -- * Subscriber Operations
 
@@ -178,9 +178,6 @@ instance SuperfluidSystemTypes sft => AgreementContract (SubscriberContract sft)
                                    , sc_settled_value_per_unit = svpu
                                    } = sc
 
-    concatAgreementOperationOutput (SubscriberOperationOutputF a) (SubscriberOperationOutputF a') =
-        SubscriberOperationOutputF (a <> a')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (SubscriberContract sft) = SettleSubscription
@@ -195,3 +192,6 @@ type SubscriberOperationOutput sft = AgreementOperationOutputF (SubscriberContra
     (PublisherMonetaryUnitData sft)
 
 instance SuperfluidSystemTypes sft => Default (SubscriberOperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (SubscriberOperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (SubscriberOperationOutput sft) where
+    SubscriberOperationOutputF a <> SubscriberOperationOutputF a' = SubscriberOperationOutputF (a <> a')

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/ProportionalDistribution/InstantDistributionAgreement.hs

@@ -91,23 +91,23 @@ instance SuperfluidSystemTypes sft => AgreementContract (PublisherContract sft) 
         where DistributionContractBase { total_unit = tu} = dcBase
               DistributionContract { dc_value_per_unit = vpu } = dc
 
-    concatAgreementOperationOutput (PublisherOperationOutputF a) (PublisherOperationOutputF a') =
-        PublisherOperationOutputF (a <> a')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (PublisherContract sft) = Distribute (SFT_MVAL sft)
 
-    type AgreementOperationOutput (PublisherContract sft) = PublisherOperationOutputF sft
+    type AgreementOperationOutput (PublisherContract sft) = PublisherOperationOutput sft
 
     data AgreementOperationOutputF (PublisherContract sft) elem = PublisherOperationOutputF
         elem -- publisher
         deriving stock (Functor, Foldable, Traversable, Generic)
 
-type PublisherOperationOutputF sft = AgreementOperationOutputF (PublisherContract sft)
+type PublisherOperationOutput sft = AgreementOperationOutputF (PublisherContract sft)
     (PublisherMonetaryUnitData sft)
 
-instance SuperfluidSystemTypes sft => Default (PublisherOperationOutputF sft)
+instance SuperfluidSystemTypes sft => Default (PublisherOperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (PublisherOperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (PublisherOperationOutput sft) where
+    PublisherOperationOutputF a <> PublisherOperationOutputF a' = PublisherOperationOutputF (a <> a')
 
 -- * Subscriber Operations
 
@@ -133,17 +133,17 @@ instance SuperfluidSystemTypes sft => AgreementContract (SubscriberContract sft)
                                    , sc_settled_value_per_unit = svpu
                                    } = sc
 
-    concatAgreementOperationOutput _ a = a
-
     functorizeAgreementOperationOutput _ _ = SubscriberOperationOutputF
 
     data AgreementOperation (SubscriberContract sft) = SettleSubscription
 
-    type AgreementOperationOutput (SubscriberContract sft) = SubscriberOperationOutputF sft
+    type AgreementOperationOutput (SubscriberContract sft) = SubscriberOperationOutput sft
 
[…]

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/ProportionalDistributionIndex.hs

@@ -100,21 +100,26 @@ instance SuperfluidSystemTypes sft => AgreementContract (SubscriberContract sft)
                                 , sub_settled_at = t'
                                 }})
 
-        in (ac', cfdaMUDΔ)
+        in (ac', SubscriberOperationOutput cfdaMUDΔ)
 
         where DistributionContract { dc_base = DistributionContractBase { total_unit = tu }} = dc0
               SubscriptionContract { sc_base = SubscriptionContractBase { sub_owned_unit = u }} = sc0
 
-    concatAgreementOperationOutput cfda cfda' = cfda <> cfda'
-
-    functorizeAgreementOperationOutput p cfda = SubscriberOperationOutputF
-        (mkAny p cfda)
+    functorizeAgreementOperationOutput p (SubscriberOperationOutput cfda) =
+        SubscriberOperationOutputF (mkAny p cfda)
 
     data AgreementOperation (SubscriberContract sft) = Subscribe (SFT_FLOAT sft)
 
-    type AgreementOperationOutput (SubscriberContract sft) =
-        (CFDA.PublisherMonetaryUnitData sft)
+    type AgreementOperationOutput (SubscriberContract sft) = SubscriberOperationOutput sft
 
     data AgreementOperationOutputF (SubscriberContract sft) elem = SubscriberOperationOutputF
         { subscription_output_cfda :: elem
         } deriving stock (Functor, Foldable, Traversable)
+
+data SubscriberOperationOutput sft = SubscriberOperationOutput
+    (CFDA.PublisherMonetaryUnitData sft)
+    deriving stock (Generic)
+
+instance SuperfluidSystemTypes sft => Default (SubscriberOperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (SubscriberOperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (SubscriberOperationOutput sft) where (<>) = const

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/Universal/ConstantFlowAgreement.hs

@@ -70,20 +70,20 @@ instance SuperfluidSystemTypes sft => AgreementContract (ContractData sft) sft w
                      & set CFMUD.netFlowRate  flowRateΔ)
         in (ac', fmap CFMUD.MkMonetaryUnitData mudsΔ)
 
-    concatAgreementOperationOutput (OperationOutputF a b) (OperationOutputF a' b') =
-        OperationOutputF (a <> a') (b <> b')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (ContractData sft) = UpdateFlow (FlowRate sft)
 
-    type AgreementOperationOutput (ContractData sft) = OperationOutputF sft
+    type AgreementOperationOutput (ContractData sft) = OperationOutput sft
 
     data AgreementOperationOutputF (ContractData sft) a = OperationOutputF
         { flow_sender   :: a
         , flow_receiver :: a
         } deriving stock (Functor, Foldable, Traversable, Generic)
 
-type OperationOutputF sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
+type OperationOutput sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
 
-instance SuperfluidSystemTypes sft => Default (OperationOutputF sft)
+instance SuperfluidSystemTypes sft => Default (OperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (OperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (OperationOutput sft) where
+    OperationOutputF a b <> OperationOutputF a' b' = OperationOutputF (a <> a') (b <> b')

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/Universal/DecayingFlowAgreement.hs

@@ -73,21 +73,21 @@ instance SuperfluidSystemTypes sft => AgreementContract (ContractData sft) sft w
 
         in (ac', fmap DFMUD.MkMonetaryUnitData mudsΔ)
 
-    concatAgreementOperationOutput (OperationOutputF a b) (OperationOutputF a' b') =
-        OperationOutputF (a <> a') (b <> b')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (ContractData sft) =
         UpdateDecayingFlow (DistributionLimit sft)
 
-    type AgreementOperationOutput (ContractData sft) = OperationOutputF sft
+    type AgreementOperationOutput (ContractData sft) = OperationOutput sft
 
     data AgreementOperationOutputF (ContractData sft) elem = OperationOutputF
         { flow_sender   :: elem
         , flow_receiver :: elem
         } deriving stock (Functor, Foldable, Traversable, Generic)
 
-type OperationOutputF sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
+type OperationOutput sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
 
-instance SuperfluidSystemTypes sft => Default (OperationOutputF sft)
+instance SuperfluidSystemTypes sft => Default (OperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (OperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (OperationOutput sft) where
+    OperationOutputF a b <> OperationOutputF a' b' = OperationOutputF (a <> a') (b <> b')

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/Universal/InstantTransferAgreement.hs

@@ -50,20 +50,20 @@ instance SuperfluidSystemTypes sft => AgreementContract (ContractData sft) sft w
                     (def & set IVMUD.untappedValue (coerce    amount)))
         in (ac', mudsΔ)
 
-    concatAgreementOperationOutput (OperationOutputF a b) (OperationOutputF a' b') =
-        OperationOutputF (a <> a') (b <> b')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (ContractData sft) = Transfer (SFT_MVAL sft)
 
-    type AgreementOperationOutput (ContractData sft) = OperationOutputF sft
+    type AgreementOperationOutput (ContractData sft) = OperationOutput sft
 
     data AgreementOperationOutputF (ContractData sft) elem = OperationOutputF
         { transfer_from :: elem
         , transfer_to   :: elem
         } deriving stock (Functor, Foldable, Traversable, Generic)
 
-type OperationOutputF sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
+type OperationOutput sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
 
-instance SuperfluidSystemTypes sft => Default (OperationOutputF sft)
+instance SuperfluidSystemTypes sft => Default (OperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (OperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (OperationOutput sft) where
+    OperationOutputF a b <> OperationOutputF a' b' = OperationOutputF (a <> a') (b <> b')

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/Universal/MinterAgreement.hs

@@ -59,21 +59,21 @@ instance SuperfluidSystemTypes sft => AgreementContract (ContractData sft) sft w
                 (def & set MVMUD.untappedValue (coerce (- amount))))
         in (ac', mudsΔ)
 
-    concatAgreementOperationOutput (OperationOutputF a b) (OperationOutputF a' b') =
-        OperationOutputF (a <> a') (b <> b')
-
     functorizeAgreementOperationOutput p = fmap (mkAny p)
 
     data AgreementOperation (ContractData sft) = Mint (SFT_MVAL sft) |
                                                  Burn (SFT_MVAL sft)
 
-    type AgreementOperationOutput (ContractData sft) = OperationOutputF sft
+    type AgreementOperationOutput (ContractData sft) = OperationOutput sft
 
     data AgreementOperationOutputF (ContractData sft) elem = OperationOutputF
         { mint_from :: elem
         , mint_to   :: elem
         } deriving stock (Functor, Foldable, Traversable, Generic)
 
-type OperationOutputF sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
+type OperationOutput sft = AgreementOperationOutputF (ContractData sft) (MonetaryUnitData sft)
 
-instance SuperfluidSystemTypes sft => Default (OperationOutputF sft)
+instance SuperfluidSystemTypes sft => Default (OperationOutput sft)
+instance SuperfluidSystemTypes sft => Monoid (OperationOutput sft) where mempty = def
+instance SuperfluidSystemTypes sft => Semigroup (OperationOutput sft) where
+    OperationOutputF a b <> OperationOutputF a' b' = OperationOutputF (a <> a') (b <> b')

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Concepts/Agreement.hs

@@ -29,8 +29,7 @@ class ( SuperfluidCoreTypes sft
       , Default ac
       , MonetaryUnitDataClass ac sft
       , Traversable (AgreementOperationOutputF ac) -- <= Foldable Functor
-      -- , Monoid (AgreementOperationOutput ac)
-      , Default (AgreementOperationOutput ac)
+      , Monoid (AgreementOperationOutput ac)
       ) => AgreementContract ac sft | ac -> sft where
 
     -- | ω function - apply agreement operation ~ao~ (hear: ω) to the agreement operation data ~ac~ to get a tuple of:
@@ -60,12 +59,6 @@ class ( SuperfluidCoreTypes sft
         => Proxy any_smud
         -> muds -> f any_smud
 
-    -- | κ function - concatenate agreement operation output, which can be functorized any time.
-    concatAgreementOperationOutput
-        :: forall muds.
-           muds ~ AgreementOperationOutput ac
-        => muds -> muds -> muds
-
     -- Note: though ~ac~ is injected, but it seems natural to have operation as associated data type instead.
     data family AgreementOperation ac :: Type
 
@@ -85,7 +78,6 @@ instance SuperfluidCoreTypes sft => MonetaryUnitDataClass (NullAgreementContract
 instance SuperfluidCoreTypes sft => AgreementContract (NullAgreementContract sft) sft where
     applyAgreementOperation ac _ _ = (ac, NullAgreementOutoutF)
     functorizeAgreementOperationOutput _ _ = NullAgreementOutoutF
-    concatAgreementOperationOutput = const
     data AgreementOperation (NullAgreementContract sft) = NullAgreementOperation
     data AgreementOperationOutputF (NullAgreementContract sft) _ = NullAgreementOutoutF
         deriving stock (Functor, Foldable, Traversable)
@@ -94,6 +86,8 @@ instance SuperfluidCoreTypes sft => AgreementContract (NullAgreementContract sft
 type NullAgreementOutout sft = AgreementOperationOutputF (NullAgreementContract sft) ()
 
 instance SuperfluidCoreTypes sft => Default (NullAgreementOutout sft) where def = def
+instance SuperfluidCoreTypes sft => Monoid (NullAgreementOutout sft) where mempty = def
+instance Semigroup (NullAgreementOutout sft) where (<>) = const
 
 -- * Agreement Contract State
 
[…]

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Token.hs

@@ -188,7 +188,7 @@ class ( Monad tk
             setContract (PDIDX.SubscriberOperationOutputF addr) (dc', sc') t = do
                 overProportionalDistributionContract addr indexId (const dc') t
                 overProportionalDistributionSubscription subscriber addr indexId (const sc') t
-        (t, aoAccounts, cfdaMUDΔ)  <- eff_agreement_operation_base
+        (t, aoAccounts, PDIDX.SubscriberOperationOutput cfdaMUDΔ)  <- eff_agreement_operation_base
             (PDIDX.SubscriberOperationOutputF publisher)
             (PDIDX.Subscribe unit)
             viewContract

### 2022-10-04 packages/spec-haskell/packages/core/test/Money/Systems/Superfluid/ConstantFlowDistributionAgreement_prop.hs

@@ -65,13 +65,13 @@ ao_1pub2subs_zero_sum_balance t0 aos0 = go (getNonEmpty aos0) t0 (def, def) def 
               where t' = t + tΔ
           go ((TO_1Pub2Subs (PubOp2 _), _) :_) _ _ _ _ = error "huh? there is no pub2"
           go ((TO_1Pub2Subs (SubOp1 ao), tΔ):aos) t (dcFull, pubMuds) scFull1 scFull2 =
-              let (isGood, ((dcFull', scFull1'), pubMudsΔ)) = single_op
+              let (isGood, ((dcFull', scFull1'), PDIDX.SubscriberOperationOutput pubMudsΔ)) = single_op
                       t' (dcFull, pubMuds) scFull1 scFull2
                       ((dcFull, scFull1), def) ao
               in  isGood && go aos t' (dcFull', pubMuds <> pubMudsΔ) scFull1' scFull2
               where t' = t + tΔ
           go ((TO_1Pub2Subs (SubOp2 ao), tΔ):aos) t (dcFull, pubMuds) scFull1 scFull2 =
-              let (isGood, ((dcFull', scFull2'), pubMudsΔ)) = single_op
+              let (isGood, ((dcFull', scFull2'), PDIDX.SubscriberOperationOutput pubMudsΔ)) = single_op
                       t' (dcFull, pubMuds) scFull1 scFull2
                       ((dcFull, scFull2), def) ao
               in  isGood && go aos t' (dcFull', pubMuds <> pubMudsΔ) scFull1 scFull2'
@@ -122,13 +122,13 @@ ao_2pubs1sub_zero_sum_balance t0 aos0 = go (getNonEmpty aos0) t0 (def, def) (def
               in  isGood && go aos t' (dcFull1, pubMuds1) (dcFull2', pubMuds2') scFull1 scFull2
               where t' = t + tΔ
           go ((TO_2Pubs1Sub (SubOp1 ao), tΔ):aos) t (dcFull1, pubMuds1) (dcFull2, pubMuds2) scFull1 scFull2 =
-              let (isGood, ((dcFull1', scFull1'), pubMuds1Δ)) = single_op
+              let (isGood, ((dcFull1', scFull1'), PDIDX.SubscriberOperationOutput pubMuds1Δ)) = single_op
                       t' (dcFull1, pubMuds1) (dcFull2, pubMuds2) scFull1 scFull2
[…]

### 2022-10-04 packages/spec-haskell/yellowpaper/Paper1.tex
agreement operation output is monoid
adding decaying flow

@@
 \part*{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 
@@
 Other notable extensions used in the paper are: $FunctionalDependencies$, $TypeFamilies$,
-$TypeFamilyDependencies$, $GADTs$, $MultiWayIf$.
+$TypeFamilyDependencies$, $GADTs$.
 
@@
 
-It should be easy to prove that they satisfy the \textit{axioms A of restricted money distribution}.
+\paragraph{Decaying Flow}
+
+Another way monetary value could flow is through an exponential decay
+function\footnote{\url{https://en.wikipedia.org/wiki/Exponential_decay}.}.
+
+Symbolically, this process can be expressed by the following differential equation, where N is the
+quantity and $\lambda$ is a positive rate called the exponential decay constant:
+
+\begin{equation}
+    {\displaystyle {\frac {dN}{dt}}=-\lambda N}
+\end{equation}
+
+The solution to this equation (see derivation below) is:
+
+\begin{equation}
+    {\displaystyle N(t)=N_{0}e^{-\lambda t}}
+\end{equation}
+
+But a more convenient semantics of it uses the parameter called ``distribution limit'' ($\theta$)
+instead. In this formulation, a decaying flow distributes $\epsilon$ amount of monetary value at a
+rate started at $\alpha$ and halving every time period of $\displaystyle \frac{ln(2)}{\lambda}$:
+
+\begin{equation}
+    \begin{split}
+        [\![decayingFlow\ u_a\ u_b\ \theta\ \lambda\ t']\!] &=
+        \lambda u \rightarrow \lambda t \rightarrow \\
+        &\begin{cases}
+             {\displaystyle  \alpha \cdot e^{-\lambda (t' - t)} - \theta} & (u_a = u) \\
+             {\displaystyle -\alpha \cdot e^{-\lambda (t' - t)} + \theta} & (u_b = u) \\
+             0 & (otherwise)
+        \end{cases}
+    \end{split}
+\end{equation}
+
+For the simplicity of the later discussion, this form of payment primitive is omitted.
 

### 2022-10-04 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/Agreements/Universal/DecayingFlowAgreement.hs

@@ -61,8 +61,8 @@ instance SuperfluidSystemTypes sft => AgreementContract (ContractData sft) sft w
         θ_Δ = fromIntegral (θ - distribution_limit ac)
 
         ac' = ContractData { distribution_limit   = θ
-                            , flow_last_updated_at = t'
-                            }
+                           , flow_last_updated_at = t'
+                           }
         mudsΔ = OperationOutputF
                 (def & set DFMUD.settledAt    t'
                      & set DFMUD.αVal        θ_Δ

### 2022-10-19 packages/spec-haskell/yellowpaper/Paper1.tex
typo fixes

@@
 
-This paper is the first one of the series yellow papers about modern payment system dubbed
+This paper is also the first one in the series of yellowpapers about modern payment system dubbed
 ``semantic money''.
@@
 
-In part\ref{part:foundation}, we shall first explore the foundation. Here we present a formal
+In part \ref{part:foundation}, we shall first explore the foundation. Here we present a formal
 definition of payment system and its components. We then select a few relevant approaches used in
@@
 language. Along with a reference implementation of the specification, we want to make a case that
-marrying with the progress of computer science, the notation of money can perform its function of
-medium of exchange can have a modern upgrade.
-
-Absent of any claim on whether if such modern upgrade is needed, we ask the readers ask
+marrying with the progress of computer science, the way of money performing its function of medium
+of exchange can have a modern upgrade.
+
+Absent of any claim on whether if such modern upgrade is needed, we invite the readers to ask
 ourselves a question together: with electronic money increasingly being used, should we keep

### 2022-10-19 packages/spec-haskell/packages/core/src/Money/Systems/Superfluid/MonetaryUnitData/ConstantFlow.hs
Yellowpaper 1 - Denotational Semantics of General Payment Primitives, and Its Payment System (#1105)

@@ -13,22 +13,24 @@ import           Lens.Internal
 
 import           Money.Systems.Superfluid.SystemTypes
 
-class (Default amuLs, SuperfluidSystemTypes sft) => MonetaryUnitLenses amuLs sft | amuLs -> sft where
-    settledAt          :: Lens' amuLs (SFT_TS sft)
-    settledValue       :: Lens' amuLs (UntappedValue (SFT_MVAL sft))
-    netFlowRate        :: Lens' amuLs (SFT_MVAL sft)
+class ( Default amuLs
+      , SuperfluidSystemTypes sft
+      ) => MonetaryUnitLenses amuLs sft | amuLs -> sft where
+    settledAt    :: Lens' amuLs (SFT_TS sft)
+    settledValue :: Lens' amuLs (UntappedValue (SFT_MVAL sft))
+    netFlowRate  :: Lens' amuLs (SFT_MVAL sft)
 
 type MonetaryUnitData :: Type -> Type -> Type
 newtype MonetaryUnitData amuLs sft = MkMonetaryUnitData { getMonetaryUnitLenses :: amuLs } deriving (Default)
 
 instance MonetaryUnitLenses amuLs sft => Semigroup (MonetaryUnitData amuLs sft) where
-    (<>) (MkMonetaryUnitData a) (MkMonetaryUnitData b) =
+    MkMonetaryUnitData a <> MkMonetaryUnitData b =
         let t  = a^.settledAt
             t' = b^.settledAt
             settledΔ = MkUntappedValue $ a^.netFlowRate * fromIntegral (t' - t)
-            c = a & set  settledAt t'
-                  & over netFlowRate        (+ b^.netFlowRate)
-                  & over settledValue       (+ (b^.settledValue + settledΔ))
+            c = a & set  settledAt    t'
+                  & over netFlowRate  (+ b^.netFlowRate)
+                  & over settledValue (+ (b^.settledValue + settledΔ))
         in MkMonetaryUnitData c
 
 instance MonetaryUnitLenses amuLs sft => MonetaryUnitDataClass (MonetaryUnitData amuLs sft) sft where

### 2022-10-31 packages/spec-haskell/yellowpaper/Paper1.tex
remove acks.
errata and gramatic fixes after reviews

@@
 \begin{abstract}
-Payment systems in information age are still largely modeled after their analog predecessors. While
-electronic money payment systems do utilize computing technology and Internet, this paper presents a
-case that a true modernization can be reached by (a) making payments happening continuously over
-time, (b) involving more than two parties in a payment if necessary, (c) having compositional
+Payment systems in the information age are still modeled after their analog predecessors. While
+electronic money payment systems do utilize computing technology and the Internet, this paper
+presents a case that true modernization can be reached by (a) making payments happening continuously
+over time, (b) involving more than two parties in payment if necessary, (c) having compositional
 financial contracts.
 
-This paper first explores the foundation of modern payment system, which consists of a money
-distribution model, payment primitives, payment execution systems of financial contracts and
+This paper first explores the foundation of modern payment systems, which consists of a money
+distribution model, payment primitives, payment execution systems of financial contracts, and
 different forms of money mediums. Then the paper uses \textit{denotational semantics} to formally
-define payment primitives for modern payment system. Lastly, this paper also includes an overview
-of \textit{Superfluid protocol}, a reference implementation of the payment primitives and its
+define payment primitives for modern payment systems. By the end, this paper includes an overview of
+the \textit{Superfluid protocol}, a reference implementation of the payment primitives, and its
 payment system.
 
-This paper includes literate Haskell code that compiles as the constructive artifact for the formal
-specifications.
-
-This paper is also the first one in the series of yellowpapers about modern payment system dubbed
-``semantic money''.
+This paper is the first in the series of yellowpapers about modern payment systems dubbed ``semantic
+money.''
 
 \end{abstract}
+
+\begin{versionhistory}
+  \vhEntry{0.9}{2022-10-19}{MZC}{For reviews}
+  \vhEntry{1.0}{2022-10-31}{MZC}{First release}
+\end{versionhistory}
 
@@
 
-It should be fair to say, every aspect of money is controversial: the nature of money, the value of
-money, money and banking, and monetary reconstruction. Two major schools of thoughts about theory of
-money are the \textit{Austrian school} (\cite{von2013theory}) and the \textit{Chicago school}
-(\cite{friedman1989quantity}). That is before the appearance of Internet-era version of monetary
-reconstruction, broadly defined as cryptocurrency, which challenges theories of money further and
-demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
-
-This yellow paper does not intend to address these controversies, instead it focuses on the function
-of money. According to Von Mises:
+It should be fair to say every aspect of money is controversial: the nature of money, the value of
+money, money and banking, and monetary reconstruction. Two major schools of thought about the theory
+of money are the \textit{Austrian school} (\cite{von2013theory}) and the \textit{Chicago school}
+(\cite{friedman1989quantity}). That was before the appearance of the Internet-era version of
+monetary reconstruction, broadly defined as cryptocurrency, which challenges theories of money
+further and demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
+
+This yellow paper does not intend to address these controversies; instead, it focuses on the
+function of money. According to Von Mises:
 
@@
 
-How do different forms of money perform this function, especially in the information age, when
-electronic forms of money are increasingly used?
-
-This paper adds a new controversy to money, that is to present a foundation of what constitutes of
-a \textit{modern payment system} and a set of \textit{payment primitives} for the system, in order
-to challenge the preconceived notions of how money can perform its function of medium of exchange.
+How do different forms of money perform this function, especially in the information age, when we
+increasingly use electronic forms of money?
+
+This paper adds a new controversy to money, presenting a foundation of what constitutes
+a \textit{modern payment system} and a set of \textit{payment primitives} for the system to
+challenge the preconceived notions of how money can perform its function of medium of exchange.
 
 In part \ref{part:foundation}, we shall first explore the foundation. Here we present a formal
-definition of payment system and its components. We then select a few relevant approaches used in
-computer science useful for modeling and defining formal specification for the payment system.
+definition of a payment system and its components. We then select a few relevant approaches used in
+computer science useful for modeling and defining formal specifications for the payment system.
 
@@
 the paper to define the \textit{general payment primitives}. Along with the denotational semantics,
-a restatement\footnote{It is a borrowed term from common law: ``restatement of the law''. In our
-case, the denotative mathematical laws.} of it in \textit{Haskell programming language}
-(\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
-
-In part \ref{part:sf}, a reference implementation of the general payment primitives and its payment
-system called \textit{Superfluid Protocol} is introduced with an overview of it.
-
-Notes on possible further investigations are also included in the end of the paper.
+the paper also includes a restatement\footnote{It is a borrowed term from common law: ``restatement
+of the law''. In our case, the denotative mathematical laws.} of it in \textit{Haskell programming
+language} (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}).
+
+In part \ref{part:sf}, we introduce a reference implementation of the general payment primitives and
+its payment system called \textit{Superfluid Protocol}, along with its overview.
+
+The end of the paper also includes notes on possible further investigations.
 
@@
 
-Here we present a definition of payment system and its components.
+Here we present a definition of a payment system and its components.
 
@@
 
-    \item \textit{payment primitives} updates money distribution,
+    \item \textit{payment primitives} update money distribution,
 
@@
 \begin{itemize}
-    \item Money can be distributed continuously over time, as opposed to be in discrete chunks.
-
-    \item Payment primitives can involve more than two parties, as opposed to be only for a sender
-and a receiver.
-
-    \item Financial system should be compositional.
+    \item Money can be distributed continuously over time, as opposed to being in discrete chunks.
+
+    \item Payment primitives can involve more than two parties, as opposed to being only for a
+sender and a receiver.
+
+    \item Financial systems should be compositional.
 \end{itemize}
@@
 A representation of money and its distribution proposed in ``a unifying theory''
-from \citeauthor{buldas2021unifying} involves the following components:
+by \citeauthor{buldas2021unifying} involves the following components:
 
@@
 
-    \item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of
-every value unit u. The set $\mathbb{N}$ is the set of all natural numbers, but instead, we can use
-any set of numerals that is totally ordered (\eg\ integers, real numbers).
-
-    \item $\beta : U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$
-of a unit. The set $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal
-construction defining any type of legal entity, such as a person, a family, a company, a state
-institution, etc.
+    \item $\nu: U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of every
+value unit u. The set $\mathbb{N}$ is the set of all natural numbers, but instead, we can use any
+set of numerals that are totally ordered (\eg,\ integers, real numbers).
+
+    \item $\beta: U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$
+of a unit. $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal construction
+defining any type of legal entity, such as a person, a family, a company, a state institution, etc.
 \end{itemize}
@@
 But the discrete nature of the model does not provide the necessary element for us to add the
-desired properties to the payment system. Here we propose a modification that involves the usage
+desired properties to the payment system. So here we propose a modification that involves the usage
 of \textit{context ($\gamma$)}:
@@
 
-Note that in this model, context can be updated independently while value functions of the same
+Note that in this model, context can be updated independently, while value functions of the same
 money distribution can produce different monetary values.
@@
 
-Here are some possible components of context, and how they work:
+Here are some possible components of context and how they work:
 
 \begin{itemize}
-    \item If time (t) is included the context, then monetary value of each monetary unit can vary
-continuously over time. Time is part of the physical reality, hence not changeable by the actors in
-the payment system.
+    \item If time (t) is included in the context, then the monetary value of each monetary unit can
+vary continuously over time. Time is part of the physical reality, hence not changeable by the
+actors in the payment system.
 
@@
 information in context. This could enable payment primitives that involve many parties. This set of
-information in context is referred to as \textit{ctx :: SharedContext}, they can be changed over
+information in context is referred to as \textit{ctx :: SharedContext}; they can be changed over
 time by the actors in the payment system.
@@
 
-Before the first time in this paper listing specification in Haskell, here are some highlights of
-conventions in the style of the code used.
+Before the first time this paper includes specification in Haskell, here are some highlights of
+conventions in the code style.
 
@@
 
-In order to make the specification free of specific choices of core data types in
-implementation, \textit{FunctionalDependencies}, \textit{TypeFamilies}
+To make the specification free of specific choices of core data types in
+implementation, \textit{FunctionalDependencies}, \textit{TypeFamilies},
 and \textit{TypeFamilyDependencies} are extensively used. As a consequence, the type signature can
@@
 A payment primitive is a data type with a generator function that produces payment primitive from
-the shared context $ctx$, primitive specific argument $args$ and timestamp $t$, along with an update
+the shared context $ctx$, primitive specific argument $args$, and timestamp $t$, along with an update
 of the shared context. Type signature \ref{eq:genPrim} is for the generator of payment
@@
 
-Loosely speaking, it is considered a primitive, if it can not be broken down into other existing
-primitives which result in the same money distribution; additionally primitives should be the only
+Loosely speaking, it is considered primitive, if it can not be broken down into other existing
+primitives, which result in the same money distribution; additionally, primitives should be the only
 constructs in a payment system that can update money distribution.
 
-Updates are \textit{monoidal}, so that they can be incremental and their parallel executions can be
+Updates are \textit{monoidal} so that they can be incremental, and their parallel executions can be
 modeled.
 
-The most known primitive is instant transfer of monetary value between one monetary unit to
+The best-known primitive is an instant transfer of monetary value between one monetary unit to
 another. The introduction of context enables more primitives to be defined, and this will be
@@
 The purpose of a payment execution environment is to perform the actual payment primitives, where
-their computation interface, parallel evaluation strategies and payment system solvency are defined.
+their computation interface, parallel evaluation strategies, and payment system solvency are defined.
 
 It is out of scope for this paper to survey in-depth the problem space of the operational semantics
-of payment execution environments. Nonetheless, a simplified model and some potential extensions to
-it is discussed briefly to place payment primitives in the big picture.
+of payment execution environments. Nonetheless, a simplified model and some potential extensions are
+discussed briefly to place payment primitives in the big picture.
 
@@
 
-While money distribution does not assign meaning to the range of monetary values, in real world
-applications, negative values can have special meanings. In the following analysis, we call any
-money unit that has a negative monetary value \textit{insolvent}.
-
-The detailed analysis of these solvency models are out of scope for this paper.
+While money distribution does not assign meaning to the range of monetary values, negative values
+can have special meanings in real-world applications. In the following analysis, we call any money
+unit with a negative monetary value \textit{insolvent}.
+
+The detailed analysis of these solvency models is out of the scope of this paper.
 
@@
 
-In a nondeterministic execution environment, we cannot determine when any financial contract will
-actually be executed. That means, there is always a chance a monetary unit could reach negative
-monetary value.
-
-To mitigate this uncertainty, a concept called \textit{buffer} is introduced. A buffer has a
-monetary value which is set aside in a solvency conditional financial contract, such that if a
-solvency condition arises, the buffer maybe drawn to cover the loss introduced by the
-nondeterministic timing of the execution.
+In a non-deterministic execution environment, we cannot determine when any financial contract will
+be executed. That means there is always a chance a monetary unit could reach negative monetary
+value.
+
+To mitigate the uncertainty of execution time, we introduce a concept called \textit{buffer}. A
+buffer has a monetary value set aside in a solvency conditional financial contract, such that if a
+solvency condition arises, the buffer may be drawn to cover the loss introduced by the
+non-deterministic timing of the execution.
 
@@
 
-Since \textit{fcNext} returns what is the next financial contract executable at a specific time,
-this deterministic property eliminates the need for the buffer.
-
-On the other hand, it introduces a different type of systemic risk, that is a kind of
-denial-of-service. It is due to that the complexity of $fcUpdate$ is $O(log(n))$, the system may not
-be able to advance its system time until all next executable contracts are executed.
+Since \textit{fcNext} returns what is the following financial contract executable at a specific
+time, this deterministic property eliminates the need for the buffer.
+
+On the other hand, it introduces a different type of systemic risk: a kind of
+denial-of-service. Because the complexity of $fcUpdate$ is $O(log(n))$, the system may not be able
+to advance its system time until all the following executable contracts are executed.
 
@@
 \begin{itemize}
-    \item \textit{Token and its Accounts} - \eg\ bank currency accounts. Each token is its own
-centralized execution environment, bearers access their monetary value through their accounts, and
+    \item \textit{Token and its Accounts} - \eg,\ bank currency accounts. Each token is its own
+centralized execution environment; bearers access their monetary value through their accounts and
 execute financial contracts through the token.
 
-    \item \textit{Note} - \eg\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The
+    \item \textit{Note} - \eg,\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The
 execution environment is independent of the notes, but it needs notes to complete the execution of
@@
 One of the main differences is from the ``user interface'' perspective. A bearer expects to keep
-many notes at hand, while maybe only needs a few accounts for each token. Also it is up to bearers
-to keep track of all their notes, while token can keep track of most of the states for bearers;
+many notes in hands while maybe only needing a few accounts for each token. Also, it is up to bearers
+to keep track of all their notes, while tokens can keep track of most of the states for bearers;
 hence notes are more decentralized and tokens are more centralized. Some also argue note-like model
@@
 The focus of this paper is to formally define a set of payment primitives that modernize our payment
-systems. To prevent reinventing wheels, it is relevant to discuss first some approaches in computer
-science that are believed to help tackling this challenge.
+systems. However, to prevent reinventing wheels, we should first discuss some approaches in computer
+science that help tackle this challenge.
 
@@
 
-Recall that we want our modern payment system to handle money distribution continuously over time,
-and its financial contracts compositional. A very closely related software design paradigm best
-known to address those needs is \textit{functional reactive programming (FRP)}.  It was first
+Recall that we want our modern payment system to handle money distribution continuously over time
+and its financial contracts to be compositional. A very closely related software design paradigm
+best known to address those needs is \textit{functional reactive programming (FRP)}.  It was first
 introduced by Conal Elliott \& Paul Hudak in solving multimedia animations
-(\cite{elliott1997functional}). Later on, Hudak also worked on \cite{hudak2002arrows} and
-\cite{wan2000functional} making FRP a more general framework for programming hybrid system with
+(\cite{elliott1997functional}). Later, Hudak also worked on \cite{hudak2002arrows} and
+\cite{wan2000functional}, making FRP a more general framework for programming hybrid systems with
 continuous behaviors in a high-level, declarative manner.
 
-After FRP got more adoption, it evolved to some variations that support discrete semantics, and some
-variations better suited for interactive systems. In this paper we will stick to and revisit the
-basic constructs of the original formulation used in \cite{elliott1997functional} where we will draw
-inspirations from.
+After FRP got more adoption, it evolved into some variations that support discrete semantics and
+some variations better suited for interactive systems. However, in this paper, we will stick to and
+revisit the basic constructs of the original formulation used in \cite{elliott1997functional} from
+which we will draw inspiration.
 
@@
 
-Values that vary over continuous time are called \textit{behaviors}. They are first-class values,
-and are built up compositionally. That is what we want in modern payment system also. The semantic
+Values that vary over continuous time are called \textit{behaviors}. They are first-class values and
+are built up compositionally. That is what we want in modern payment systems also. The semantic
 function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given time:
@@
 
-In modern payment system, the payment primitives executed in payment execution environments are
-one type of events. More types of events can be read from the original paper \footfullcite[][section
+In modern payment systems, the payment primitives executed in payment execution environments are
+one type of event. More types of events can be read from the original paper \footfullcite[][section
 2.3 Semantics of Events]{elliott1997functional}.
@@
 makes behaviors reactive. Specifically, the behavior \textit{b untilB e} exhibits b's behavior
-until \textit{e} occurs, and then swiches to a new behavior encoded in \textit{e}:
+until \textit{e} occurs, and then switches to a new behavior encoded in \textit{e}:
 
@@
 
-In the context of modern payment system, the occurrences of payment primitives (events) change the
-behaviors of monetary units in how much monetary values it has over continuous. The building blocks
-of the financial contracts should be about modeling these events and their reactivity declaratively.
+In the context of modern payment systems, the occurrences of payment primitives (events) change the
+behaviors of monetary units in terms of how much monetary value it has over continuous. The
+building blocks of the financial contracts should be about modeling these events and their
+reactivity declaratively.
 
@@
 
-The syntactic category we are interested in is \textit{payment primitives}, which we should treat
-them as FRP-style \textit{Behavior} data types. In the following chapters, it is also unambiguously
-referred to in short as $[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie\ must be defined
-by structural recursion.
-
-It is important to note that our purpose of using the denotational semantics is to give precise
-meaning to payment primitives, independent of its implementation (which deals with performance,
-optimization, side effects, etc.). We will spend the part \ref{part:gpp} exploring the denotational
-semantics for general payment primitives in modern payment system.
+The syntactic category we are interested in is \textit{payment primitives}, which we should treat as
+FRP-style \textit{Behavior} data types. In the following chapters, it is also unambiguously referred
+to in short as $[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie,\ must be defined by
+structural recursion.
+
+It is important to note that our purpose in using the denotational semantics is to give precise
+meaning to payment primitives independent of their implementations (which deal with performance,
+optimization, side effects, etc.). We will spend part \ref{part:gpp} exploring the denotational
+semantics for general payment primitives in modern payment systems.
 
@@
 
-The set of payment primitives supported in a payment system is general, if (a) monetary value of
+The set of payment primitives supported in a payment system is general if (a) the monetary value of
 each monetary unit can vary continuously over time (b) monetary values can logically be shifted
@@
 primitives that is general and serves as a starting point for the readers to explore the space of
-modern payment system.
+modern payment systems.
 
@@
 
-Recall the definition of payment system previously, money distribution sits in the core of the
+Recall in the definition of payment system previously, money distribution sits in the core of the
 system, and that is the syntactic category $\mathcal{M}$ we will be dealing with:
@@
 
-That is to say, at any given time, the sum of monetary value of all monetary units shall always
-equal to zero. Zero is used to keep the semantical meaning of payment system simple and elegant. In
-its applications, a payment system may use some special monetary unit accounting negative monetary
-values to accommodate concepts such as mining, minting, money printing, etc.
+That is to say, at any given time, the sum of the monetary value of all monetary units shall always
+equal zero. Zero is used to keep the semantical meaning of payment systems simple and elegant. In
+its applications, a payment system may use some special monetary unit accounting for negative
+monetary values to accommodate concepts such as mining, minting, money printing, etc.
 
@@
 To come up with such lawful money distribution, we can divide and conquer. In a payment system, if
-we restrict that only payment primitives can provide ``updates'' to its money distribution, so that
-a money distribution is only a result of a sequence of payment primitive updates; then we can have
+we restrict that only payment primitives can provide ``updates'' to their money distribution so that
+money distribution is only a result of a sequence of payment primitive updates; then, we can have
 these axioms as the basis for the proof.
@@
 
-First we must impose the law of conservation of value on payment primitives as an axiom, in order to
+First, we must impose the law of conservation of value on payment primitives as an axiom in order to
 prove inductively that such restricted money distribution satisfies the law of conservation of value
@@
 
-\subsection{One to One Payment Primitives}
+\subsection{One-to-One Payment Primitives}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Here are the primitives involving a sender ($u_a$) and a receiver ($u_b$) (one to one payments).
+Here are the primitives involving a sender ($u_a$) and a receiver ($u_b$) (one-to-one payments).
 
@@
 
-A \textit{index} (we use symbol $k$ for them) has a function $\rho$ which produces a real number for
+An \textit{index} (we use symbol $k$ for them) has a function $\rho$ which produces a real number for
 each monetary unit:
@@
 
-Let's generalize the one to one payment primitives using index abstraction. We use $I$ subscript for
+Let's generalize the one-to-one payment primitives using index abstraction. We use $I$ subscript for
 the indexed versions of the primitives.
@@
 
-An even more general abstraction is to model participants involved a payment primitive
-a \textit{network} (we use symbol $w$ for them).
-
-It has the function $\rho$ as in \textit{index}, bnd it satisfies a different law:
+An even more general abstraction is to model participants involved a payment
+primitive \textit{network} (we use the symbol $w$ for them).
+
+It has the function $\rho$ as in \textit{index}, and it satisfies a different law:
 
@@
 
-The question now is, should we use the most general form of the semantics to guide implementation?
-
-The answer is most likely a no. Not because it is not useful, after all mathematical formula is
+The question now is, should we use the most general form of semantics to guide implementation?
+
+The answer is most likely a no. Not because it is not useful; after all mathematical formula is
 about truth and perhaps also elegance in it, but because of we may miss optimization opportunities
@@
 this paper and its sequels, an implementation in Haskell was created. It aims to implement the full
-specifications of (a) denotational semantics of payment primitives, (b) compositional financial
+specifications of (a) the denotational semantics of payment primitives, (b) compositional financial
 contracts for the payment primitives, (c) token \& note model of money mediums, and their execution
@@
 
-This paper covers the overview of the implementation with regards to (a).
+This paper covers the overview of the implementation with regard to (a).
 
@@
 use \textit{QuickCheck}\footnote{\url{https://wiki.haskell.org/QuickCheck} - Haskell wiki page for
-QuickCheck.} to test the necessary laws are not violated using randomized test vector.
+QuickCheck.} to test that the necessary laws are not violated using randomized test vectors.
 
@@
 ``Propositions as Types''). Agda being a dependently typed functional programming language fully
-embodies this insight, hence a good candidate for creating provable correct program.
+embodies this insight, hence a good candidate for creating provable correct programs.
 
@@
 Accounting, also known as accountancy, is the measurement, processing, and communication of
-financial and non financial information about economic entities such as businesses and
+financial and non-financial information about economic entities such as businesses and
 corporations. \footfullcite{needles2013principles}
@@
 
-The \textit{real time balance} introduced in this paper can be seen as a instance in
-the \textit{general accounting domain} specifically for financial contracts in dealing with payment
-primitives, which can be seen as a real time version of the cash flow accounting. Along with balance
-sheet accounting, income statement accounting, the conversion between these instances of general
+The \textit{real time balance} introduced in this paper can be seen as an instance in
+the \textit{general accounting domain}, specifically for financial contracts in dealing with payment
+primitives, which can be seen as a real time version of cash flow accounting. Along with balance
+sheet accounting, and income statement accounting, the conversion between these instances of general
 accounting domains are often called ``reconciliations''.
 
-More work can be done on how to create a simple and elegant automation system for the
-reconciliations.
+More work can be done on how to create a simple and elegant automation system for reconciliations.
 
@@
 modernized to handle money distribution continuously over time, its financial contracts are
-compositional, and its general accounting domain are automated and processed in real time.  }
+compositional, and its general accounting domain is automated and processed in real time.  }
 
@@
 
-This paper defines the what constitutes a modern payment system, with its payment primitives
-formally specified using denotational semantics and restated using Haskell programming
-language. Along with a reference implementation of the specification, we want to make a case that
-marrying with the progress of computer science, the way of money performing its function of medium
-of exchange can have a modern upgrade.
-
-Absent of any claim on whether if such modern upgrade is needed, we invite the readers to ask
-ourselves a question together: with electronic money increasingly being used, should we keep
-emulating the function money of its traditional quality, or could we rethink what it may be in the
-information age?
-
-In future work, we will look into deeper other topics of real time finance, and continue to refine
+This paper defines what constitutes a modern payment system, with its payment primitives formally
+specified using denotational semantics and restated using Haskell programming language. Along with a
+reference implementation of the specification, we want to make a case that marrying with the
+progress of computer science, the way of money performs its function of medium of exchange can have
+a modern upgrade.
+
+Absent any claim on whether a modern upgrade is needed; we invite the readers to ask ourselves a
+question together: with electronic money increasingly being used, should we keep emulating the
+function of money of its traditional quality, or could we rethink what it may be in the information
+age?
+
+In future work, we will look into deeper other topics of real time finance and continue to refine
 the methodology used to achieve \textit{simple and precise} specifications guiding correct and
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\part*{Acknowledgments}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-(To be confirmed.)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2022-11-15 examples/continous-auction-hardhat/hardhat.config.ts
Revert "SDK-redux stable version release (0.3.0) (#825)"
This reverts commit 21a142f9868aeec5a04aa09b9fa74724df99ee7b.

@@ -1,50 +1,0 @@
-import * as dotenv from "dotenv";
-
-import { HardhatUserConfig, task } from "hardhat/config";
-import "@nomiclabs/hardhat-etherscan";
-import "@nomiclabs/hardhat-waffle";
-import "@typechain/hardhat";
-import "hardhat-gas-reporter";
-import "solidity-coverage";
-require("@nomiclabs/hardhat-truffle5");
-require("@nomiclabs/hardhat-ethers");
-import "@typechain/hardhat";
-
-
-dotenv.config();
-
-// This is a sample Hardhat task. To learn how to create your own go to
-// https://hardhat.org/guides/create-task.html
-task("accounts", "Prints the list of accounts", async (taskArgs, hre) => {
-  const accounts = await hre.ethers.getSigners();
-
-  for (const account of accounts) {
-    console.log(account.address);
-  }
-});
-
-// You need to export an object to set up your config
-// Go to https://hardhat.org/config/ to learn more
-
-const config: HardhatUserConfig = {
-  solidity: "0.7.6",
-  networks: {
-    ropsten: {
-      url: process.env.ROPSTEN_URL || "",
-      accounts:
-        process.env.PRIVATE_KEY !== undefined ? [process.env.PRIVATE_KEY] : [],
-    },
-  },
-  gasReporter: {
-    enabled: process.env.REPORT_GAS !== undefined,
-    currency: "USD",
-  },
-  etherscan: {
-    apiKey: process.env.ETHERSCAN_API_KEY,
-  },
-  paths: {
-    artifacts: './artifacts',
-  },
-};
-
-export default config;

### 2022-11-15 examples/continuous-auction/truffle-config.js

@@ -33,7 +33,7 @@ module.exports = {
     // Configure your compilers
     compilers: {
         solc: {
-            version: "0.8.13" // Fetch exact version from solc-bin (default: truffle's version)
+            version: "0.7.6" // Fetch exact version from solc-bin (default: truffle's version)
             // docker: true,        // Use "0.5.1" you've installed locally with docker (default: false)
             // settings: {          // See the solidity docs for advice about optimization and evmVersion
             //  optimizer: {

### 2022-11-15 examples/flowlottery/solidity-contracts/truffle-config.js

@@ -2,7 +2,7 @@ const HDWalletProvider = require("@truffle/hdwallet-provider");
 require("dotenv").config();
 const GAS_LIMIT = 8e6;
 
-const M = (module.exports = {
+module.exports = {
     networks: {
         goerli: {
             provider: () =>
@@ -15,30 +15,20 @@ const M = (module.exports = {
             gasPrice: 10e9, // 10 GWEI
             //confirmations: 6, // # of confs to wait between deployments. (default: 0)
             timeoutBlocks: 50, // # of blocks before a deployment times out  (minimum/default: 50)
-            skipDryRun: false, // Skip dry run before migrations? (default: false for public nets )
+            skipDryRun: false // Skip dry run before migrations? (default: false for public nets )
         },
         ganache: {
             host: "127.0.0.1",
             network_id: "*",
             port: process.env.GANACHE_PORT || 8545,
-        },
+        }
     },
     compilers: {
         solc: {
-            version: "0.8.13", // Fetch exact version from solc-bin (default: truffle's version)
-            settings: {
-                // See the solidity docs for advice about optimization and evmVersion
-                optimizer: {
-                    enabled: true,
-                    runs: 200,
-                },
-            },
-        },
+            version: "0.7.6" // Fetch exact version from solc-bin (default: truffle's version)
+        }
     },
     mocha: {
-        timeout: 1000000,
-    },
-});
-
-// hot-fuzz support
-require("@superfluid-finance/hot-fuzz").hotfuzzPatchTruffleConfig(M);
+        timeout: 1000000
+    }
+};

### 2022-11-15 examples/nftbillboard-userdata/packages/hardhat/hardhat.config.js

@@ -25,7 +25,7 @@ module.exports = {
   defaultNetwork,
 
   solidity: {
-    version: "0.8.13",
+    version: "0.7.0",
     settings: {
       optimizer: {
         enabled: true

### 2022-11-15 examples/simple-acl-close/.solcover.js

@@ -1,3 +1,0 @@
-module.exports = {
-    skipFiles: ["test"],
-};

### 2022-11-15 packages/ethereum-contracts/.solcover.js

@@ -1,6 +1,6 @@
 module.exports = {
     providerOptions: {
-        network_id: 8555,
+        network_id: 6777,
     },
     skipFiles: [
         "mocks/",
@@ -9,7 +9,5 @@ module.exports = {
     mocha: {
         grep: "@skip-on-coverage", // Find everything with this tag
         invert: true, // Run the grep's inverse set.
-        enableTimeouts: false
     },
-    configureYulOptimizer: true
 };

### 2022-11-15 packages/ethereum-contracts/scripts/deploy-erc1820.js

@@ -3,8 +3,7 @@ const assert = require("assert").strict;
 
 const Transaction = require("ethereumjs-tx").Transaction;
 const ethUtils = require("ethereumjs-util");
-// TODO: this is a weird dependency, should probably get this from elsewhere
-const ERC1820Registry = require("./artifacts/ERC1820Registry.json");
+const ERC1820Registry = require("../artifacts/ERC1820Registry.json");
 const {getScriptRunnerFactory: S, hasCode} = require("./libs/common");
 
 /**
@@ -57,23 +56,11 @@ module.exports = eval(`(${S.toString()})({skipArgv: true})`)(async function (
         console.log("Deploying...");
         const account = options.from || (await web3.eth.getAccounts())[0];
         console.log("Step 1: send ETH");
-        // NOTE: we estimate gas when running test coverage w/ hardhat
-        // otherwise there is a weird bug which requires the user to have
-        // over 2k ETH to send the transaction
-        const estimatedGasObject = {
+        await web3.eth.sendTransaction({
             from: account,
             to: res.sender,
             value: "100000000000000000", //web3.utils.toWei(0.1)
-        };
-        if (process.env.IS_HARDHAT) {
-            const estimatedGas = await web3.eth.estimateGas(estimatedGasObject);
-            await web3.eth.sendTransaction({
-                ...estimatedGasObject,
-                gas: estimatedGas,
-            });
-        } else {
-            await web3.eth.sendTransaction(estimatedGasObject);
-        }
+        });
         console.log("Step 2: send signed transaction");
         await web3.eth.sendSignedTransaction(res.rawTx);
         console.log("Deployment done.");

### 2022-11-15 packages/ethereum-contracts/tasks/dev.sh

@@ -1,20 +1,0 @@
-#!/bin/sh
-
-# It will use nodemon to monitor changes and reload test for TDD experience.
-# And:
-# if parameters is provided, they are considered testsuites and will be run using hardhat test,
-# otherwise full testsuite is run.
-
-cd "$(dirname "$0")"/..
-
-export IS_HARDHAT=true
-
-C="$@"
-
-if [ -z "$C" ];then
-    X="yarn test:contracts:hardhat 2>&1"
-else
-    X="yarn run-hardhat test $C"
-fi
-
-yarn run-nodemon "$X"

### 2022-11-15 packages/ethereum-contracts/test/contracts/agreements/ConstantFlowAgreementV1.behavior.js

@@ -1,5 +1,4 @@
 const {expectEvent} = require("@openzeppelin/test-helpers");
-const {expectRevertedWith} = require("../../utils/expectRevert");
 const {web3tx, toBN} = require("@decentral.ee/web3-helpers");
 const CFADataModel = require("./ConstantFlowAgreementV1.data.js");
 const MFASupport = require("../utils/MFASupport");
@@ -51,8 +50,7 @@ async function _shouldChangeFlow({
     // add all roles
     cfaDataModel.addRole("sender", sender);
     cfaDataModel.addRole("receiver", receiver);
-    const isDeleteFlow = ["deleteFlow", "deleteFlowByOperator"].includes(fn);
-    if (isDeleteFlow) {
+    if (fn === "deleteFlow") {
         assert.isDefined(by);
         const agentAddress = testenv.getAddress(by);
         let rewardAddress = await governance.getRewardAddress(
@@ -63,7 +61,6 @@ async function _shouldChangeFlow({
             rewardAddress = agentAddress;
         }
         // agent is the liquidator (executor of deleteFlow)
-        // or agent is the flowOperator
         cfaDataModel.addRole("agent", by);
         cfaDataModel.addRole("reward", testenv.toAlias(rewardAddress));
     }
@@ -102,7 +99,7 @@ async function _shouldChangeFlow({
     cfaDataModel.expectedNetFlowDeltas[cfaDataModel.roles.receiver] = toBN(
         flowRate
     ).sub(toBN(cfaDataModel.flows.main.flowInfoBefore.flowRate));
-    if (isDeleteFlow) {
+    if (fn === "deleteFlow") {
         if (!(cfaDataModel.roles.agent in cfaDataModel.expectedNetFlowDeltas)) {
             cfaDataModel.expectedNetFlowDeltas[cfaDataModel.roles.agent] =
                 toBN(0);
@@ -209,34 +206,6 @@ async function _shouldChangeFlow({
                 userData,
             });
             break;
-        case "createFlowByOperator":
-        case "updateFlowByOperator":
-            tx = await testenv.contracts.superfluid.callAgreement(
-                testenv.contracts.cfa.address,
-                testenv.contracts.cfa.contract.methods[fn](
-                    cfaDataModel.flows.main.flowId.superToken,
-                    cfaDataModel.flows.main.flowId.sender,
-                    cfaDataModel.flows.main.flowId.receiver,
-                    flowRate.toString(),
-                    "0x"
-                ).encodeABI(),
-                "0x",
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/agreements/InstantDistributionAgreementV1.test.js

@@ -1,6 +1,5 @@
-const {expectEvent} = require("@openzeppelin/test-helpers");
+const {expectRevert, expectEvent} = require("@openzeppelin/test-helpers");
 const {web3tx, wad4human, toWad} = require("@decentral.ee/web3-helpers");
-
 const {
     shouldCreateIndex,
     shouldDistribute,
@@ -11,11 +10,8 @@ const {
     shouldClaimPendingDistribution,
 } = require("./InstantDistributionAgreementV1.behaviour.js");
 
-const {expectRevertedWith} = require("../../utils/expectRevert");
-
 const IDASuperAppTester = artifacts.require("IDASuperAppTester");
 const TestEnvironment = require("../../TestEnvironment");
-const {ZERO_ADDRESS} = require("@openzeppelin/test-helpers/src/constants");
 
 const DEFAULT_INDEX_ID = "42";
 
@@ -25,7 +21,7 @@ describe("Using InstantDistributionAgreement v1", function () {
 
     const {INIT_BALANCE} = t.configs;
 
-    let alice, bob, carol;
+    let alice, bob, carol, dan;
     let superToken;
 
     before(async function () {
@@ -33,7 +29,7 @@ describe("Using InstantDistributionAgreement v1", function () {
             isTruffle: true,
             nAccounts: 5,
         });
-        ({alice, bob, carol} = t.aliases);
+        ({alice, bob, carol, dan} = t.aliases);
 
         superToken = t.sf.tokens.TESTx;
     });
@@ -47,7 +43,7 @@ describe("Using InstantDistributionAgreement v1", function () {
             const account = expectedBalances[i][0];
             const expectedBalance = expectedBalances[i][1];
             //const expectedDeposit = expectedBalances[i][2] || "0";
-            const balance = await superToken.balanceOf(account);
+            const balance = await superToken.balanceOf.call(account);
             console.log(
                 `${t.toAlias(account)}'s current balance: `,
                 wad4human(balance)
@@ -81,7 +77,7 @@ describe("Using InstantDistributionAgreement v1", function () {
                     indexId: DEFAULT_INDEX_ID,
                 });
 
-                await expectRevertedWith(
+                await expectRevert(
                     shouldCreateIndex({
                         testenv: t,
                         superToken,
@@ -135,7 +131,7 @@ describe("Using InstantDistributionAgreement v1", function () {
             });
 
             it("#1.1.5 publisher should fail to update non-existent index", async () => {
-                await expectRevertedWith(
+                await expectRevert(
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/misc.test.js

@@ -1,0 +1,308 @@
+const TestEnvironment = require("../TestEnvironment");
+
+const {toBN} = require("@decentral.ee/web3-helpers");
+const {expectRevert} = require("@openzeppelin/test-helpers");
+
+const DEFAULT_ADMIN_ROLE =
+    "0x0000000000000000000000000000000000000000000000000000000000000000";
+
+describe("Miscellaneous for test coverages", function () {
+    this.timeout(300e3);
+    const t = TestEnvironment.getSingleton();
+
+    const {ZERO_ADDRESS} = t.constants;
+
+    let admin, alice;
+
+    before(async () => {
+        await t.beforeTestSuite({
+            isTruffle: true,
+            nAccounts: 5,
+        });
+        ({admin, alice} = t.aliases);
+    });
+
+    describe("UUPS", () => {
+        const UUPSProxy = artifacts.require("UUPSProxy");
+        const UUPSProxiableMock = artifacts.require("UUPSProxiableMock");
+
+        it("UUPSProxy", async () => {
+            const proxy = await UUPSProxy.new();
+            const proxiable = await UUPSProxiableMock.at(proxy.address);
+            const uuid1 = web3.utils.sha3("UUPSProxiableMock1");
+            const mock = await UUPSProxiableMock.new(uuid1, 1);
+            await expectRevert(
+                proxy.initializeProxy(ZERO_ADDRESS),
+                "UUPSProxy: zero address"
+            );
+            await proxy.initializeProxy(mock.address);
+            await expectRevert(
+                proxy.initializeProxy(mock.address),
+                "UUPSProxy: already initialized"
+            );
+            assert.equal(await proxiable.proxiableUUID(), uuid1);
+        });
+
+        it("UUPSProxiable", async () => {
+            const proxy = await UUPSProxy.new();
+            const proxiable = await UUPSProxiableMock.at(proxy.address);
+            const uuid1 = web3.utils.sha3("UUPSProxiableMock1");
+            const uuid2 = web3.utils.sha3("UUPSProxiableMock2");
+            const mock1a = await UUPSProxiableMock.new(uuid1, 1);
+            const mock1b = await UUPSProxiableMock.new(uuid1, 2);
+            const mock2 = await UUPSProxiableMock.new(uuid2, 1);
+
+            assert.equal(await mock1a.getCodeAddress(), ZERO_ADDRESS);
+            await expectRevert(
+                mock1a.updateCode(mock1a.address),
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/superfluid/ERC20.behavior.js

@@ -1,8 +1,12 @@
 // NOTE: copied and modified from https://github.com/OpenZeppelin/openzeppelin-contracts/
-const {BN, constants, expectEvent} = require("@openzeppelin/test-helpers");
+const {
+    BN,
+    constants,
+    expectEvent,
+    expectRevert,
+} = require("@openzeppelin/test-helpers");
 const {expect} = require("chai");
 const {ZERO_ADDRESS} = constants;
-const {expectRevertedWith} = require("../../utils/expectRevert");
 
 function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
     let initialHolder, recipient, anotherAccount;
@@ -140,7 +144,7 @@ function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
                         const amount = initialSupply.addn(1);
 
                         it("reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.transferFrom(
                                     tokenOwner,
                                     to,
@@ -166,7 +170,7 @@ function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
                         const amount = initialSupply;
 
                         it("reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.transferFrom(
                                     tokenOwner,
                                     to,
@@ -182,7 +186,7 @@ function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
                         const amount = initialSupply.addn(1);
 
                         it("reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.transferFrom(
                                     tokenOwner,
                                     to,
@@ -207,7 +211,7 @@ function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
                 });
 
                 it("reverts", async function () {
-                    await expectRevertedWith(
+                    await expectRevert(
                         this.token.transferFrom(tokenOwner, to, amount, {
                             from: spender,
                         }),
@@ -227,7 +231,7 @@ function shouldBehaveLikeERC20(errorPrefix, initialSupply, setupAccounts) {
             });
 
             it("reverts", async function () {
-                await expectRevertedWith(
+                await expectRevert(
                     this.token.transferFrom(tokenOwner, to, amount, {
                         from: spender,
                     }),
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/superfluid/ERC777.behavior.js

@@ -1,9 +1,13 @@
 // NOTE: copied and modified from https://github.com/OpenZeppelin/openzeppelin-contracts/
-const {BN, constants, expectEvent} = require("@openzeppelin/test-helpers");
+const {
+    BN,
+    constants,
+    expectEvent,
+    expectRevert,
+} = require("@openzeppelin/test-helpers");
 const {ZERO_ADDRESS} = constants;
 
 const {expect} = require("chai");
-const {expectRevertedWith} = require("../../utils/expectRevert");
 
 const ERC777SenderRecipientMock = artifacts.require(
     "ERC777SenderRecipientMock"
@@ -68,20 +72,18 @@ function _shouldBehaveLikeERC777DirectSend(setupAccounts, data) {
 
             it("reverts when sending more than the balance", async function () {
                 const balance = await this.token.balanceOf(holder);
-                await expectRevertedWith(
+                await expectRevert.unspecified(
                     this.token.send(recipient, balance.addn(1), data, {
                         from: holder,
-                    }),
-                    "revert"
+                    })
                 );
             });
 
             it("reverts when sending to the zero address", async function () {
-                await expectRevertedWith(
+                await expectRevert.unspecified(
                     this.token.send(ZERO_ADDRESS, new BN("1"), data, {
                         from: holder,
-                    }),
-                    "revert"
+                    })
                 );
             });
         });
@@ -101,11 +103,10 @@ function _shouldBehaveLikeERC777DirectSend(setupAccounts, data) {
             );
 
             it("reverts when sending a non-zero amount", async function () {
-                await expectRevertedWith(
+                await expectRevert.unspecified(
                     this.token.send(recipient, new BN("1"), data, {
                         from: holder,
-                    }),
-                    "revert"
+                    })
                 );
             });
         });
@@ -148,7 +149,7 @@ function _shouldBehaveLikeERC777OperatorSend(
 
             it("reverts when sending more than the balance", async function () {
                 const balance = await this.token.balanceOf(holder);
-                await expectRevertedWith(
+                await expectRevert.unspecified(
                     this.token.operatorSend(
                         holder,
                         recipient,
@@ -156,13 +157,12 @@ function _shouldBehaveLikeERC777OperatorSend(
                         data,
                         operatorData,
                         {from: operator}
-                    ),
-                    "revert"
+                    )
                 );
             });
 
             it("reverts when sending to the zero address", async function () {
-                await expectRevertedWith(
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/superfluid/SuperToken.ERC777.test.js

@@ -1,7 +1,6 @@
 const TestEnvironment = require("../../TestEnvironment");
 
-const {expectEvent} = require("@openzeppelin/test-helpers");
-const {expectRevertedWith} = require("../../utils/expectRevert");
+const {expectRevert, expectEvent} = require("@openzeppelin/test-helpers");
 const {expect} = require("chai");
 
 const {web3tx, toWad} = require("@decentral.ee/web3-helpers");
@@ -249,14 +248,14 @@ describe("SuperToken's ERC777 implementation", function () {
             });
 
             it("reverts when self-authorizing", async function () {
-                await expectRevertedWith(
+                await expectRevert(
                     this.token.authorizeOperator(holder, {from: holder}),
                     "ERC777Operators: authorizing self as operator"
                 );
             });
 
             it("reverts when self-revoking", async function () {
-                await expectRevertedWith(
+                await expectRevert(
                     this.token.revokeOperator(holder, {from: holder}),
                     "ERC777Operators: revoking self as operator"
                 );
@@ -382,7 +381,7 @@ describe("SuperToken's ERC777 implementation", function () {
                 });
 
                 it("cannot be revoked for themselves", async function () {
-                    await expectRevertedWith(
+                    await expectRevert(
                         this.token.revokeOperator(defaultOperatorA, {
                             from: defaultOperatorA,
                         }),
@@ -463,7 +462,7 @@ describe("SuperToken's ERC777 implementation", function () {
                         });
 
                         it("send reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.send(recipient, amount, testData, {
                                     from: holder,
                                 }),
@@ -472,7 +471,7 @@ describe("SuperToken's ERC777 implementation", function () {
                         });
 
                         it("operatorSend reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.operatorSend(
                                     sender,
                                     recipient,
@@ -486,7 +485,7 @@ describe("SuperToken's ERC777 implementation", function () {
                         });
 
                         it("mint (internal) reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
                                 this.token.mintInternal(
                                     recipient,
                                     amount,
@@ -499,7 +498,7 @@ describe("SuperToken's ERC777 implementation", function () {
                         });
 
                         it("mint (internal) to zero address reverts", async function () {
-                            await expectRevertedWith(
+                            await expectRevert(
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/superfluid/SuperToken.NonStandard.test.js

@@ -1,7 +1,6 @@
 const TestEnvironment = require("../../TestEnvironment");
 
-const {expectEvent} = require("@openzeppelin/test-helpers");
-const {expectRevertedWith} = require("../../utils/expectRevert");
+const {expectEvent, expectRevert} = require("@openzeppelin/test-helpers");
 
 const {web3tx, toWad, toDecimals, toBN} = require("@decentral.ee/web3-helpers");
 
@@ -60,14 +59,14 @@ describe("SuperToken's Non Standard Functions", function () {
         });
 
         it("#1.3 only host can update the code", async () => {
-            await expectRevertedWith(
+            await expectRevert(
                 superToken.updateCode(ZERO_ADDRESS),
                 "SuperToken: only host can update code"
             );
         });
 
         it("#1.4 only can initialize once", async () => {
-            await expectRevertedWith(
+            await expectRevert(
                 superToken.initialize(ZERO_ADDRESS, 18, "name", "symbol"),
                 "Initializable: contract is already initialized"
             );
@@ -120,7 +119,7 @@ describe("SuperToken's Non Standard Functions", function () {
 
         it("#2.2 - should not upgrade without enough underlying balance", async () => {
             const initialBalance = await testToken.balanceOf.call(alice);
-            await expectRevertedWith(
+            await expectRevert(
                 web3tx(superToken.upgrade, "SuperToken.upgrade - bad balance")(
                     initialBalance.add(toBN(1)),
                     {from: alice}
@@ -214,7 +213,7 @@ describe("SuperToken's Non Standard Functions", function () {
         });
 
         it("#2.5 - should not downgrade if there is no balance", async () => {
-            await expectRevertedWith(
+            await expectRevert(
                 web3tx(
                     superToken.downgrade,
                     "SuperToken.downgrade - bad balance"
@@ -465,7 +464,7 @@ describe("SuperToken's Non Standard Functions", function () {
 
         it("#2.9 - upgradeTo should trigger tokensReceived", async () => {
             const mock = await ERC777SenderRecipientMock.new();
-            await expectRevertedWith(
+            await expectRevert(
                 superToken.upgradeTo(mock.address, toWad(2), "0x", {
                     from: alice,
                 }),
@@ -555,7 +554,7 @@ describe("SuperToken's Non Standard Functions", function () {
                 from: alice,
             });
 
-            await expectRevertedWith(
+            await expectRevert(
                 superToken.upgradeTo(mockWallet.address, toWad(2), "0x", {
                     from: alice,
                 }),
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/tokens/NativeSuperToken.test.js

@@ -1,0 +1,53 @@
+const {expectRevert} = require("@openzeppelin/test-helpers");
+
+const ISuperTokenFactory = artifacts.require("ISuperTokenFactory");
+const TestEnvironment = require("../../TestEnvironment");
+const NativeSuperTokenProxy = artifacts.require("NativeSuperTokenProxy");
+
+const {web3tx, toWad} = require("@decentral.ee/web3-helpers");
+
+describe("NativeSuperTokenProxy Contract", function () {
+    this.timeout(300e3);
+    const t = TestEnvironment.getSingleton();
+
+    let admin;
+    let superTokenFactory;
+
+    before(async () => {
+        await t.beforeTestSuite({
+            isTruffle: true,
+            nAccounts: 1,
+        });
+
+        ({admin} = t.aliases);
+        superTokenFactory = await ISuperTokenFactory.at(
+            await t.contracts.superfluid.getSuperTokenFactory()
+        );
+    });
+
+    beforeEach(async function () {
+        await t.beforeEachTestCase();
+    });
+
+    it("#1 create token", async () => {
+        const tokenProxy = await NativeSuperTokenProxy.new();
+        await web3tx(
+            superTokenFactory.initializeCustomSuperToken,
+            "superTokenFactory.initializeCustomSuperToken"
+        )(tokenProxy.address);
+        await web3tx(tokenProxy.initialize, "tokenProxy.initialize")(
+            "Didi Token",
+            "DD",
+            toWad(42)
+        );
+        const token = await t.sf.contracts.ISuperToken.at(tokenProxy.address);
+        assert.equal(
+            (await token.balanceOf.call(admin)).toString(),
+            toWad(42).toString()
+        );
+        await expectRevert(
+            tokenProxy.initialize("Hacker", "HH", toWad(0)),
+            "Initializable: contract is already initialized"
+        );
+    });
+});

### 2022-11-15 packages/ethereum-contracts/test/contracts/upgradability/UUPS.test.js

@@ -1,67 +1,0 @@
-const TestEnvironment = require("../../TestEnvironment");
-const {expectRevertedWith} = require("../../utils/expectRevert");
-
-describe("Miscellaneous for test coverages", function () {
-    const t = TestEnvironment.getSingleton();
-
-    const {ZERO_ADDRESS} = t.constants;
-
-    before(async () => {
-        await t.beforeTestSuite({
-            isTruffle: true,
-            nAccounts: 5,
-        });
-    });
-
-    describe("UUPS", () => {
-        const UUPSProxy = artifacts.require("UUPSProxy");
-        const UUPSProxiableMock = artifacts.require("UUPSProxiableMock");
-
-        it("UUPSProxy", async () => {
-            const proxy = await UUPSProxy.new();
-            const proxiable = await UUPSProxiableMock.at(proxy.address);
-            const uuid1 = web3.utils.sha3("UUPSProxiableMock1");
-            const mock = await UUPSProxiableMock.new(uuid1, 1);
-            await expectRevertedWith(
-                proxy.initializeProxy(ZERO_ADDRESS),
-                "UUPSProxy: zero address"
-            );
-            await proxy.initializeProxy(mock.address);
-            await expectRevertedWith(
-                proxy.initializeProxy(mock.address),
-                "UUPSProxy: already initialized"
-            );
-            assert.equal(await proxiable.proxiableUUID(), uuid1);
-        });
-
-        it("UUPSProxiable", async () => {
-            const proxy = await UUPSProxy.new();
-            const proxiable = await UUPSProxiableMock.at(proxy.address);
-            const uuid1 = web3.utils.sha3("UUPSProxiableMock1");
-            const uuid2 = web3.utils.sha3("UUPSProxiableMock2");
-            const mock1a = await UUPSProxiableMock.new(uuid1, 1);
-            const mock1b = await UUPSProxiableMock.new(uuid1, 2);
-            const mock2 = await UUPSProxiableMock.new(uuid2, 1);
-
-            assert.equal(await mock1a.getCodeAddress(), ZERO_ADDRESS);
-            await expectRevertedWith(
-                mock1a.updateCode(mock1a.address),
-                "UUPSProxiable: not upgradable"
-            );
-            await proxiable.updateCode(mock1a.address);
-
-            await proxy.initializeProxy(mock1a.address);
-            assert.equal(await proxiable.proxiableUUID(), uuid1);
-            assert.equal(await proxiable.waterMark(), 1);
-
[…]

### 2022-11-15 packages/ethereum-contracts/test/contracts/utils/BatchLiquidator.test.js

@@ -1,4 +1,4 @@
-const {expectRevertedWith} = require("../../utils/expectRevert");
+const {expectRevert} = require("@openzeppelin/test-helpers");
 
 const TestEnvironment = require("../../TestEnvironment");
 const BatchLiquidator = artifacts.require("BatchLiquidator");
@@ -149,7 +149,7 @@ describe("Superfluid Liquidator Contract", function () {
         });
 
         it("#1.4 Revert if size of senders and receivers don't match", async () => {
-            await expectRevertedWith(
+            await expectRevert(
                 batch.deleteFlows(
                     t.sf.host.address,
                     t.sf.agreements.cfa.address,

### 2022-11-15 packages/ethereum-contracts/testsuites/library-contracts.js

@@ -1,0 +1,2 @@
+require("../test/contracts/libs/CFAv1Library.test.js");
+require("../test/contracts/libs/IDAv1Library.test.js");

### 2022-11-15 packages/hot-fuzz/hardhat.config.disabled.ts

@@ -1,15 +1,0 @@
-import { HardhatUserConfig } from "hardhat/config";
-
-const config: HardhatUserConfig = {
-    solidity: {
-        version: "0.8.13",
-        settings: {
-            optimizer: {
-                enabled: true,
-                runs: 200,
-            },
-        },
-    },
-};
-
-export default config;

### 2022-11-15 packages/hot-fuzz/truffle-config.js

@@ -1,119 +1,0 @@
-/**
- * Use this file to configure your truffle project. It's seeded with some
- * common settings for different networks and features like migrations,
- * compilation and testing. Uncomment the ones you need or modify
- * them to suit your project as necessary.
- *
- * More information about configuration can be found at:
- *
- * https://trufflesuite.com/docs/truffle/reference/configuration
- *
- * To deploy via Infura you'll need a wallet provider (like @truffle/hdwallet-provider)
- * to sign your transactions before they're sent to a remote public node. Infura accounts
- * are available for free at: infura.io/register.
- *
- * You'll also need a mnemonic - the twelve word phrase the wallet uses to generate
- * public/private key pairs. If you're publishing your code to GitHub make sure you load this
- * phrase from a file you've .gitignored so it doesn't accidentally become public.
- *
- */
-
-// const HDWalletProvider = require('@truffle/hdwallet-provider');
-//
-// const fs = require('fs');
-// const mnemonic = fs.readFileSync(".secret").toString().trim();
-
-const M = (module.exports = {
-    /**
-     * Networks define how you connect to your ethereum client and let you set the
-     * defaults web3 uses to send transactions. If you don't specify one truffle
-     * will spin up a development blockchain for you on port 9545 when you
-     * run `develop` or `test`. You can ask a truffle command to use a specific
-     * network from the command line, e.g
-     *
-     * $ truffle test --network <network-name>
-     */
-
-    networks: {
-        // Useful for testing. The `development` name is special - truffle uses it by default
-        // if it's defined here and no other network is specified at the command line.
-        // You should run a client (like ganache-cli, geth or parity) in a separate terminal
-        // tab if you use this network and you must also set the `host`, `port` and `network_id`
-        // options below to some value.
-        //
-        // development: {
-        //  host: "127.0.0.1",     // Localhost (default: none)
-        //  port: 8545,            // Standard Ethereum port (default: none)
-        //  network_id: "*",       // Any network (default: none)
-        // },
-        // Another network with more advanced options...
-        // advanced: {
-        // port: 8777,             // Custom port
-        // network_id: 1342,       // Custom network
-        // gas: 8500000,           // Gas sent with each transaction (default: ~6700000)
-        // gasPrice: 20000000000,  // 20 gwei (in wei) (default: 100 gwei)
-        // from: <address>,        // Account to send txs from (default: accounts[0])
[…]

### 2022-11-15 packages/js-sdk/src/InstantDistributionAgreementV1Helper.js

@@ -30,7 +30,6 @@ module.exports = class InstantDistributionAgreementV1Helper {
         publisher,
         indexId,
         userData = "0x",
-        gasOptions = {},
         onTransaction = () => null,
     }) {
         const superTokenNorm = await this._sf.utils.normalizeTokenParam(
@@ -50,57 +49,10 @@ module.exports = class InstantDistributionAgreementV1Helper {
             ],
             sender: publisherNorm,
             method: this._sf.host.callAgreement,
-            gasOptions: {
-                maxPriorityFeePerGas: gasOptions.maxPriorityFeePerGas,
-                maxFeePerGas: gasOptions.maxFeePerGas,
-            },
             onTransaction,
         });
         console.debug("Index created.");
         return tx;
-    }
-
-    /**
-     * @dev Get details of an index
-     * @param {tokenParam} superToken SuperToken for the index
-     * @param {addressParam} publisher Publisher of the index
-     * @param {int} indexId ID of the index
-     * @return {Promise<Subscription>} Subscription data
-     */
-    async getIndex({superToken, publisher, indexId}) {
-        const superTokenNorm = await this._sf.utils.normalizeTokenParam(
-            superToken
-        );
-        const publisherNorm = await this._sf.utils.normalizeAddressParam(
-            publisher
-        );
-        const result = await this._ida.getIndex(
-            superTokenNorm,
-            publisherNorm,
-            indexId
-        );
-        return this.constructor._sanitizeIndexData(result);
-    }
-
-    /**
-     * @dev List indices of a publisher
-     * @param {tokenParam} superToken SuperToken for the index
-     * @param {addressParam} publisher Publisher of the index
-     * @return {Promise<Subscription>} Subscription data
-     */
-    async listIndices({superToken, publisher}) {
-        const superTokenNorm = await this._sf.utils.normalizeTokenParam(
-            superToken
-        );
-        const publisherNorm = await this._sf.utils.normalizeAddressParam(
-            publisher
-        );
-        return (
-            await this._sf.getPastEvents(this._ida, "IndexCreated", {
-                token: superTokenNorm,
-                publisher: publisherNorm,
-            })
-        ).map((e) => Number(e.indexId.toString()));
     }
 
     /**
@@ -118,7 +70,6 @@ module.exports = class InstantDistributionAgreementV1Helper {
         indexId,
         amount,
         userData = "0x",
-        gasOptions = {},
[…]

### 2022-11-15 packages/js-sdk/src/Utils.js

@@ -1,3 +1,4 @@
+const BN = require("bn.js");
 /**
  * @dev Utility class
  */
@@ -15,6 +16,6 @@ module.exports = class Utils {
     }
 
     normalizeFlowRateParam(param) {
-        return param.toString();
+        return BN.isBN(param) ? param.toString() : param;
     }
 };

### 2022-11-15 packages/js-sdk/src/utils/general.d.ts

@@ -1,15 +1,13 @@
 import type { Framework } from '../Framework';
 import type { Transaction } from 'web3-core';
-import { GasOptions } from "../types/gasOptions";
 
 export function validateAddress(address: string): void;
 export function isAddress(address: string): boolean;
 export function getCleanAddress(address: string): string;
-export function completeTransaction({ sf, method, args, sender, onTransaction, gasOptions }: {
+export function completeTransaction({ sf, method, args, sender, onTransaction }: {
     sf: Framework;
     method: () => Transaction;
     args: Array<string>;
     sender: string;
     onTransaction: () => any;
-    gasOptions?: GasOptions;
 }): Promise<Transaction>;

### 2022-11-15 packages/js-sdk/test/ConstantFlowAgreementV1Helper.test.js

@@ -87,20 +87,6 @@ describe("ConstantFlowAgreementV1Helper class", function () {
             ).toString(),
             "38580246913580"
         );
-        const aliceFlows = await sf.cfa.getAccountFlowInfo({
-            superToken: superToken.address,
-            account: alice,
-        });
-        assert.equal(aliceFlows.flowRate, "-38580246913580");
-        const bobFlows = await sf.cfa.getAccountFlowInfo({
-            superToken: superToken.address,
-            account: bob,
-        });
-        assert.equal(bobFlows.flowRate, "38580246913580");
-        assert.equal(
-            aliceFlows.timestamp.toString(),
-            bobFlows.timestamp.toString()
-        );
     });
 
     it("createFlow with onTransaction", async () => {

### 2022-11-15 packages/js-sdk/test/Framework.test.js

@@ -256,19 +256,6 @@ describe("Framework class", function () {
                 assert.equal(await sf.superTokens.ETHx.symbol(), "ETHx");
             });
 
-            it("use loadSuperNativeToken option", async () => {
-                const sf = new SuperfluidSDK.Framework({
-                    isTruffle: true,
-                    loadSuperNativeToken: true,
-                    version: "test",
-                });
-                await sf.initialize();
-
-                assert.equal(sf.superTokens.ETHx, sf.tokens.ETHx);
-                assert.equal(sf.superTokens.ETHx.superTokenCustomType, "SETH");
-                assert.equal(await sf.superTokens.ETHx.symbol(), "ETHx");
-            });
-
             it("load by native token symbol plus x", async () => {
                 const sf = new SuperfluidSDK.Framework({
                     isTruffle: true,

### 2022-11-15 packages/sdk-core/scripts/setDefaultSubgraphReleaseTag.js

@@ -1,11 +1,0 @@
-const { writeFileSync } = require('fs')
-const { join } = require('path')
-
-// This solution is necessary to embed environment variable data at build time.
-// Example: GitHub Actions runs canary build and wants to embed "dev" Subgraph release tag as the default.
-
-const FILE_PATH = join(__dirname, './../src/defaultSubgraphReleaseTag.json');
-
-writeFileSync(FILE_PATH, JSON.stringify({
-    value: process.env.SUBGRAPH_RELEASE_TAG || "v1"
-}, null, 2)); 

### 2022-11-15 packages/sdk-core/scripts/setup.ts

@@ -1,11 +1,17 @@
 import { ethers } from "hardhat";
 import { abi as TestTokenABI } from "../src/abi/TestToken.json";
+import { abi as IResolverABI } from "../src/abi/IResolver.json";
+import { abi as SuperTokenABI } from "../src/abi/SuperToken.json";
+import { abi as IConstantFlowAgreementV1ABI } from "../src/abi/IConstantFlowAgreementV1.json";
+import { abi as IInstantDistributionAgreementV1ABI } from "../src/abi/IInstantDistributionAgreementV1.json";
 import {
     IConstantFlowAgreementV1,
     IInstantDistributionAgreementV1,
+    IResolver,
+    SuperToken,
     TestToken,
 } from "../src/typechain";
-import { DataMode, Framework, WrapperSuperToken } from "../src";
+import { DataMode, Framework } from "../src";
 
 // NOTE: This assumes you are testing with the generic hardhat mnemonic as the deployer:
 // test test test test test test test test test test test junk
@@ -34,6 +40,25 @@ export const setup = async (props: ISetupProps) => {
     if (!provider) {
         throw new Error("No provider");
     }
+    const resolver = new ethers.Contract(
+        RESOLVER_ADDRESS,
+        IResolverABI,
+        Deployer
+    ) as IResolver;
+    const superTokenAddress = await resolver.get("supertokens.test.fDAIx");
+    const SuperToken = new ethers.Contract(
+        superTokenAddress,
+        SuperTokenABI,
+        Deployer
+    ) as SuperToken;
+    const underlyingToken = await SuperToken.connect(
+        Deployer
+    ).getUnderlyingToken();
+    const Token = new ethers.Contract(
+        underlyingToken,
+        TestTokenABI,
+        Deployer
+    ) as TestToken;
     const chainId = (await provider.getNetwork()).chainId;
     const frameworkClass = await Framework.create({
         chainId,
@@ -43,21 +68,16 @@ export const setup = async (props: ISetupProps) => {
         customSubgraphQueriesEndpoint: props.subgraphEndpoint,
         protocolReleaseVersion: "test",
     });
-    const CFAV1 = frameworkClass.contracts.cfaV1.connect(
+    const CFAV1 = new ethers.Contract(
+        frameworkClass.settings.config.cfaV1Address,
+        IConstantFlowAgreementV1ABI,
         Deployer
     ) as IConstantFlowAgreementV1;
[…]

### 2022-11-15 packages/sdk-core/src/ConstantFlowAgreementV1.ts

@@ -8,67 +8,63 @@ import {
     IAgreementV1Options,
     ICreateFlowParams,
     IDeleteFlowParams,
-    IFullControlParams,
     IGetAccountFlowInfoParams,
-    IGetFlowOperatorDataByIDParams,
-    IGetFlowOperatorDataParams,
     IGetFlowParams,
-    IUpdateFlowByOperatorParams,
-    IUpdateFlowOperatorPermissionsParams,
     IUpdateFlowParams,
     IWeb3FlowInfo,
     IWeb3FlowInfoParams,
-    IWeb3FlowOperatorData,
-    IWeb3FlowOperatorDataParams,
 } from "./interfaces";
 import { IConstantFlowAgreementV1 } from "./typechain";
-import {
-    getSanitizedTimestamp,
-    isPermissionsClean,
-    normalizeAddress,
-} from "./utils";
+import { getSanitizedTimestamp, normalizeAddress } from "./utils";
 
 const cfaInterface = new ethers.utils.Interface(
     IConstantFlowAgreementV1ABI.abi
 );
 
 /**
- * Constant Flow Agreement V1 Helper Class
+ * @dev Constant Flow Agreement V1 Helper Class
  * @description A helper class to interact with the CFAV1 contract.
  */
 export default class ConstantFlowAgreementV1 {
     readonly options: IAgreementV1Options;
     readonly host: Host;
-    readonly contract: IConstantFlowAgreementV1;
 
     constructor(options: IAgreementV1Options) {
         this.options = options;
         this.host = new Host(options.config.hostAddress);
-        this.contract = new ethers.Contract(
+    }
+
+    private get cfaContract() {
+        return new ethers.Contract(
             this.options.config.cfaV1Address,
             IConstantFlowAgreementV1ABI.abi
         ) as IConstantFlowAgreementV1;
     }
 
-    /** ### CFA Read Functions ### */
+    // CFA Read Functions
 
     /**
-     * Get the details of a flow.
+     * @dev Get the details of a flow.
      * @param superToken the superToken of the agreement
      * @param sender the sender of the flow
      * @param receiver the receiver of the flow
      * @param providerOrSigner a provider or signer object
      * @returns {Promise<IWeb3FlowInfo>} Web3 Flow info object
      */
-    getFlow = async (params: IGetFlowParams): Promise<IWeb3FlowInfo> => {
-        const normalizedToken = normalizeAddress(params.superToken);
[…]

### 2022-11-15 packages/sdk-core/src/Framework.ts

@@ -5,17 +5,12 @@ import Web3 from "web3";
 
 import BatchCall from "./BatchCall";
 import ConstantFlowAgreementV1 from "./ConstantFlowAgreementV1";
-import Governance from "./Governance";
 import Host from "./Host";
 import InstantDistributionAgreementV1 from "./InstantDistributionAgreementV1";
 import Operation from "./Operation";
 import Query from "./Query";
 import { SFError } from "./SFError";
-import SuperToken, {
-    NativeAssetSuperToken,
-    PureSuperToken,
-    WrapperSuperToken,
-} from "./SuperToken";
+import SuperToken from "./SuperToken";
 import IResolverABI from "./abi/IResolver.json";
 import SuperfluidLoaderABI from "./abi/SuperfluidLoader.json";
 import { chainIdToResolverDataMap, networkNameToChainIdMap } from "./constants";
@@ -24,12 +19,7 @@ import {
     getSubgraphQueriesEndpoint,
     validateFrameworkConstructorOptions,
 } from "./frameworkHelpers";
-import {
-    IConfig,
-    IContracts,
-    IResolverData,
-    ISignerConstructorOptions,
-} from "./interfaces";
+import { IConfig, ISignerConstructorOptions } from "./interfaces";
 import { IResolver, SuperfluidLoader } from "./typechain";
 import { DataMode } from "./types";
 import { isEthersProvider, isInjectedWeb3 } from "./utils";
@@ -62,16 +52,14 @@ export interface IFrameworkSettings {
 }
 
 /**
- * Superfluid Framework Class
+ * @dev Superfluid Framework Class
  * @description The entrypoint for the SDK-core, `create` an instance of this for full functionality.
  */
 export default class Framework {
     readonly userInputOptions: IFrameworkOptions;
     settings: IFrameworkSettings;
-    contracts: IContracts;
 
     cfaV1: ConstantFlowAgreementV1;
-    governance: Governance;
     host: Host;
     idaV1: InstantDistributionAgreementV1;
     query: Query;
@@ -86,31 +74,15 @@ export default class Framework {
         this.cfaV1 = new ConstantFlowAgreementV1({
             config: this.settings.config,
         });
-        this.governance = new Governance(
-            this.settings.config.governanceAddress,
-            this.settings.config.hostAddress
-        );
         this.host = new Host(this.settings.config.hostAddress);
         this.idaV1 = new InstantDistributionAgreementV1({
             config: this.settings.config,
         });
[…]

### 2022-11-15 packages/sdk-core/src/Governance.ts

@@ -1,104 +1,0 @@
-import { ethers } from "ethers";
-
-import SuperfluidGovernanceIIABI from "./abi/SuperfluidGovernanceII.json";
-import {
-    IGetGovernanceParametersParams,
-    IWeb3GovernanceParams,
-} from "./interfaces";
-import { SuperfluidGovernanceII } from "./typechain/SuperfluidGovernanceII";
-
-export default class Governance {
-    contract: SuperfluidGovernanceII;
-    hostAddress: string;
-
-    constructor(govAddress: string, hostAddress: string) {
-        this.contract = new ethers.Contract(
-            govAddress,
-            SuperfluidGovernanceIIABI.abi
-        ) as SuperfluidGovernanceII;
-        this.hostAddress = hostAddress;
-    }
-
-    /**
-     * Returns the 3Ps config for the specified token (or default) - the liquidation period and patrician period
-     * @see https://docs.superfluid.finance/superfluid/sentinels/liquidations-and-toga
-     * @param providerOrSigner a provider or signer for executing a web3 call
-     * @param token specified governance parameter token
-     * @returns {Object} liquidationPeriod and patricianPeriod as strings
-     */
-    getPPPConfig = async ({
-        providerOrSigner,
-        token = ethers.constants.AddressZero,
-    }: IGetGovernanceParametersParams) => {
-        const { liquidationPeriod, patricianPeriod } = await this.contract
-            .connect(providerOrSigner)
-            .getPPPConfig(this.hostAddress, token);
-        return {
-            liquidationPeriod: liquidationPeriod.toString(),
-            patricianPeriod: patricianPeriod.toString(),
-        };
-    };
-
-    /**
-     * Returns the reward address for the specified token (or default)
-     * @param providerOrSigner a provider or signer for executing a web3 call
-     * @param token specified governance parameter token
-     * @returns {string} the reward address
-     */
-    getRewardAddress = async ({
-        providerOrSigner,
-        token = ethers.constants.AddressZero,
-    }: IGetGovernanceParametersParams) => {
-        return await this.contract
-            .connect(providerOrSigner)
-            .getRewardAddress(this.hostAddress, token);
-    };
-
-    /**
-     * Returns the minimum deposit for the specified token (or default)
-     * @param providerOrSigner a provider or signer for executing a web3 call
-     * @param token specified governance parameter token
-     * @returns {string} minimum deposit
-     */
-    getMinimumDeposit = async ({
-        providerOrSigner,
[…]

### 2022-11-15 packages/sdk-core/src/InstantDistributionAgreementV1.ts

@@ -27,27 +27,29 @@ const idaInterface = new ethers.utils.Interface(
 );
 
 /**
- * Instant Distribution Agreement V1 Helper Class
+ * @dev Instant Distribution Agreement V1 Helper Class
  * @description A helper class to interact with the IDAV1 contract.
  */
 export default class InstantDistributionAgreementV1 {
     readonly options: IAgreementV1Options;
     readonly host: Host;
-    readonly contract: IInstantDistributionAgreementV1;
 
     constructor(options: IAgreementV1Options) {
         this.options = options;
         this.host = new Host(options.config.hostAddress);
-        this.contract = new ethers.Contract(
+    }
+
+    private get idaContract() {
+        return new ethers.Contract(
             this.options.config.idaV1Address,
             IInstantDistributionAgreementV1ABI.abi
         ) as IInstantDistributionAgreementV1;
     }
 
-    /** ### IDA Read Functions ### */
+    // IDA Read Functions
 
     /**
-     * Get the details of a `Subscription`.
+     * @dev Get the details of a `Subscription`.
      * @param superToken the superToken of the agreement
      * @param publisher the address of the publisher of the index
      * @param indexId the index id
@@ -55,19 +57,23 @@ export default class InstantDistributionAgreementV1 {
      * @param providerOrSigner a provider or signer object
      * @returns {Promise<IWeb3Subscription>} Web3 Subscription object
      */
-    getSubscription = async (
-        params: IGetSubscriptionParams
-    ): Promise<IWeb3Subscription> => {
-        const normalizedToken = normalizeAddress(params.superToken);
-        const normalizedPublisher = normalizeAddress(params.publisher);
-        const normalizedSubscriber = normalizeAddress(params.subscriber);
+    getSubscription = async ({
+        superToken,
+        publisher,
+        indexId,
+        subscriber,
+        providerOrSigner,
+    }: IGetSubscriptionParams): Promise<IWeb3Subscription> => {
+        const normalizedToken = normalizeAddress(superToken);
+        const normalizedPublisher = normalizeAddress(publisher);
+        const normalizedSubscriber = normalizeAddress(subscriber);
         try {
-            const subscription = await this.contract
-                .connect(params.providerOrSigner)
+            const subscription = await this.idaContract
+                .connect(providerOrSigner)
                 .getSubscription(
                     normalizedToken,
                     normalizedPublisher,
-                    params.indexId,
+                    indexId,
[…]

### 2022-11-15 packages/sdk-core/src/SFError.ts

@@ -8,8 +8,6 @@ export type ErrorType =
     | "IDAV1_READ"
     | "INVALID_ADDRESS"
     | "INVALID_OBJECT"
-    | "UNCLEAN_PERMISSIONS"
-    | "NEGATIVE_FLOW_ALLOWANCE"
     | "EXECUTE_TRANSACTION"
     | "POPULATE_TRANSACTION"
     | "SIGN_TRANSACTION"
@@ -37,8 +35,6 @@ const errorTypeToTitleMap = new Map<ErrorType, string>([
     ["BATCH_CALL_ERROR", "Batch Call"],
     ["NETWORK_MISMATCH", "Network Mismatch"],
     ["UNSUPPORTED_WEB_3_ONLY", "Unsupported Web 3 Only"],
-    ["UNCLEAN_PERMISSIONS", "Unclean Permissions"],
-    ["NEGATIVE_FLOW_ALLOWANCE", "Negative Flow Rate Allowance"],
 ]);
 
 interface ISFErrorProps {

### 2022-11-15 packages/sdk-core/src/SuperToken.ts

@@ -1,46 +1,35 @@
-import { BytesLike, ethers, Overrides } from "ethers";
+import { ethers, Overrides } from "ethers";
 
 import ConstantFlowAgreementV1 from "./ConstantFlowAgreementV1";
-import ERC20Token from "./ERC20Token";
-import Governance from "./Governance";
 import InstantDistributionAgreementV1 from "./InstantDistributionAgreementV1";
 import Operation from "./Operation";
 import { SFError } from "./SFError";
-import ISETHABI from "./abi/ISETH.json";
+import Token from "./Token";
 import SuperTokenABI from "./abi/SuperToken.json";
-import { chainIdToResolverDataMap, networkNameToChainIdMap } from "./constants";
+import { networkNameToChainIdMap } from "./constants";
 import { getNetworkName } from "./frameworkHelpers";
 import {
     IConfig,
     IRealtimeBalanceOfParams,
     ISuperTokenBaseIDAParams,
-    ISuperTokenCreateFlowByOperatorParams,
     ISuperTokenCreateFlowParams,
     ISuperTokenDeleteFlowParams,
     ISuperTokenDistributeParams,
-    ISuperTokenFlowOperatorDataByIDParams,
-    ISuperTokenFlowOperatorDataParams,
-    ISuperTokenFullControlParams,
     ISuperTokenGetFlowInfoParams,
     ISuperTokenGetFlowParams,
     ISuperTokenGetIndexParams,
     ISuperTokenGetSubscriptionParams,
     ISuperTokenPublisherOperationParams,
     ISuperTokenPubSubParams,
-    ISuperTokenUpdateFlowByOperatorParams,
-    ISuperTokenUpdateFlowOperatorPermissionsParams,
     ISuperTokenUpdateFlowParams,
     ISuperTokenUpdateIndexValueParams,
     ISuperTokenUpdateSubscriptionUnitsParams,
     IWeb3FlowInfo,
-    IWeb3FlowOperatorData,
-    IWeb3GovernanceParams,
     IWeb3Index,
     IWeb3RealTimeBalanceOf,
     IWeb3Subscription,
 } from "./interfaces";
 import { SuperToken as ISuperToken } from "./typechain";
-import { ISETH } from "./typechain/ISETH";
 import {
     getSanitizedTimestamp,
     getStringCurrentTimeInSeconds,
@@ -52,6 +41,7 @@ export interface ITokenSettings {
     readonly config: IConfig;
     readonly chainId: number;
     readonly networkName: string;
[…]

### 2022-11-15 packages/sdk-core/src/events.ts

@@ -2,9 +2,7 @@ export type EventBase = {
     id: string;
     blockNumber: number;
     transactionHash: string;
-    order: number;
     timestamp: number;
-    logIndex: number;
 };
 
 export interface IEventFilter {
@@ -14,7 +12,6 @@ export interface IEventFilter {
 
 export type AccountEvents =
     | FlowUpdatedEvent
-    | FlowOperatorUpdatedEvent
     | IndexCreatedEvent
     | IndexDistributionClaimedEvent
     | IndexSubscribedEvent
@@ -52,8 +49,7 @@ export type OtherEvents =
     | SuperTokenLogicCreatedEvent
     | SuperTokenLogicUpdatedEvent
     | PPPConfigurationChangedEvent
-    | TrustedForwarderChangedEvent
-    | UnknownEvent;
+    | TrustedForwarderChangedEvent;
 
 export type AllEvents = AccountEvents | OtherEvents;
 
@@ -63,16 +59,6 @@ export interface FlowUpdatedEvent extends EventBase {
     sender: string;
     receiver: string;
     flowRate: string;
-    flowOperator: string;
-    deposit: string;
-}
-
-export interface FlowOperatorUpdatedEvent extends EventBase {
-    name: "FlowOperatorUpdated";
-    token: string;
-    sender: string;
-    permissions: number;
-    flowRateAllowance: string;
 }
 
 export interface IndexCreatedEvent extends EventBase {
@@ -365,8 +351,4 @@ export interface TrustedForwarderChangedEvent extends EventBase {
     isKeySet: boolean;
     forwarder: string;
     enabled: boolean;
-}
-
-export interface UnknownEvent extends EventBase {
-    name: "_Unknown";
 }

### 2022-11-15 packages/sdk-core/src/index.ts

@@ -2,16 +2,11 @@ export * from "./subgraph/schema.generated";
 
 import BatchCall from "./BatchCall";
 import ConstantFlowAgreementV1 from "./ConstantFlowAgreementV1";
-import ERC20Token from "./ERC20Token";
 import Framework from "./Framework";
-import Governance from "./Governance";
 import Host from "./Host";
 import InstantDistributionAgreementV1 from "./InstantDistributionAgreementV1";
 import Query from "./Query";
 import SuperToken from "./SuperToken";
-import { WrapperSuperToken } from "./SuperToken";
-import { PureSuperToken } from "./SuperToken";
-import { NativeAssetSuperToken } from "./SuperToken";
 
 export * from "./interfaces";
 export * from "./utils";
@@ -20,18 +15,13 @@ export * from "./ordering";
 export * from "./events";
 export * from "./types";
 
-export { BatchCall };
-export { ConstantFlowAgreementV1 };
-export { ERC20Token };
 export { Framework };
-export { Governance };
-export { Host };
-export { InstantDistributionAgreementV1 };
-export { NativeAssetSuperToken };
-export { PureSuperToken };
-export { Query };
 export { SuperToken };
-export { WrapperSuperToken };
+export { Query };
+export { ConstantFlowAgreementV1 };
+export { InstantDistributionAgreementV1 };
+export { Host };
+export { BatchCall };
 
 export * from "./subgraph/entities/account/account";
 export * from "./subgraph/entities/accountTokenSnapshot/accountTokenSnapshot";
@@ -46,8 +36,6 @@ export * from "./subgraph/events/events";
 export * from "./subgraph/events/flowUpdatedEvent";
 export * from "./subgraph/events/indexUpdatedEvent";
 export * from "./subgraph/events/subscriptionUnitsUpdatedEvents";
-
-export * from "./subgraph/meta/meta";
 
 export * from "./subgraph/mappedSubgraphTypes";
 export * from "./SFError";

### 2022-11-15 packages/sdk-core/src/interfaces.ts

@@ -1,12 +1,4 @@
 import { ethers, Overrides } from "ethers";
-
-import {
-    IConstantFlowAgreementV1,
-    IInstantDistributionAgreementV1,
-    IResolver,
-    Superfluid,
-} from "./typechain";
-import { SuperfluidGovernanceII } from "./typechain/SuperfluidGovernanceII";
 // TODO (0xdavinchee): reorganize this
 // Maybe moving these into categorical files
 // makes more sense than stuffing them all here
@@ -55,16 +47,9 @@ export interface ISuperTokenModifyFlowParams {
 export interface ISuperTokenCreateFlowParams
     extends ISuperTokenModifyFlowParams {
     readonly flowRate: string;
-}
-
-export interface ISuperTokenCreateFlowByOperatorParams
-    extends ISuperTokenCreateFlowParams {
     readonly sender: string;
 }
-
 export type ISuperTokenUpdateFlowParams = ISuperTokenCreateFlowParams;
-export type ISuperTokenUpdateFlowByOperatorParams =
-    ISuperTokenCreateFlowByOperatorParams;
 export interface ISuperTokenDeleteFlowParams
     extends ISuperTokenModifyFlowParams {
     readonly sender: string;
@@ -122,45 +107,21 @@ export interface ISuperTokenUpdateSubscriptionUnitsParams {
     readonly userData?: string;
     readonly overrides?: Overrides & { from?: string | Promise<string> };
 }
-
-export interface IModifyFlowParams extends ISuperTokenModifyFlowParams {
+export interface IModifyFlowParams {
+    readonly receiver: string;
     readonly superToken: string;
+    readonly flowRate?: string;
+    readonly sender?: string;
+    readonly userData?: string;
+    readonly overrides?: Overrides & { from?: string | Promise<string> };
 }
 export interface ICreateFlowParams extends IModifyFlowParams {
     readonly flowRate: string;
 }
-export interface ICreateFlowByOperatorParams extends ICreateFlowParams {
-    readonly sender: string;
-}
 
 export type IUpdateFlowParams = ICreateFlowParams;
-export type IUpdateFlowByOperatorParams = ICreateFlowByOperatorParams;
-
 export interface IDeleteFlowParams extends IModifyFlowParams {
     readonly sender: string;
-}
-
-export interface ISuperTokenUpdateFlowOperatorPermissionsParams {
-    readonly flowOperator: string;
-    readonly permissions: number;
-    readonly flowRateAllowance: string;
[…]

### 2022-11-15 packages/sdk-core/src/pagination.ts

@@ -1,19 +1,17 @@
 import { ILightEntity } from "./interfaces";
 
 /**
- * Paging Helper Class
+ * @dev Paging Helper Class
  */
 export type Paging = {
     readonly take: number;
     readonly skip?: number;
     readonly lastId?: string;
-    readonly pageNumber?: number;
 };
 
 /**
  * For paginating Subgraph queries by using skip and take approach. Good for small result sets, not performant for large sets.
  * Use {@link LastIdPaging} for most performant pagination strategy.
- * NOTE: Also known as "offset based pagination".
  */
 export type SkipPaging = {
     readonly take: number;
@@ -23,7 +21,6 @@ export type SkipPaging = {
 /**
  * For paginating Subgraph queries by using the last ID of the previous paged result to get the next page.
  * Relies on Subgraph ordering ID's in ascending order which it always does unless the results are ordered by `id` in `desc` order.
- * NOTE: Also known as "cursor based pagination".
  */
 export type LastIdPaging = {
     readonly take: number;
@@ -31,31 +28,7 @@ export type LastIdPaging = {
 };
 
 /**
- * WARNING: Works only with the new QueryHandlers.
- * Essentially the same as @see SkipPaging but with more UI pagination friendly API.
- */
-export type PageNumberPaging = {
-    /**
-     * "Page size" in other words.
-     */
-    readonly take: number;
-    /**
-     * Page number starts from 1.
-     */
-    readonly pageNumber: number;
-};
-
-/**
- * WARNING: Works only with number literal of @see Number.POSITIVE_INFINITY.
- * WARNING: Works only with the new QueryHandlers.
- * Recursively gets all the possible Subgraph results.
- */
-export type AllPaging = {
-    readonly take: number;
-};
-
-/**
- * PagedResult Interface
+ * @dev PagedResult Interface
  */
 export interface PagedResult<T extends ILightEntity> {
     /**
@@ -67,12 +40,7 @@ export interface PagedResult<T extends ILightEntity> {
      * `undefined` when there's no next page.
      */
     readonly nextPaging?: Paging;
-
-    /**
-     * @obsolete Use `items` instead.
-     */
     readonly data: T[];
-    readonly items: T[];
 }
 
 /**
@@ -93,38 +61,14 @@ export const createPagedResult = <T extends ILightEntity>(
         nextPaging: hasNextPage
             ? isSkipPaging(paging)
                 ? nextSkipPaging(paging)
[…]

### 2022-11-15 packages/sdk-core/src/subgraph/entities/accountTokenSnapshot/accountTokenSnapshot.ts

@@ -37,7 +37,6 @@ export interface AccountTokenSnapshot {
     updatedAtTimestamp: Timestamp;
     account: Address;
     token: Address;
-    tokenSymbol: string;
 }
 
 export type AccountTokenSnapshotListQuery = SubgraphListQuery<
@@ -73,7 +72,6 @@ export class AccountTokenSnapshotQueryHandler extends SubgraphQueryHandler<
             ...x,
             account: x.account.id,
             token: x.token.id,
-            tokenSymbol: x.token.symbol,
             updatedAtBlockNumber: Number(x.updatedAtBlockNumber),
             updatedAtTimestamp: Number(x.updatedAtTimestamp),
         }));

### 2022-11-15 packages/sdk-core/test/0_framework.test.ts

@@ -11,7 +11,6 @@ export const ROPSTEN_SUBGRAPH_ENDPOINT =
 
 describe("Framework Tests", () => {
     let deployer: SignerWithAddress;
-    let alpha: SignerWithAddress;
     let superToken: SuperToken;
     let framework: Framework;
     let INFURA_API_URL = "https://polygon-rpc.com/";
@@ -21,13 +20,12 @@ describe("Framework Tests", () => {
     );
 
     before(async () => {
-        const { frameworkClass, Deployer, SuperToken, Alpha } = await setup({
+        const { frameworkClass, Deployer, SuperToken } = await setup({
             amount: "10000000000",
             subgraphEndpoint: ROPSTEN_SUBGRAPH_ENDPOINT,
         });
         framework = frameworkClass;
         deployer = Deployer;
-        alpha = Alpha;
         superToken = SuperToken;
     });
 
@@ -61,7 +59,7 @@ describe("Framework Tests", () => {
         it("Should throw an error if network and chainId don't match", async () => {
             try {
                 await Framework.create({
-                    networkName: "polygon-mainnet",
+                    networkName: "matic",
                     chainId: 4,
                     provider: deployer.provider!,
                 });
@@ -73,7 +71,6 @@ describe("Framework Tests", () => {
         });
 
         it("Should throw an error if your provider network and selected chainId/networkName don't match", async () => {
-            const chainId = (await deployer.provider!.getNetwork()).chainId;
             try {
                 await Framework.create({
                     chainId: 4,
@@ -82,7 +79,7 @@ describe("Framework Tests", () => {
             } catch (err: any) {
                 expect(err.message).to.equal(
                     "Network Mismatch Error - Your provider network chainId is: " +
-                        chainId +
+                        1337 +
                         " whereas your desired chainId is: " +
                         4
                 );
@@ -93,7 +90,7 @@ describe("Framework Tests", () => {
             try {
                 // NOTE: as any to get this to throw an error when test no provider initialization (as if this was JS)
                 await Framework.create({
-                    networkName: "polygon-mainnet",
+                    networkName: "matic",
                 } as any);
             } catch (err: any) {
                 expect(err.message).to.equal(
@@ -136,9 +133,8 @@ describe("Framework Tests", () => {
     describe("Framework.create Tests", () => {
         it("Should throw an error if loadFramework fails", async () => {
             try {
-                const chainId = (await deployer.provider!.getNetwork()).chainId;
[…]

### 2022-11-15 packages/sdk-core/test/1_supertoken.test.ts

@@ -1,1152 +1,0 @@
-import { expect } from "chai";
-import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
-import { Framework } from "../src/index";
-import {
-    IConstantFlowAgreementV1,
-    IInstantDistributionAgreementV1,
-    SuperToken as SuperTokenType,
-    TestToken,
-} from "../src/typechain";
-import { SuperToken } from "../src";
-import { getFlowOperatorId, getPerSecondFlowRateByMonth } from "../src/utils";
-import { setup } from "../scripts/setup";
-import { ROPSTEN_SUBGRAPH_ENDPOINT } from "./0_framework.test";
-import { BigNumber, BigNumberish, ethers } from "ethers";
-import { NativeAssetSuperToken, WrapperSuperToken } from "../src/SuperToken";
-import {
-    AUTHORIZE_FLOW_OPERATOR_CREATE,
-    AUTHORIZE_FULL_CONTROL,
-} from "../src/constants";
-
-const INITIAL_AMOUNT_PER_USER = "10000000000";
-const toBN = (x: BigNumberish) => ethers.BigNumber.from(x);
-const MAX_FLOW_RATE = toBN(2).pow(toBN(95)).sub(toBN(1)).toString();
-
-export const clipDepositNumber = (deposit: BigNumber, roundingDown = false) => {
-    // last 32 bits of the deposit (96 bits) is clipped off
-    const rounding = roundingDown
-        ? 0
-        : deposit.and(toBN(0xffffffff)).isZero()
-        ? 0
-        : 1;
-    return deposit.shr(32).add(toBN(rounding)).shl(32);
-};
-
-describe("SuperToken Tests", () => {
-    let framework: Framework;
-    let cfaV1: IConstantFlowAgreementV1;
-    let idaV1: IInstantDistributionAgreementV1;
-    let deployer: SignerWithAddress;
-    let alpha: SignerWithAddress;
-    let superToken: SuperTokenType;
-    let token: TestToken;
-    let daix: WrapperSuperToken;
-    let bravo: SignerWithAddress;
-    let charlie: SignerWithAddress;
-    let signerCount: number;
-
-    before(async () => {
-        const {
-            frameworkClass,
-            CFAV1,
-            IDAV1,
-            Deployer,
-            Alpha,
-            Bravo,
-            Charlie,
-            SuperToken,
-            Token,
-            SignerCount,
[…]

### 2022-11-15 packages/sdk-core/test/2_ida.test.ts

@@ -1,0 +1,386 @@
+import { expect } from "chai";
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { Framework } from "../src/index";
+import { IInstantDistributionAgreementV1, SuperToken } from "../src/typechain";
+import { setup } from "../scripts/setup";
+import { ethers } from "ethers";
+
+describe("IDA V1 Tests", () => {
+    let idaV1: IInstantDistributionAgreementV1;
+    let framework: Framework;
+    let deployer: SignerWithAddress;
+    let alpha: SignerWithAddress;
+    let superToken: SuperToken;
+    let bravo: SignerWithAddress;
+
+    before(async () => {
+        const { IDAV1, frameworkClass, Deployer, Alpha, Bravo, SuperToken } =
+            await setup({ dataMode: "WEB3_ONLY" });
+        idaV1 = IDAV1;
+        framework = frameworkClass;
+        deployer = Deployer;
+        alpha = Alpha;
+        bravo = Bravo;
+        superToken = SuperToken;
+    });
+
+    it("Should throw an error if one of the input addresses is invalid", async () => {
+        try {
+            framework.idaV1.createIndex({
+                indexId: "0",
+                superToken: superToken.address + "z",
+            });
+        } catch (err: any) {
+            expect(err.message).to.eql(
+                "Invalid Address Error - The address you have entered is not a valid ethereum address."
+            );
+        }
+    });
+
+    it("Should throw an error on the reads as expected", async () => {
+        // NOTE: using casting to pass in wrong input to force error
+        try {
+            await framework.idaV1.getIndex({
+                superToken: superToken.address,
+                publisher: deployer.address,
+                indexId: "0",
+                providerOrSigner: "" as any,
+            });
+        } catch (err: any) {
+            expect(err.message).to.contain(
+                "InstantDistributionAgreementV1 Read Error - There was an error getting the index"
+            );
+        }
+
+        try {
+            await framework.idaV1.getSubscription({
+                superToken: superToken.address,
+                publisher: deployer.address,
+                indexId: "0",
+                subscriber: alpha.address,
+                providerOrSigner: "" as any,
+            });
+        } catch (err: any) {
+            expect(err.message).to.contain(
+                "InstantDistributionAgreementV1 Read Error - There was an error getting the subscription"
+            );
+        }
+    });
+
+    it("Should create an index properly and get the newly created index", async () => {
+        await expect(
+            framework.idaV1
[…]

### 2022-11-15 packages/sdk-redux/src/redux-slices/rtk-query/cacheTags/CacheTagTypes.ts

@@ -1,0 +1,22 @@
+// NOTE: If you add a type here then you have to also add it to tag types on the RTK Query slice.
+/**
+ * All possible cache tag types.
+ * @private
+ * @category Cache Tags
+ */
+export type CacheTagTypes = 'Event' | 'Index' | 'Stream' | 'Token';
+
+/**
+ * Create a cache tag for RTK-Query.
+ * @private
+ * @category Cache Tags
+ */
+export const createTag = (type: CacheTagTypes, ...keys: (string | number)[]) => ({
+    type: type,
+    id: keys.join('_').toLowerCase(),
+});
+
+// Order of address priorities if all present:
+// 1. SuperToken Address
+// 2. Publisher / Sender / From Address
+// 3. Subscriber / Receiver / To Address

### 2022-11-15 packages/sdk-redux/src/redux-slices/rtk-query/subgraph-slice/createEntityQueryEndpoints.ts

@@ -1,0 +1,133 @@
+import {QueryDefinition} from '@reduxjs/toolkit/dist/query';
+import {
+    Account,
+    AccountQueryHandler,
+    AccountTokenSnapshot,
+    AccountTokenSnapshotQueryHandler,
+    ILightEntity,
+    Index,
+    IndexQueryHandler,
+    IndexSubscription,
+    IndexSubscriptionQueryHandler,
+    PagedResult,
+    RelevantAddressProviderFromFilter,
+    RelevantAddressProviderFromResult,
+    Stream,
+    StreamPeriod,
+    StreamPeriodQueryHandler,
+    StreamQueryHandler,
+    SubgraphGetQuery,
+    SubgraphGetQueryHandler,
+    SubgraphListQuery,
+    SubgraphListQueryHandler,
+    Token,
+    TokenQueryHandler,
+    TokenStatistic,
+    TokenStatisticQueryHandler,
+} from '@superfluid-finance/sdk-core';
+
+import {CacheTagTypes} from '../cacheTags/CacheTagTypes';
+import {CacheTime} from '../cacheTime';
+
+import {
+    AccountQuery,
+    AccountsQuery,
+    AccountTokenSnapshotQuery,
+    AccountTokenSnapshotsQuery,
+    IndexesQuery,
+    IndexQuery,
+    IndexSubscriptionQuery,
+    IndexSubscriptionsQuery,
+    StreamPeriodQuery,
+    StreamPeriodsQuery,
+    StreamQuery,
+    StreamsQuery,
+    TokenQuery,
+    TokensQuery,
+    TokenStatisticQuery,
+    TokenStatisticsQuery,
+} from './entityQueryArgs';
+import {provideCacheTagsFromRelevantAddresses} from './provideCacheTagsFromRelevantAddresses';
+import {SubgraphSliceBaseQueryType, SubgraphSliceEndpointBuilder} from './subgraphSlice';
+
+export const createEntityQueryEndpoints = (builder: SubgraphSliceEndpointBuilder) => {
+    // NOTE: Ignoring prettier because longer lines are more readable here.
+    // prettier-ignore
+    return {
+        account: get<Account, AccountQuery>(builder, new AccountQueryHandler(), "Event"),
+        accounts: list<Account, AccountsQuery>(builder, new AccountQueryHandler(), "Event"),
+        accountTokenSnapshot: get<AccountTokenSnapshot, AccountTokenSnapshotQuery>(builder, new AccountTokenSnapshotQueryHandler(), "Token"),
[…]

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/cacheTags/monitorAddressForNextEventToInvalidateCache.ts

@@ -1,31 +1,0 @@
-import {AnyAction} from '@reduxjs/toolkit';
-import {ThunkDispatch} from '@reduxjs/toolkit';
-
-import {getFramework} from '../../../sdkReduxConfig';
-import {MillisecondTimes} from '../../../utils';
-import {TransactionInfo} from '../../argTypes';
-
-import {invalidateSpecificCacheTagsForEvents} from './invalidateSpecificCacheTagsForEvents';
-
-/**
- * Monitors given address for next event to invalidate cache and then stops.
- * NOTE: Optimizations for robustness could be done here.
- * @private
- * @category Cache Tags
- */
-export const monitorAddressForNextEventToInvalidateCache = async (
-    address: string,
-    transactionInfo: TransactionInfo,
-    dispatch: ThunkDispatch<any, any, AnyAction>
-) => {
-    const framework = await getFramework(transactionInfo.chainId);
-    framework.query.on(
-        (events, unsubscribe) => {
-            invalidateSpecificCacheTagsForEvents(transactionInfo.chainId, events, dispatch);
-            unsubscribe();
-        },
-        MillisecondTimes.OneSecond,
-        address,
-        MillisecondTimes.OneMinute
-    );
-};

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/endpoints/flowEndpoints.ts

@@ -1,91 +1,0 @@
-import {getFramework, getSigner} from '../../../../sdkReduxConfig';
-import {TransactionInfo} from '../../../argTypes';
-import {registerNewTransactionAndReturnQueryFnResult} from '../../../transactionTrackerSlice/registerNewTransaction';
-import {RpcEndpointBuilder} from '../rpcEndpointBuilder';
-
-import {FlowCreateMutation, FlowDeleteMutation, FlowUpdateMutation} from './flowArgs';
-
-export const createFlowEndpoints = (builder: RpcEndpointBuilder) => ({
-    flowCreate: builder.mutation<TransactionInfo, FlowCreateMutation>({
-        queryFn: async (arg, queryApi) => {
-            const signer = await getSigner(arg.chainId);
-            const framework = await getFramework(arg.chainId);
-            const superToken = await framework.loadSuperToken(arg.superTokenAddress);
-
-            const senderAddress = arg.senderAddress ? arg.senderAddress : await signer.getAddress();
-
-            const transactionResponse = await superToken
-                .createFlow({
-                    sender: senderAddress,
-                    receiver: arg.receiverAddress,
-                    flowRate: arg.flowRateWei,
-                    userData: arg.userDataBytes,
-                })
-                .exec(signer);
-
-            return await registerNewTransactionAndReturnQueryFnResult({
-                transactionResponse,
-                chainId: arg.chainId,
-                signer: senderAddress,
-                waitForConfirmation: !!arg.waitForConfirmation,
-                dispatch: queryApi.dispatch,
-                title: 'Create Stream',
-                extraData: arg.transactionExtraData,
-            });
-        },
-    }),
-    flowUpdate: builder.mutation<TransactionInfo, FlowUpdateMutation>({
-        queryFn: async (arg, queryApi) => {
-            const signer = await getSigner(arg.chainId);
-            const framework = await getFramework(arg.chainId);
-            const superToken = await framework.loadSuperToken(arg.superTokenAddress);
-            const senderAddress = arg.senderAddress ? arg.senderAddress : await signer.getAddress();
-
-            const transactionResponse = await superToken
-                .updateFlow({
-                    sender: senderAddress,
-                    receiver: arg.receiverAddress,
-                    flowRate: arg.flowRateWei,
-                    userData: arg.userDataBytes,
-                })
-                .exec(signer);
-
-            return await registerNewTransactionAndReturnQueryFnResult({
-                transactionResponse,
-                chainId: arg.chainId,
[…]

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/endpoints/indexArgs.ts

@@ -1,82 +1,0 @@
-import {BaseSuperTokenMutation, NothingString} from '../../../argTypes';
-
-/**
- * Creates an IDA Index.
- */
-export interface IndexCreateMutation extends BaseSuperTokenMutation {
-    /** The id of the index. */
-    indexId: string;
-    /** Extra user data provided. */
-    userDataBytes: string | NothingString;
-}
-
-/**
- * Updates the `units` allocated to a Subscription.
- */
-export interface IndexUpdateSubscriptionUnitsMutation extends BaseSuperTokenMutation {
-    /** The subscriber address whose units you want to update. */
-    subscriberAddress: string;
-    /** The id of the index. */
-    indexId: string;
-    /** The amount of units you want to update to. */
-    unitsNumber: string;
-    /** Extra user data provided. */
-    userDataBytes: string | NothingString;
-}
-
-/**
- * Deletes a Subscription by setting the `units` allocated to the Subscriber to 0.
- */
-export interface IndexDeleteSubscriptionMutation extends BaseSuperTokenMutation {
-    /** The id of the index. */
-    indexId: string;
-    /** The subscriber address whose subscription you want to delete. */
-    publisherAddress: string;
-    /** The publisher address of the index you are targeting. */
-    subscriberAddress: string;
-    /** Extra user data provided. */
-    userDataBytes: string | NothingString;
-}
-
-/**
- * Distributes `amount` of token to an index
- */
-export interface IndexDistributeMutation extends BaseSuperTokenMutation {
-    /** The id of the index. */
-    indexId: string;
-    /** The amount of tokens to be distributed. */
-    amountWei: string;
-    /** Extra user data provided. */
-    userDataBytes: string | NothingString;
-}
-
-/**
- * Approves a Subscription, so the Subscriber won't need to claim tokens when the Publisher distributes.
- */
-export interface IndexSubscriptionApproveMutation extends BaseSuperTokenMutation {
-    indexId: string;
-    publisherAddress: string;
-    userDataBytes: string | NothingString;
-}
-
-/**
- * Revokes a Subscription, so the Subscriber will need to claim tokens when the Publisher distributes.
- */
-export interface IndexSubscriptionRevokeMutation extends BaseSuperTokenMutation {
-    /** The id of the index. */
-    indexId: string;
-    /** The index publisher address you want to revoke for the subscriber. */
-    publisherAddress: string;
-    /** Extra user data provided. */
[…]

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/rpcApiSlice.ts

@@ -1,21 +1,0 @@
-import {CreateApi} from '@reduxjs/toolkit/dist/query';
-import type {ModuleName} from '@reduxjs/toolkit/dist/query/apiTypes';
-
-import {typeGuard} from '../../../utils';
-import {cacheTagTypes} from '../cacheTags/CacheTagTypes';
-import {getSerializeQueryArgs} from '../getSerializeQueryArgs';
-
-import {rpcBaseQuery} from './rpcBaseQuery';
-import {RpcEndpointBuilder} from './rpcEndpointBuilder';
-import {RpcReducerPath} from './rpcReducerPath';
-
-export const createRpcApiSlice = <T extends ModuleName>(createRtkQueryApi: CreateApi<T>) =>
-    createRtkQueryApi({
-        reducerPath: typeGuard<RpcReducerPath>('superfluid_rpc'),
-        baseQuery: rpcBaseQuery(),
-        tagTypes: cacheTagTypes,
-        endpoints: (_builder: RpcEndpointBuilder) => ({}),
-        serializeQueryArgs: getSerializeQueryArgs(),
-    });
-
-export type RpcApiSliceEmpty = ReturnType<typeof createRpcApiSlice>;

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/rpcBaseQuery.ts

@@ -1,8 +1,0 @@
-import {SerializedError} from '@reduxjs/toolkit';
-import {BaseQueryFn} from '@reduxjs/toolkit/dist/query';
-
-export const rpcBaseQuery = (): BaseQueryFn<void, unknown, SerializedError, Record<string, unknown>> => () => {
-    throw new Error('All queries & mutations must use the `queryFn` definition syntax.');
-};
-
-export type RpcBaseQuery = ReturnType<typeof rpcBaseQuery>;

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/rpcEndpointBuilder.ts

@@ -1,8 +1,0 @@
-import {EndpointBuilder} from '@reduxjs/toolkit/dist/query/endpointDefinitions';
-
-import {CacheTagType} from '../cacheTags/CacheTagTypes';
-
-import {RpcBaseQuery} from './rpcBaseQuery';
-import {RpcReducerPath} from './rpcReducerPath';
-
-export type RpcEndpointBuilder = EndpointBuilder<RpcBaseQuery, CacheTagType, RpcReducerPath>;

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/rpcApiSlice/rpcReducerPath.ts

@@ -1,1 +1,0 @@
-export type RpcReducerPath = 'superfluid_rpc';

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/subgraphApiSlice/endpoints/entityEndpoints.ts

@@ -1,131 +1,0 @@
-import {
-    Account,
-    AccountQueryHandler,
-    AccountTokenSnapshot,
-    AccountTokenSnapshotQueryHandler,
-    ILightEntity,
-    Index,
-    IndexQueryHandler,
-    IndexSubscription,
-    IndexSubscriptionQueryHandler,
-    PagedResult,
-    RelevantAddressProviderFromFilter,
-    RelevantAddressProviderFromResult,
-    Stream,
-    StreamPeriod,
-    StreamPeriodQueryHandler,
-    StreamQueryHandler,
-    SubgraphGetQuery,
-    SubgraphGetQueryHandler,
-    SubgraphListQuery,
-    SubgraphListQueryHandler,
-    Token,
-    TokenQueryHandler,
-    TokenStatistic,
-    TokenStatisticQueryHandler,
-} from '@superfluid-finance/sdk-core';
-
-import {getSubgraphClient} from '../../../../sdkReduxConfig';
-import {createGeneralTags} from '../../cacheTags/CacheTagTypes';
-import {CacheTime} from '../../cacheTime';
-import {provideSpecificCacheTagsFromRelevantAddresses} from '../provideSpecificCacheTagsFromRelevantAddresses';
-import {SubgraphEndpointBuilder} from '../subgraphEndpointBuilder';
-
-import {
-    AccountQuery,
-    AccountsQuery,
-    AccountTokenSnapshotQuery,
-    AccountTokenSnapshotsQuery,
-    IndexesQuery,
-    IndexQuery,
-    IndexSubscriptionQuery,
-    IndexSubscriptionsQuery,
-    StreamPeriodQuery,
-    StreamPeriodsQuery,
-    StreamQuery,
-    StreamsQuery,
-    TokenQuery,
-    TokensQuery,
-    TokenStatisticQuery,
-    TokenStatisticsQuery,
-} from './entityArgs';
-
-export const createEntityEndpoints = (builder: SubgraphEndpointBuilder) => {
-    // NOTE: Ignoring prettier because longer lines are more readable here.
-    // prettier-ignore
-    return {
-        account: get<Account, AccountQuery>(builder, new AccountQueryHandler()),
-        accounts: list<Account, AccountsQuery>(builder, new AccountQueryHandler()),
-        accountTokenSnapshot: get<AccountTokenSnapshot, AccountTokenSnapshotQuery>(builder, new AccountTokenSnapshotQueryHandler()),
[…]

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/subgraphApiSlice/provideSpecificCacheTagsFromRelevantAddresses.ts

@@ -1,26 +1,0 @@
-import {RelevantAddresses} from '@superfluid-finance/sdk-core';
-
-import {createMostSpecificTag} from '../cacheTags/CacheTagTypes';
-
-export const provideSpecificCacheTagsFromRelevantAddresses = (
-    chainId: number,
-    relevantAddresses: RelevantAddresses
-) => {
-    if (relevantAddresses.tokens.length) {
-        return relevantAddresses.tokens
-            .map((tokenAddress: string) =>
-                [createMostSpecificTag({chainId, address1: tokenAddress})].concat(
-                    relevantAddresses.accounts.map((accountAddress: string) =>
-                        createMostSpecificTag({chainId, address1: tokenAddress, address2: accountAddress})
-                    )
-                )
-            )
-            .flat();
-    } else if (relevantAddresses.accounts.length) {
-        return relevantAddresses.accounts.map((accountAddress: string) =>
-            createMostSpecificTag({chainId, address1: accountAddress})
-        );
-    } else {
-        return [createMostSpecificTag({chainId})];
-    }
-};

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/subgraphApiSlice/subgraphBaseQuery.ts

@@ -1,8 +1,0 @@
-import {SerializedError} from '@reduxjs/toolkit';
-import {BaseQueryFn} from '@reduxjs/toolkit/dist/query';
-
-export const subgraphBaseQuery = (): BaseQueryFn<void, unknown, SerializedError, Record<string, unknown>> => () => {
-    throw new Error('All queries & mutations must use the `queryFn` definition syntax.');
-};
-
-export type SubgraphBaseQuery = ReturnType<typeof subgraphBaseQuery>;

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/subgraphApiSlice/subgraphEndpointBuilder.ts

@@ -1,8 +1,0 @@
-import {EndpointBuilder} from '@reduxjs/toolkit/dist/query/endpointDefinitions';
-
-import {CacheTagType} from '../cacheTags/CacheTagTypes';
-
-import {SubgraphBaseQuery} from './subgraphBaseQuery';
-import {SubgraphReducerPath} from './subgraphReducerPath';
-
-export type SubgraphEndpointBuilder = EndpointBuilder<SubgraphBaseQuery, CacheTagType, SubgraphReducerPath>;

### 2022-11-15 packages/sdk-redux/src/reduxSlices/rtkQuery/subgraphApiSlice/subgraphReducerPath.ts

@@ -1,1 +1,0 @@
-export type SubgraphReducerPath = 'superfluid_subgraph';

### 2022-11-15 packages/sdk-redux/src/reduxSlices/transactionTrackerSlice/ethersError.ts

@@ -1,7 +1,0 @@
-import {ethers} from 'ethers';
-
-export type EthersError = Error & {
-    code: ethers.errors;
-    reason?: 'replaced' | 'repriced' | 'cancelled';
-    cancelled?: boolean;
-};

### 2022-11-15 packages/sdk-redux/src/reduxSlices/transactionTrackerSlice/registerNewTransaction.ts

@@ -1,66 +1,0 @@
-import {ThunkDispatch} from '@reduxjs/toolkit';
-import {ethers} from 'ethers';
-
-import {getFramework} from '../../sdkReduxConfig';
-
-import {initiateNewTransactionTrackingThunk} from './thunks/initiateNewTransactionTrackingThunk';
-import {TransactionTitle} from './transactionTitle';
-import {waitForOneConfirmation} from './waitForOneConfirmation';
-
-export interface RegisterNewTransactionArg {
-    /**
-     * The chain ID transaction is on.
-     * WARNING: Don't pass `chainId` off of ether's `TransactionResponse` because it's not set correctly on timely manner.
-     */
-    chainId: number;
-    signer: string;
-    transactionResponse: ethers.providers.TransactionResponse;
-    /**
-     * Whether to wait for one transaction confirmation.
-     */
-    waitForConfirmation: boolean;
-    /**
-     * For dispatching redux thunks.
-     */
-    dispatch: ThunkDispatch<any, any, any>;
-    /**
-     * Any key you want to give the transaction to identify it later.
-     */
-    title: TransactionTitle;
-    /**
-     * Any extra data you want to attach to the transaction. Make sure it's serializable!
-     */
-    extraData: Record<string, unknown> | undefined;
-}
-
-/**
- * Transactions have to be registered for them to be tracked inside the redux store and monitored for re-orgs.
- */
-export const registerNewTransaction = async (arg: RegisterNewTransactionArg) => {
-    const {chainId, signer, transactionResponse, waitForConfirmation, dispatch, title, extraData} = arg;
-    const framework = await getFramework(chainId);
-
-    dispatch(
-        initiateNewTransactionTrackingThunk({
-            chainId,
-            signer,
-            transactionResponse,
-            title,
-            extraData: extraData ?? {},
-        })
-    );
-
-    if (waitForConfirmation) {
-        await waitForOneConfirmation(framework.settings.provider, transactionResponse.hash);
-    }
-};
-
-export const registerNewTransactionAndReturnQueryFnResult = async (arg: RegisterNewTransactionArg) => {
-    registerNewTransaction(arg);
-    return {
-        data: {
-            hash: arg.transactionResponse.hash,
-            chainId: arg.chainId,
-        },
-    };
-};

### 2022-11-15 packages/sdk-redux/src/reduxSlices/transactionTrackerSlice/thunks/initiateNewTransactionTrackingThunk.ts

@@ -1,41 +1,0 @@
-import {createAsyncThunk} from '@reduxjs/toolkit';
-import {ethers} from 'ethers';
-
-import {getTransactionTrackerSlice} from '../../../sdkReduxConfig';
-import {TransactionTitle} from '../transactionTitle';
-import {transactionTrackerSlicePrefix} from '../transactionTrackerSlice';
-
-import {trackPendingTransactionThunk} from './trackPendingTransactionThunk';
-
-/**
- * Used for tracking _brand new_ transactions.
- */
-export const initiateNewTransactionTrackingThunk = createAsyncThunk<
-    void,
-    {
-        chainId: number;
-        transactionResponse: ethers.providers.TransactionResponse;
-        signer: string;
-        title: TransactionTitle;
-        extraData: Record<string, unknown>;
-    }
->(`${transactionTrackerSlicePrefix}/initiateNewTransactionTracking`, async (arg, {dispatch}) => {
-    arg.transactionResponse.chainId = arg.chainId; // Recommended by Ethers to specify Chain ID when doing serialization.
-
-    const transactionHash = arg.transactionResponse.hash;
-
-    dispatch(
-        getTransactionTrackerSlice().actions.addTransaction({
-            chainId: arg.chainId,
-            hash: transactionHash,
-            signer: ethers.utils.getAddress(arg.signer),
-            timestampMs: new Date().getTime(),
-            status: 'Pending',
-            transactionResponse: ethers.utils.serializeTransaction(arg.transactionResponse),
-            title: arg.title,
-            extraData: arg.extraData,
-        })
-    );
-
-    dispatch(trackPendingTransactionThunk({transactionHash, chainId: arg.chainId}));
-});

### 2022-11-15 packages/sdk-redux/src/utils.ts

@@ -10,8 +10,8 @@ export const typeGuard = <T>(obj: T) => obj;
  * The reasoning for such a helper is to conditionally add items to an array in a nice syntax.
  * @private
  */
-export function insertIf<T>(condition: boolean | unknown, getElements: () => T[]): T[] {
-    return condition ? getElements() : [];
+export function insertIf<T>(condition: boolean | unknown, ...elements: T[]): T[] {
+    return condition ? elements : [];
 }
 
 /**

### 2022-11-15 packages/spec-haskell/packages/validator/src/Main.hs

@@ -1,14 +1,0 @@
-import           System.Environment                    (getArgs)
-
-import           Money.Superfluid.Validator.Simulation (runSimMonad)
-
-import qualified Money.Superfluid.Validator.Demos.DFA
-import qualified Money.Superfluid.Validator.Demos.Expo
-
-main :: IO ()
-main = do
-    args <- getArgs
-    case args of
-        ["--demo", "expo"] -> runSimMonad Money.Superfluid.Validator.Demos.Expo.demo
-        ["--demo", "dfa"]  -> runSimMonad Money.Superfluid.Validator.Demos.DFA.demo
-        _                  -> putStrLn "---- Welcome to Superfluid Validator ----"

### 2022-11-15 packages/spec-haskell/packages/validator/src/Money/Superfluid/Validator/Demos/DFA.hs

@@ -1,61 +1,0 @@
-{-# OPTIONS_GHC -Wno-missing-signatures #-}
-{-# LANGUAGE OverloadedStrings #-}
-
-module Money.Superfluid.Validator.Demos.DFA (demo) where
-
-import           Control.Monad
-import           Control.Monad.IO.Class
-import           Data.Coerce
-import           Data.Time.Clock.POSIX                    (getPOSIXTime)
-import           GHC.Stack
-import           Text.Printf
-
-import qualified Money.Superfluid.Instances.Simple.System as SF
-
-import           Money.Superfluid.Validator.Simulation
-
-now =  do
-    t <- getPOSIXTime
-    return $ fromIntegral (round t :: SF.SimpleTimestamp)
-
-initBalance = SF.toWad (10000.0 :: Double)
-
-distributionLimitN n = SF.toWad $ 1000 * (n :: Double)
-
-token = "MAGIC"
-alice = "alice"
-bob = "bob"
-carol = "carol"
-dan = "dan"
-
-travelDaysAndPrintBalances :: HasCallStack => SF.SimpleTimestamp -> Int -> SimMonad ()
-travelDaysAndPrintBalances t0 days = do
-    t <- getCurrentTime
-    let t_offset = t - t0
-    forM_ [(1::Int) .. 24 * days] $ \i -> do
-        timeTravel 3600
-        aliceBalance <- runToken token $ SF.balanceOfAccount alice
-        bobBalance <- runToken token $ SF.balanceOfAccount bob
-        carolBalance <- runToken token $ SF.balanceOfAccount carol
-        danBalance <- runToken token $ SF.balanceOfAccount dan
-        liftIO $ putStrLn $ printf "%f %s %s %s %s"
-            ((fromIntegral (coerce t_offset + i * 3600) :: Double) / (3600.0 * 24))
-            (show . SF.untappedLiquidityFromRTB $ aliceBalance)
-            (show . SF.untappedLiquidityFromRTB $ bobBalance)
-            (show . SF.untappedLiquidityFromRTB $ carolBalance)
-            (show . SF.untappedLiquidityFromRTB $ danBalance)
-
-demo :: HasCallStack => SimMonad ()
-demo = do
-    liftIO $ putStrLn "==== Decaying ConstantFlow Agreement Demo ====\n"
-    t0 <- liftIO now
-    timeTravel t0
-    createToken token [alice, bob, carol, dan] initBalance
[…]

### 2022-11-15 packages/subgraph/scripts/deployContractsAndToken.ts

@@ -1,9 +1,7 @@
-import {ethers} from "hardhat";
+import { ethers } from "hardhat";
 import deployFramework from "@superfluid-finance/ethereum-contracts/scripts/deploy-framework";
 import deployTestToken from "@superfluid-finance/ethereum-contracts/scripts/deploy-test-token";
 import deploySuperToken from "@superfluid-finance/ethereum-contracts/scripts/deploy-super-token";
-import deployNativeSuperToken from "@superfluid-finance/ethereum-contracts/scripts/deploy-unlisted-native-super-token";
-// import resolverListSuperToken from "@superfluid-finance/ethereum-contracts/scripts/resolver-list-super-token";
 import set3PsConfig from "@superfluid-finance/ethereum-contracts/scripts/gov-set-3Ps-config";
 
 export const errorHandler = (type: string, err: any) => {
@@ -32,37 +30,9 @@ async function main() {
             from: Deployer,
         }
     );
-    // deploy native asset super token
-    await deploySuperToken(
-        (x: any) => errorHandler("SuperToken", x),
-        [":", "ETH"],
-        {
-            web3: (global as any).web3,
-            from: Deployer,
-        }
-    );
-    // deploy native super token
-    await deployNativeSuperToken(
-        (x: any) => errorHandler("NativeSuperToken", x),
-        [":", "Mr.Token", "MR", "10000000"],
-        {
-            web3: (global as any).web3,
-            from: Deployer,
-        }
-    );
-    // TODO: figure out why this script is not properly getting the token symbol
-    // await resolverListSuperToken(
-    //     (x: any) => errorHandler("ResolverListSuperToken", x),
-    //     [":", mrTokenAddress],
-    //     {
-    //         web3: (global as any).web3,
-    //         from: Deployer,
-    //     }
-    // );
     await set3PsConfig(
         (x: any) => errorHandler("3PsConfig", x),
-        [":", "0x1f65B7b9b3ADB4354fF76fD0582bB6b0d046a41c", 3600, 720],
-        {
+        [":", "0x1f65B7b9b3ADB4354fF76fD0582bB6b0d046a41c", 3600, 720], {
             web3: (global as any).web3,
             from: Deployer,
         }

### 2022-11-15 packages/subgraph/src/addresses.template.ts

@@ -41,13 +41,13 @@ export function getHostAddress(): Address {
         address = "0x74b57883f8ce9F2BD330286E884CfD8BB24AC4ED";
     }
     if (network == "avalanche") {
-        address = "0x60377C7016E4cdB03C87EF474896C11cB560752C";
+        address = "";
     }
     if (network == "arbitrum-one") {
-        address = "0xCf8Acb4eF033efF16E8080aed4c7D5B9285D2192";
+        address = "";
     }
     if (network == "optimism") {
-        address = "0x567c4B141ED61923967cA25Ef4906C8781069a10";
+        address = "";
     }
     return Address.fromString(address);
 }
@@ -89,13 +89,13 @@ export function getResolverAddress(): Address {
         address = "0x218B65780615Ff134f9Ad810CB98839534D3C0D6";
     }
     if (network == "avalanche") {
-        address = "0x24a3F04F70B7f07B9673EadD3e146391BcfEa5c1";
+        address = "";
     }
     if (network == "arbitrum-one") {
-        address = "0x609b9d9d6Ee9C3200745A79B9d3398DBd63d509F";
+        address = "";
     }
     if (network == "optimism") {
-        address = "0x743B5f46BC86caF41bE4956d9275721E0531B186";
+        address = "";
     }
     return Address.fromString(address);
 }

### 2022-11-15 packages/subgraph/src/mappings/resolver.ts

@@ -8,7 +8,7 @@ import {
     RoleGrantedEvent,
     RoleRevokedEvent,
 } from "../../generated/schema";
-import {createEventID, getOrder} from "../utils";
+import { createEventID } from "../utils";
 
 export function handleRoleAdminChanged(event: RoleAdminChanged): void {
     let ev = new RoleAdminChangedEvent(
@@ -17,8 +17,6 @@ export function handleRoleAdminChanged(event: RoleAdminChanged): void {
     ev.transactionHash = event.transaction.hash;
     ev.timestamp = event.block.timestamp;
     ev.blockNumber = event.block.number;
-    ev.order = getOrder(event.block.number, event.logIndex);
-    ev.logIndex = event.logIndex;
     ev.name = "RoleAdminChanged";
     ev.addresses = [];
     ev.role = event.params.role;
@@ -32,8 +30,6 @@ export function handleRoleGranted(event: RoleGranted): void {
     ev.transactionHash = event.transaction.hash;
     ev.timestamp = event.block.timestamp;
     ev.blockNumber = event.block.number;
-    ev.logIndex = event.logIndex;
-    ev.order = getOrder(event.block.number, event.logIndex);
     ev.name = "RoleGranted";
     ev.addresses = [];
     ev.role = event.params.role;
@@ -46,8 +42,6 @@ export function handleRoleRevoked(event: RoleRevoked): void {
     ev.transactionHash = event.transaction.hash;
     ev.timestamp = event.block.timestamp;
     ev.blockNumber = event.block.number;
-    ev.logIndex = event.logIndex;
-    ev.order = getOrder(event.block.number, event.logIndex);
     ev.name = "RoleRevoked";
     ev.addresses = [];
     ev.role = event.params.role;

### 2022-11-15 packages/subgraph/tasks/deploy-all-networks.sh

@@ -4,10 +4,10 @@ JQ="../../node_modules/node-jq/bin/jq"
 mustache="../../node_modules/mustache/bin/mustache"
 graph="../../node_modules/@graphprotocol/graph-cli"
 
-NETWORKS=( $($JQ -r .[] ./networks.json) )
+CONTRACTS=( $($JQ -r .[] ./networks.json) )
 [ $? == 0 ] || exit 1
 
 chmod +x ./tasks/deploy-to-network.sh
-for i in "${NETWORKS[@]}";do
+for i in "${CONTRACTS[@]}";do
     ./tasks/deploy-to-network.sh $1 $i
 done

### 2022-11-15 packages/subgraph/test/queries/eventQueries.ts

@@ -1,4 +1,4 @@
-import {gql} from "graphql-request";
+import { gql } from "graphql-request";
 
 // CFA Event Queries
 export const getFlowUpdatedEvents = gql`
@@ -7,49 +7,20 @@ export const getFlowUpdatedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
-            transactionHash
             timestamp
+            transactionHash
             name
             blockNumber
-            logIndex
             addresses
             token
             sender
             receiver
-            flowOperator
             flowRate
             totalAmountStreamedUntilTimestamp
             totalSenderFlowRate
             totalReceiverFlowRate
-            deposit
             oldFlowRate
             type
-        }
-    }
-`;
-
-export const getFlowOperatorUpdatedEvents = gql`
-    query getFlowOperatorUpdatedEvents($transactionHash: Bytes!) {
-        response: flowOperatorUpdatedEvents(
-            where: { transactionHash: $transactionHash }
-        ) {
-            id
-            order
-            transactionHash
-            timestamp
-            name
-            blockNumber
-            logIndex
-            addresses
-            token
-            sender
-            flowOperator
-            permissions
-            flowRateAllowance
-            flowOperator {
-                id
-            }
         }
     }
 `;
@@ -62,11 +33,9 @@ export const getIndexCreatedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
             transactionHash
             name
             blockNumber
-            logIndex
             addresses
             token
             publisher
@@ -85,11 +54,9 @@ export const getIndexDistributionClaimedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
             transactionHash
             name
             blockNumber
-            logIndex
             addresses
             token
             publisher
@@ -109,11 +76,9 @@ export const getIndexUpdatedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
             transactionHash
             name
             blockNumber
-            logIndex
             addresses
             token
             publisher
@@ -136,11 +101,9 @@ export const getIndexSubscribedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
             transactionHash
             name
             blockNumber
-            logIndex
             addresses
             token
             publisher
@@ -160,11 +123,9 @@ export const getIndexUnitsUpdatedEvents = gql`
             where: { transactionHash: $transactionHash }
         ) {
             id
-            order
             transactionHash
             name
[…]

### 2022-11-15 packages/subgraph/test/queries/globalQueries.ts

@@ -1,386 +1,0 @@
-import { gql } from "graphql-request";
-
-const getAccountIds = gql`
-    query getAccountIds($id: ID!) {
-        response: accounts(where: { id: $id }) {
-            id
-        }
-    }
-`;
-
-const getAccountTokenSnapshotIds = gql`
-    query getAccountTokenSnapshotIds($id: ID!) {
-        response: accountTokenSnapshots(where: { account: $id }) {
-            id
-        }
-    }
-`;
-
-const getEvents = gql`
-    query getEvents {
-        response: events {
-            id
-        }
-    }
-`;
-
-const getFlowUpdatedEventsLightEntities = gql`
-    query getFlowUpdatedEventsLightEntities {
-        response: flowUpdatedEvents {
-            stream {
-                id
-            }
-        }
-    }
-`;
-
-const getFlowOperatorUpdatedEventsLightEntities = gql`
-    query getFlowOperatorUpdatedEventsLightEntities {
-        response: flowOperatorUpdatedEvents {
-            flowOperator {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexCreatedEventsLightEntities = gql`
-    query getIndexCreatedEventsLightEntities {
-        response: indexCreatedEvents {
-            index {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexDistributionClaimedEventsLightEntities = gql`
-    query getIndexDistributionClaimedEventsLightEntities {
-        response: indexDistributionClaimedEvents {
-            index {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexUpdatedEventsLightEntities = gql`
-    query getIndexUpdatedEventsLightEntities {
-        response: indexUpdatedEvents {
-            index {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexSubscribedEventsLightEntities = gql`
-    query getIndexSubscribedEventsLightEntities {
-        response: indexSubscribedEvents {
-            index {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexUnitsUpdatedEventsLightEntities = gql`
-    query getIndexUnitsUpdatedEventsLightEntities {
-        response: indexUnitsUpdatedEvents {
-            index {
-                id
-            }
-        }
-    }
-`;
-
-const getIndexUnsubscribedEventsLightEntities = gql`
-    query getIndexUnsubscribedEventsLightEntities {
-        response: indexUnsubscribedEvents {
-            index {
[…]

### 2022-11-15 packages/subgraph/test/validation/hol/flowOperatorValidator.ts

@@ -1,72 +1,0 @@
-import { expect } from "chai";
-import { fetchEntityAndEnsureExistence } from "../../helpers/helpers";
-import {
-    IAccountTokenSnapshot,
-    IEvent,
-    IExpectedFlowOperatorData,
-    IFlowOperator,
-} from "../../interfaces";
-import { getAccountTokenSnapshot } from "../../queries/aggregateQueries";
-import { getFlowOperator } from "../../queries/holQueries";
-import { validateReverseLookup } from "../validators";
-
-export const fetchFlowOperatorAndValidate = async ({
-    event,
-    expectedFlowOperator,
-    isCreate,
-}: {
-    event: IEvent;
-    expectedFlowOperator: IExpectedFlowOperatorData;
-    isCreate: boolean;
-}) => {
-    const flowOperatorId = expectedFlowOperator.id;
-    const flowOperatorEntity =
-        await fetchEntityAndEnsureExistence<IFlowOperator>(
-            getFlowOperator,
-            flowOperatorId,
-            "FlowOperator"
-        );
-
-    validateFlowOperator(flowOperatorEntity, expectedFlowOperator);
-
-    // validate flow operator updated events reverse lookup
-    validateReverseLookup(event, flowOperatorEntity.flowOperatorUpdatedEvents);
-
-    if (isCreate) {
-        await validateATSReverseLookupsForFlowOperator(flowOperatorEntity);
-    }
-};
-
-const validateATSReverseLookupsForFlowOperator = async (
-    flowOperator: IFlowOperator
-) => {
-    const senderATS =
-        await fetchEntityAndEnsureExistence<IAccountTokenSnapshot>(
-            getAccountTokenSnapshot,
-            flowOperator.sender.id + "-" + flowOperator.token.id,
-            "AccountTokenSnapshot"
-        );
-    const flowOperatorLightEntity = { id: flowOperator.id };
-    validateReverseLookup(flowOperatorLightEntity, senderATS.flowOperators);
-};
-
-const validateFlowOperator = (
-    flowOperatorEntity: IFlowOperator,
-    expectedFlowOperator: IExpectedFlowOperatorData
-) => {
-    expect(flowOperatorEntity.id, "Flow Operator: id error").to.equal(
-        expectedFlowOperator.id
-    );
-    expect(
-        flowOperatorEntity.permissions,
-        "Flow Operator: permissions error"
[…]

### 2022-11-15 packages/subgraph/test/validation/hol/streamValidator.ts

@@ -1,17 +1,21 @@
 import { BigNumber } from "@ethersproject/bignumber";
 import { expect } from "chai";
 import { fetchEntityAndEnsureExistence } from "../../helpers/helpers";
-import { IStream, IStreamData, IEvent, IAccount } from "../../interfaces";
+import {
+    IStream,
+    IStreamData,
+    IEvent,
+    IAccount,
+} from "../../interfaces";
 import { getAccount, getStream } from "../../queries/holQueries";
 import { validateReverseLookup } from "../validators";
 
 export const fetchStreamAndValidate = async (
     streamData: IStreamData,
     expectedStreamedUntilUpdatedAt: BigNumber,
-    newFlowRate: string,
+    flowRate: string,
     event: IEvent,
-    isCreate: boolean,
-    newDeposit: string
+    isCreate: boolean
 ) => {
     const streamId = streamData.id;
     const stream = await fetchEntityAndEnsureExistence<IStream>(
@@ -24,8 +28,7 @@ export const fetchStreamAndValidate = async (
         stream,
         expectedStreamedUntilUpdatedAt.toString(),
         streamId,
-        newFlowRate,
-        newDeposit
+        flowRate
     );
 
     // validate flowUpdated reverse lookup on Stream entity
@@ -33,11 +36,11 @@ export const fetchStreamAndValidate = async (
 
     if (isCreate) {
         // validate accounts reverse lookup on Stream entity creation
-        await validateAccountReverseLookupsForStream(stream);
+        validateAccountReverseLookups(stream);
     }
 };
 
-const validateAccountReverseLookupsForStream = async (stream: IStream) => {
+export const validateAccountReverseLookups = async (stream: IStream) => {
     const senderAccount = await fetchEntityAndEnsureExistence<IAccount>(
         getAccount,
         stream.sender.id,
@@ -53,24 +56,19 @@ const validateAccountReverseLookupsForStream = async (stream: IStream) => {
     validateReverseLookup(streamLightEntity, receiverAccount.inflows);
 };
 
-const validateStreamEntity = (
+export const validateStreamEntity = (
     subgraphStream: IStream,
     expectedStreamedUntilUpdatedAt: string,
     streamId: string,
-    newFlowRate: string,
-    newDeposit: string
+    currentFlowRate: string
 ) => {
-    expect(subgraphStream.id, "Stream: id error").to.equal(streamId);
[…]

### 2022-11-15 packages/subgraph/test/validation/hol/subscriptionValidator.ts

@@ -1,7 +1,9 @@
 import { expect } from "chai";
 import { ethers } from "ethers";
-import { Framework } from "@superfluid-finance/sdk-core";
-import { IDAEventType } from "../../helpers/constants";
+import {Framework} from "@superfluid-finance/sdk-core";
+import {
+    IDAEventType,
+} from "../../helpers/constants";
 import { fetchEntityAndEnsureExistence, toBN } from "../../helpers/helpers";
 import {
     IIndexSubscription,
@@ -10,10 +12,13 @@ import {
     IIDAEvents,
     ILightEntity,
 } from "../../interfaces";
-import { getAccount, getSubscription } from "../../queries/holQueries";
+import {
+    getAccount,
+    getSubscription,
+} from "../../queries/holQueries";
 import { validateReverseLookup } from "../validators";
 
-const validateAccountReverseLookupsForSubscription = async (
+export const validateAccountReverseLookups = async (
     subscription: IIndexSubscription
 ) => {
     const subscriptionLightEntity = { id: subscription.id };
@@ -104,7 +109,7 @@ export const fetchSubscriptionAndValidate = async (
     ) {
         // We only enter here if a subscriber is being added for the first time
         // subscribers who delete or set units to 0 are still in the array
-        validateAccountReverseLookupsForSubscription(indexSubscription);
+        validateAccountReverseLookups(indexSubscription);
     }
 };
 

### 2022-11-15 tasks/find-dup-devDependencies.sh

@@ -1,11 +1,0 @@
-#!/bin/sh
-
-P=$(echo packages/*/package.json package.json)
-# find duplicated devDependencies in packages
-jq -r '.devDependencies | keys | .[]' $P | \
-    sort | uniq -c | \
-    grep -ve '^ *1' | awk '{print $2}' | while read i;do
-    echo $i
-    grep '"'$i'"' $P
-    echo
-done

### 2022-11-15 packages/spec-haskell/yellowpaper/Paper1.tex

@@
 It is based on the insight of the deep connection (equivalence/isomorphism) between logic and
-dependently typed programming, often called "the Curry–Howard correspondence", as discovered and
+dependently typed programming, often called ``the Curry–Howard correspondence'', as discovered and
 developed during the 20th century (explained in \cite{wadler2015propositions} by Phillip Wadler as

### 2022-12-19 packages/spec-haskell/yellowpaper/Paper.tex
restatement wip

--- 2022-09-29 packages/spec-haskell/yellowpaper/Paper.tex
@@
-%% Include a preamble at choice during processing.
-\input{preamble.tex}
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Document Preamble
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{article}
 
-\title{Denotational Semantics of General Payment Primitives, and Its Payment System}
+%% Base Folder for Inputs
+\makeatletter
+\def\input@path{{../tex/}}
+\makeatother
 
-\author{\\
-    Miao, ZhiCheng\\
-    Co-founder, Superfluid Finance\\
+%% Import Packages
+\usepackage{fvextra}
+\usepackage{csquotes}
+\usepackage{xcolor}
+\usepackage{minted}
+
+%% Literate Haskell Macros
+
+%%% include common formatting
+\input{lhsfmt.tex}
+%%% for ignoring some code
+\long\def\ignore#1{}
+%%% for creating a paragraph
+\newcommand{\lhsparagraph}[1]{\paragraph{#1}\mbox{}\\}
+
+%% Document Meta Data
+
+\title{Superfluid Money: Enabling Generalized Schemes For Monetary Units}
+
+\author{
+    Miao, ZhiCheng (hellwolf)\\
+    Co-Founder, Superfluid Finance\\
     miao@superfluid.finance
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Title Page
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{biblatex}
+\addbibresource{../tex/Biblio.bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Document Body
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
 
@@
     \begin{center}
-        (Some distant lyrics as the placeholder for the actual abstract)
+        (Some Distant Lyric as Placeholder)
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
 
-It should be fair to say, every aspect of money are controversial: the nature of money, the value of money, money and
-banking, and monetary reconstruction. Two major schools of thoughts about theory of money are the \textit{Austrian
-    school} (\cite{von2013theory}) and the \textit{Chicago school} (\cite{friedman1989quantity}). That is before the
-appearance of Internet-era version of monetary reconstruction, broadly defined as cryptocurrency, which challenges
-theories of money further and demands their updates (\cite{ammous2018can} \cite{hardle2020understanding}).
+It should be fair to say, every aspects of money are controversial: the nature of money, the value of money, money and
+banking, and monetary reconstruction. \cite{von2013theory}
 
-This yellow paper does not intend to address these controversies, but to focus on the function of money. According to
-Von Mises:
+But less has been challenged is the underlying theory of money schemes, or often called payment systems.
 
-\begin{displayquote}
-The function of money is to facilitate the business of the market by acting as a common medium of
-exchange. \footfullcite[][Chapter One, Chapter I, § 1, p1]{von2013theory}
-\end{displayquote}
+This yellow paper aims to add a new controversy, by introducing the concept of context into the money schemes and
+generalizing existing theory for a new unifying theory of money schemes in Part 1.
 
-How do different forms of money perform this function, especially in the information age, when electronic forms of money
-are increasingly used?
+In Part 2, we also put forth a realization and specification of a version of contextual money scheme known enabled by a
+system called Superfluid money.
 
-This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
-can perform its function of medium of exchange.
+The yellow paper also uses literate Haskell as a technique to embed concepts and specifications as compilable code for
+better verifiability and reusability.
 
-In Chapter 2, we shall first explore the foundation for the survey. Here we present a formal definition of payment
-system and its components. We then select a few relevant approaches used in computer science useful for modeling and
-defining formal specification for the payment system.
+(STILL WIP)
 
-One of the approaches is \textit{denotational semantics}, which is used in Chapter 3 of the paper to define the general
-payment primitives. Along with the denotational semantics, a restatement\footnote{It is a borrowed term from common law:
-"restatement of the law". In our case, the denotative mathematical "laws".} of it in \textit{Haskell programming
-    language} (\cite{hudak1992report} \cite{jones2003haskell} \cite{marlow2010haskell}) is also included.
+\newpage
+\part{Philosophy of Money}
+\newpage
 
-In Chapter 4, a reference implementation of the general payment primitives and its payment system called
-\textit{Superfluid Money} is introduced.
+\section{Nature of Money}
 
-In Chapter 5, some possible further investigations are included for future study purpose.
+\section{Money Schemes}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Foundation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{A New Unifying Theory}
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Payment System}
-%%%%%%%%%%%%%%%%%%%%%%%%
+\input{MoneyDistributionConcepts.tex}
 
-Here we present a definition of payment system and its components.
+\subsection{Communism}
 
-\paragraph{Payment system}
+\input{Communism.tex}
 
-It can be solely defined by these components:
+\subsection{Context free Schemes}
 
-\begin{itemize}
-\item \textit{money distribution} models how monetary value is distributed amongst bearers\footnote{(Banking \& Finance)
-a person who presents a note or bill for payment. - Collins English Dictionary},
-\item \textit{payment primitives} updates money distribution,
-\item \textit{payment execution environment} performs payment primitives,
-\item and \textit{forms of money medium} are the "user interfaces" of money for the bearers.
-\end{itemize}
+Most of the existing money schemes are of this category, where a money unit completely disregards its context and hence
+its liquidity value and bearer are static until the next money redistribution occurs.
 
-\paragraph{Modernization}
+Here are the type definitions of these money schemes defined in \cite{buldas2021unifying}:
 
-For its modern upgrade, the system should also have these properties:
+TODO...
 
-\begin{itemize}
-\item Money can be distributed continuously over time, as opposed to be discrete.
-\item Payment primitives can involve more than two parties, as opposed to be only for a sender and a receiver.
-\item Financial system should be compositional.
-\end{itemize}
+\subsection{Contextual Schemes}
 
-\subsection{Money Distribution}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In contract, under the contextual money schemes, the liquidity value and maybe even bearer of a money unit can be a
+function of context too.
 
-A representation of money and its distribution proposed in \cite{buldas2021unifying} involves the following components:
+TODO...
 
-\begin{itemize}
-\item U is the set of monetary units.
-\item $\nu : U \rightarrow \mathbb{N}$ is the value function defining the value $\nu(u)$ of every value unit u. The set
-    $\mathbb{N}$ is the set of all natural numbers, but instead, we can use any set of numerals that is totally ordered
-    (\eg\ integers, real numbers).
-\item $\beta : U \rightarrow \mathcal{B}$ is the bearer function defining the bearer $\beta(u)$ of a unit. The set
-    $\mathcal{B}$ is the set of possible bearers. The bearer is usually a legal construction defining any type of legal
-    entity, such as a person, a family, a company, a state institution, etc.
-\end{itemize}
-
-This discrete nature of this money distribution model is schematically depicted in~\ref{fig:discrete-md}:
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{../assets/discrete-money-distribution.png}
-    \caption{Schematic representation of discrete money distribution}
-    \label{fig:discrete-md}
-\end{figure}
-
-\subsubsection{Using Context}
-
-But the discrete nature of the model does not provide the necessary element for us to add the desired properties to the
-payment system. Here we propose a modification that involves the usage of \textit{context ($\gamma$)}:
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{../assets/money-distribution-with-ctx.png}
-    \caption{Schematic representation of money distribution with context}
-    \label{fig:md-with-ctx}
-\end{figure}
-
-Note that in this model, context can be updated independently while value functions of the same money distribution can
-produce different monetary values.
-
-\paragraph{Components of Context}
-
-Here are some possible components of context, and how they work:
-
-\begin{itemize}
-\item If time (t) is included the context, then monetary value of each monetary unit can vary continuously over
-    time. Time is part of the physical reality, hence not changeable by the actors in the payment system.
-\item Any subset of monetary units can also have their value functions depending on the same information in
-    context. This could enable payment primitives that involve many parties. This set of information in context is
-    referred to as \textit{ctx :: SharedContext}, they can be changed over time by the actors in the payment system.
-\end{itemize}
-
-For the purpose of this paper, the model of context is: $\gamma = (t :: Timestamp) \oplus (ctx :: SharedContext)$.
-
-\subsubsection{Haskell Definition Of Money Distribution}
-
-\input{MoneyDistribution.lhs.tex}
-
-\subsection{Payment Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Payment primitives are functions that takes a money distribution, shared context, some payment instruction (args) and
-timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
-associative binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid. } of money
-distribution and shared context as outputs:
-
-\begin{minted}[escapeinside=||,mathescape=true]{haskell}
-    somePaymentPrimitive :: ( Timestamp t
-                            , MoneyDistribution md
-                            , SharedContext ctx
-                            , PaymentInstruction args
-                            , Monoid md, Monoid ctx
-                            )
-                         => md |$\times$| ctx -> args -> t -> md |$\times$| ctx
-\end{minted}
-
-Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
-in the same money distribution; additionally primitives should be the only constructs in a payment system that can
-update money distribution.
-
-Updates are \textit{monoidal}, so that they can be incremental and their parallel executions can be modeled.
-
-The best known primitive is instant transfer of monetary value between one monetary unit to another. The introduction of
-context enables more primitives to be defined, and this will be discussed in later chapters.
-
-\subsection{Payment Execution Environment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The purpose of a payment execution environment is to perform the actual payment primitives, where their computation
-interface, parallel evaluation strategies and payment system solvency are defined.
-
-It is out of scope for this paper to survey in-depth the problem space of the operation semantics of payment execution
-environments. Nonetheless, a simplified model and some potential extensions to it is discussed briefly.
-
-\subsubsection{Composing Financial Contracts}
-
-\input{FinancialContract.lhs.tex}
-
-\subsubsection{Simplified Execution Environment Models}
-
-\input{PaymentExecutionEnvironment.lhs.tex}
-
-\subsection{Payment System Solvency}
-
-While money distribution does not assign meaning to the range of monetary values, in real world applications, negative
-values can have special meanings. In the following analysis, we call any money unit that has a negative monetary value
-insolvent.
-
-The detailed analysis of these solvency models are out of scope for this paper.
-
-\paragraph{Buffer Based Solvency Treatment}
-
-In a nondeterministic execution environment, we cannot determine when any financial contract will actually be
-executed. That means, there is always a chance a monetary unit could reach negative monetary value.
-
-To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value which is set aside in a solvency conditional financial contract, such that if a solvency
-condition arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the execution.
-
-\paragraph{Deterministic Solvency Treatment}
-
-Since \textit{fcNext} returns what is the next financial contract executable at a specific time, this deterministic
-property eliminates the need for the buffer.
-
-But it introduces a different type of systemic risk, that is denial-of-service, since the system cannot advance the
-system time until all next executable contracts are executed.
-
-\subsection{Money Mediums}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{displayquote}
-A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
-digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
-etc. \footfullcite[][P3]{buldas2021unifying}
-\end{displayquote}
-
-We call them money mediums, and we further separate them into two big groups:
-
-\begin{itemize}
-\item \textit{Token and its Accounts} - \eg\ bank currency accounts. Each token is its own centralized execution
-    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
-    token.
-\item \textit{Note} - \eg\ federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
-    independent of the notes, but it needs notes to complete the execution of financial contracts.
-\end{itemize}
-
-One of the main differences is from the ``user interface'' perspective. A bearer expects to keep many notes at hand,
-while maybe only needs a few accounts for each token. Also it is up to bearers to keep track of all their notes, while
-token can keep track of most of the states for bearers; hence notes are more decentralized and tokens are more
-centralized. Some also argue note-like model is better for complex concurrent and distributed computing environment
-\footfullcite[][P2]{chakravarty2020extended}.
-
-\subsubsection{Haskell Definition Of Money Mediums}
-
-\input{MoneyMedium.lhs.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Relevant Approaches}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The focus of this paper is to formally define a set of payment primitives that modernize our payment systems. To prevent
-reinventing wheels, it is relevant to discuss first some approaches in computer science that are believed to help
-solving this challenge.
-
-\subsection{Functional Reactive Programming}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Recall that we want our modernized payment systems to handle money distribution continuously over time, and its financial
-contracts compositional. A very closely related software design paradigm best known to address those needs is
-\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving
-multimedia animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
-\cite{wan2000functional} making FRP a more general framework for programming hybrid system with continuous behaviors in
-a high-level, declarative manner.
-
-After FRP got more adoption, it evolved to some variations that support discrete semantics, and some variations better
-suited more for interactive systems. In this paper we will stick to and revisit the basic constructions of the original
-formulation used in \cite{elliott1997functional} where we will draw inspirations from.
-
-\paragraph{Temporal Modeling and Behaviors}
-
-Values that vary over continuous time are called \textit{behaviors}. They are first-class values, and are built up
-compositionally. In modernized payment systems, we should want the monetary values of monetary units capable of varying over
-continuous time. The semantic function of $\alpha$-behaviors produces the value of type $\alpha$ of a behavior at a given
-time:
-
-\begin{equation}
-    at : Behavior_{\alpha} \rightarrow Time \rightarrow \alpha
-\end{equation}
-
-\paragraph{Event Modeling}
-
-Like behaviors, \textit{events} are first-class values too. The semantic function of $\alpha$-event describes the time and
-information associated with an \textit{occurrence} of the event:
-
-\begin{equation}
-    occ : Event_{\alpha} \rightarrow Time \times \alpha
-\end{equation}
-
-In modernized payment systems, the payment primitives executed in payment execution environments are one type of
-events. More types of events can be read from the original paper \footfullcite[][section 2.3 Semantics of
-    Events]{elliott1997functional}.
-
-\paragraph{Reactivity}
-
-They key to modeling the payment execution environment using FRP is the \textit{reactivity}, which makes behaviors
-reactive. Specifically, the behavior \textit{b untilB e} exhibits b's behavior until \textit{e} occurs, and then swiches
-to a new behavior encoded in \textit{e}:
-
-\begin{equation}
-    \begin{split}
-    &untilB : Behavior_{\alpha} \rightarrow Event_{Behavior_{\alpha}} \rightarrow Behavior_{\alpha} \\
-    &at\ [\![b\ until\ B]\!]\ t = if\ t\ \leq\ t_{e}\ then\ at\ [\![b]\!]\ t\ else\ at\ [\![b']\!]\ t \\
-    &\qquad where (t_e, b') = occ[\![e]\!]
-    \end{split}
-\end{equation}
-
-Note that $[\![.]\!]$ is the denotational semantics notation to be introduced later.
-
-In the context of modernized payment systems, the occurrences of payment primitives (events) change the behaviors of
-monetary units in how much monetary values it has over continuous. The building blocks of the financial contracts should
-be about modeling these events and their reactivity declaratively.
-
-\subsection{Denotational Semantics}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We also want a formal and precise specification of payment primitives. The title of the paper includes
-\textit{denotational semantics}: ``it is a \textit{compositional} style for precisely specifying the meanings of
-languages, invented by Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward})'', and Conal Elliott
-proposed that denotational semantics can also be applied to \textit{data types within a programming language}
-\footfullcite[][section 2, denotational semantics and data types]{Elliott2009-type-class-morphisms-TR}.
-
-To create denotational semantics for each syntactic category $\mathcal{C}$, we should specify:
-
-\begin{itemize}
-\item a mathematical model $[\![\mathcal{C}]\!]$ of meanings, and
-\item a semantic function $[\![.]\!]_{\mathcal{C}} :: \mathcal{C} \rightarrow [\![\mathcal{C}]\!]$.
-\end{itemize}
-
-The syntactic category we are interested in is \textit{payment primitives}, which we should treat them as FRP-style
-\textit{Behavior} data types. In the following chapters, it is also unambiguously referred to in short as
-$[\![.]\!]$. Various $[\![.]\!]$ must be compositional, \ie must be defined by structural recursion.
-
-It is important to note that our purpose of using the denotational semantics is to give precise meaning to payment
-primitives, independent of its implementation (which deals with performance, optimization, side effects, etc.). We will
-spend the next chapter exploring the denotational semantics for general payment primitives in modernized payment
-systems.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{General Payment Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The set of payment primitives supported in a payment system is general, if monetary value of each monetary unit can vary
-continuously over time and monetary values can logically be shifted between two or more monetary units. The extent of
-the generality of each payment system may vary. We introduce a set of payment primitives that is general and serves as a
-starting point for the readers to explore the space of modern payment system. The specifications will be formally
-defined using denotational semantics, and its restatement in Haskell is also applied as a constructive artifact friendly
-to computer environment\footnote{One may argue for a restatement in \textit{Agda} instead, for it has a richer
-dependently-type system for needed constructive proofs. This matter will be dealt in the ``future investigations'' chapter
-of this paper.}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Denotational Semantics}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Here is the convention for symbols used in the formulas:
-
-\begin{itemize}
-    \item \textbf{M} is \textit{money distribution}.
-    \item \textbf{U} is for \textit{the set of all money units in M}.
-    \item $\boldsymbol{\nu}$ is for \textit{monetary value}.
-    \item \textbf{t} is for \textit{time}.
-    \item \textbf{mu, ma, mb, etc.} are for \textit{monetary units}.
-\end{itemize}
-
-\subsection{Money Distribution}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Recall the definition of payment system previously, money distribution sits in the core of the system, and that is the
-syntactic category $\mathcal{M}$ we will be dealing with:
-
-\begin{itemize}
-\item The meaning of $[\![\mathcal{M}]\!]$ is money distribution.
-\item Semantic function $[\![.]\!] :: \mathcal{M} \rightarrow [\![\mathcal{M}]\!] $ include payment primitives.
-\end{itemize}
-
-\paragraph{Model}
-
-This is the model for money distribution.
-
-\begin{equation}\label{md_model}
-    \begin{split}
-        [\![M\ mu\ t\ \nu]\!] &= mu \rightarrow t \rightarrow \nu \\
-        [\![.]\!] &= M\ mu\ t\ \nu \rightarrow (mu \rightarrow t \rightarrow \nu) \\
-    \end{split}
-\end{equation}
-
-\paragraph{Monoidal}
-
-With this model, $\mathcal{M}$ is also monoidal, hence compositional.
-
-\begin{equation}
-    \begin{split}
-        [\![\emptyset]\!] &= \lambda mu \times t\ \rightarrow 0 \\
-        [\![ma \oplus mb]\!] &= \lambda mu \times t\ \rightarrow [\![ma]\!]\ mu\ t\ +\ [\![mb]\!]\ mu\ t \\
-    \end{split}
-\end{equation}
-
-Knowing that function application category $a \rightarrow b$ is also monoidal:
-
-\begin{equation}
-    \begin{split}
-        \emptyset &= \lambda a \rightarrow \emptyset \\
-        f \oplus g &= \lambda a \rightarrow f\ a \oplus g\ a \\
-    \end{split}
-\end{equation}
-
-With some substitutions, we get the desired \textit{monoid homomorphism} property for $\mathcal{M}$.
-
-\begin{equation}
-    \begin{split}
-        [\![\emptyset]\!] &= \emptyset \\
-        [\![ma \oplus mb]\!] &= [\![ma]\!] \oplus [\![mb]\!] \\
-    \end{split}
-\end{equation}
-
-\subsection{Payment Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A payment primitive \textit{prim} is a semantic function that produces a monoidal money distribution, semantically
-representing an ``update'' to a money distribution:
-
-\begin{equation}
-    [\![prim\ args]\!] = [\![M\ mu\ t\ \nu]\!]
-\end{equation}
-
-\paragraph{Law of Conservation of Value}
-
-First of all, money distribution must obey the \textit{law of conservation of value}:
-
-\begin{equation}
-    \forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t = 0}
-\end{equation}
-
-That is to say, for any given time, the sum of monetary value of all monetary units shall always equal to zero. Zero is
-used to keep the semantical meaning of payment system simple and elegant. In its applications, a payment system may use
-some special monetary unit accounting negative monetary values to accommodate concepts such as mining, minting, money
-printing, etc.
-
-Further more, in a payment system, we restrict that only payment primitives can provide ``updates'' to its money
-distribution. So a money distribution is a result of a sequence of payment primitive updates:
-
-\begin{equation}
-    \begin{split}
-        &\textbf{Axioms A:\ }
-        \textit{law of conservation of value for payment primitives} \\
-        &\forall t \in \mathbb{R} ({\displaystyle \sum_{mu \in U} [\![prim\ args]\!]\ mu\ t = 0}) \\
-        \\
-        &\textbf{Axioms B:\ }
-        \textit{money distribution consists of updates from payment primitives} \\
-        &[\![M\ mu\ t\ \nu]\!] =
-          [\![prim_1\ args_1]\!] \oplus [\![prim_2\ args_2]\!] \oplus [\![prim_3\ args_3]\!] \oplus \dotsb
-    \end{split}
-\end{equation}
-
-This allows us impose the law of conservation of value on payment primitives, then prove the law for money
-distribution inductively using monoid homomorphism:
-
-\begin{equation}
-    \begin{split}
-        &\textbf{In addition to the axioms, given:} \\
-        \\
-        &\textit{(base case with empty money distribution is trivial)} \\
-        &\forall t \in \mathbb{R} {\displaystyle \sum_{mu \in U} [\![\emptyset]\!]\ mu\ t = 0} \\
-        \\
-        &\textit{(monoid homomorphism)} \\
-        &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1\oplus prim_2\ args_2]\!]\ mu\ t} = \\
-        &\qquad {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
-          {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \\
-        \\
-        &\textbf{We have:} \\
-        &\forall t \in \mathbb{R}. \\
-        &{\displaystyle \sum_{mu \in U} [\![M\ mu\ t\ \nu]\!]\ mu\ t} \\
-        &\textit{(applying Axioms B)} \\
-        = &{\displaystyle \sum_{mu \in U}
-            ([\![prim_1\ args_1]\!] \oplus
-            [\![prim_2\ args_2]\!] \oplus
-            [\![prim_3\ args_3]\!]\oplus \dotsb)
-        }\ mu\ t\\
-        &\textit{(applying monoid homomorphism)} \\
-        = &{\displaystyle \sum_{mu \in U} [\![prim_1\ args_1]\!]\ mu\ t} \oplus
-        {\displaystyle \sum_{mu \in U} [\![prim_2\ args_2]\!]\ mu\ t} \oplus
-        {\displaystyle \sum_{mu \in U} [\![prim_3\ args_3]\!]\ mu\ t} \oplus \dotsb
-        )\\
-        &\textit{(applying Axioms A)} \\
-        =&\ 0
-        \\
-        \blacksquare
-    \end{split}
-\end{equation}
-
-\subsection{One to One Payment Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-???
-
-\begin{equation}\label{sem_transfer}
-    \begin{split}
-        [\![&transfer\ from\ to\ amount\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ from = mu \rightarrow -amount \\
-        &|\ to   = mu \rightarrow amount \\
-        &|\ otherwise \rightarrow 0 \\
-        )
-    \end{split}
-\end{equation}
-
-\begin{equation}\label{sem_updateConstantFlow}
-    \begin{split}
-        [\![&updateConstantFlow\ from\ to\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ from = mu \rightarrow -flowRate * (t - t') \\
-        &|\ to   = mu \rightarrow flowRate  * (t - t') \\
-        &|\ otherwise \rightarrow 0 \\
-        )
-    \end{split}
-\end{equation}
-
-\subsection{Index Abstraction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Proportional Distribution Primitives}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{equation}
-    unit :: sub \rightarrow subs \rightarrow Int
-\end{equation}
-
-\begin{equation}
-    proportion\ sub\ subs = {{ unit\ sub\ subs } \over { \displaystyle \sum_{x \in subs} unit\ x\ subs }}
-\end{equation}
-
-\begin{equation}\label{sem_distributeProportionally}
-    \begin{split}
-        [\![&distributeProportionally\ pub\ subs\ amount\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ pub = mu \rightarrow -amount \\
-        &|\ \exists sub \in subs\ { sub = mu } \rightarrow amount * (proportion\ mu\ subs) \\
-        &|\ otherwise \rightarrow 0 \\
-        )
-    \end{split}
-\end{equation}
-
-\begin{equation}\label{sem_distributeProportionally}
-    \begin{split}
-        [\![&updateProportionalDistributionConstantFlow\ pub\ subs\ flowRate\ t'\ md]\!] = [\![md]\!]\ \oplus \\
-        (\lambda\ case&\ mu\ t \\
-        &|\ pub = mu \rightarrow -flowRate * (t - t') \\
-        &|\ \exists sub \in subs\ { sub = mu } \rightarrow flowRate * (t - t') * (proportion\ mu\ subs) \\
-        &|\ otherwise \rightarrow 0 \\
-        )
-    \end{split}
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Restatement in Haskell}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Superfluid Money - A Reference Implementation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\part{Superfluid Money}
+\newpage
 
@@
 
-\section{Type Of Monetary Units}
+\section{Type Of Money Units}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Future Investigations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 
-\section{Restatement in Agda, Correctness and Equivalence Proofs}
-
-\section{Payment in General Accounting Domains}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
 \printbibliography{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
